---
title: "Attitudes"
output: html_document
date: "2026-04-15"
---

```{r echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
library(dplyr)
library(tidyverse)
library(kableExtra)
library(lmtest)
library(ggplot2)
library(fixest)
library(lfe)
#rm(list=ls())
options(tibble.width = Inf)
options(width = 200)
```

```{r preliminaries, echo=FALSE}
rm(list=ls()) #clean out memory 
```

## Google Trends Search

Loading

```{r}
syria   <- read_csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Syriasentiment1.csv")
ukraine <- read_csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Ukrainesentiment1.csv")

df <- bind_rows(syria, ukraine)
```

```{r}
library(tidyr)

df_wide <- df %>%
  select(year, refugee_group, avg_tone_hostile_proxy, share_strongly_negative) %>%
  pivot_wider(names_from = refugee_group, values_from = c(avg_tone_hostile_proxy, share_strongly_negative))

df_wide <- df_wide %>%
  mutate(
    tone_gap = avg_tone_hostile_proxy_ukraine - avg_tone_hostile_proxy_syria,
    strong_neg_gap = share_strongly_negative_ukraine - share_strongly_negative_syria
  )

library(ggplot2)

ggplot(df_wide, aes(x = year)) +
  geom_line(aes(y = avg_tone_hostile_proxy_syria, color = "Syria")) +
  geom_line(aes(y = avg_tone_hostile_proxy_ukraine, color = "Ukraine")) +
  labs(
    y = "Media tone (hostility proxy)",
    color = "Group",
    title = "Media tone toward refugees by origin"
  )
```

Federal

```{r}
federal_afd_share <- readRDS("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/federal_muni_harm_25 (1).rds")

national_df <- federal_afd_share %>%
  filter(election_year >= 2013) %>%
  mutate(
    # Replace NA with 0 for fringe parties
    afd = coalesce(afd, 0),
    npd = coalesce(npd, 0),
    rep = coalesce(rep, 0),
    dvu = coalesce(dvu, 0),
    die_rechte = coalesce(die_rechte, 0),

    # Construct far-right composite at Kreis level
    far_right_local = afd + npd + rep + dvu + die_rechte
  ) %>%
  group_by(election_year) %>%
  summarize(
    # Properly weighted national AfD share
    afd_share = sum(afd * valid_votes, na.rm = TRUE) /
                sum(valid_votes, na.rm = TRUE),

    # Properly weighted national far-right share
    far_right_share = sum(far_right_local * valid_votes, na.rm = TRUE) /
                      sum(valid_votes, na.rm = TRUE)
  ) %>%
  rename(year = election_year) %>%
  arrange(year)
```

```{r}
library(dplyr)
library(ggplot2)
library(patchwork)
library(scales)

# ----------------------------
# Clean media data
# ----------------------------
media_plot <- df_wide %>%
  transmute(
    year = as.numeric(year),
    syria_hostility   = -avg_tone_hostile_proxy_syria,
    ukraine_hostility = -avg_tone_hostile_proxy_ukraine
  ) %>%
  arrange(year)

# ----------------------------
# Clean vote data
# ----------------------------
afd_plot <- national_df %>%
  transmute(
    year = as.numeric(year),
    afd_share = as.numeric(afd_share),
    far_right_share = as.numeric(far_right_share)
  ) %>%
  distinct(year, .keep_all = TRUE) %>%
  arrange(year)

# ----------------------------
# Define x-axis ticks (every other year)
# ----------------------------
year_ticks <- seq(2013, 2025, by = 2)

# ----------------------------
# Top plot
# ----------------------------
p1 <- ggplot(media_plot, aes(x = year)) +
  geom_line(aes(y = syria_hostility, color = "Syria"), linewidth = 1) +
  geom_point(aes(y = syria_hostility, color = "Syria"), size = 2) +
  geom_line(aes(y = ukraine_hostility, color = "Ukraine"), linewidth = 1) +
  geom_point(aes(y = ukraine_hostility, color = "Ukraine"), size = 2) +
  scale_color_manual(values = c("Syria" = "#F8766D", "Ukraine" = "#00BFC4")) +
  scale_x_continuous(breaks = year_ticks, limits = c(2013, 2025)) +
  labs(
    title = "Media hostility toward refugees by origin",
    x = NULL,
    y = "Refugee hostility",
    color = "Group"
  ) +
  theme_minimal(base_size = 12) +  # smaller overall text
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10)
  )

# ----------------------------
# Bottom plot
# ----------------------------
p2 <- ggplot(afd_plot, aes(x = year)) +
  geom_line(aes(y = afd_share, color = "AfD", group = 1), linewidth = 1) +
  geom_point(aes(y = afd_share, color = "AfD"), size = 2.5) +
  geom_line(aes(y = far_right_share, color = "Far-right composite", group = 1),
            linewidth = 1, linetype = "dashed") +
  geom_point(aes(y = far_right_share, color = "Far-right composite"), size = 2) +
  scale_color_manual(values = c("AfD" = "black", "Far-right composite" = "gray45")) +
  scale_x_continuous(breaks = year_ticks, limits = c(2013, 2025)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(
    title = "National far-right vote share",
    x = "Year",
    y = "Vote share",
    color = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.text = element_text(size = 10)
  )

# ----------------------------
# Combine plots
# ----------------------------
final_plot <- p1 / p2 +
  plot_layout(heights = c(1.2, 1))

final_plot
```

```{r}
library(dplyr)
library(ggplot2)
library(patchwork)
library(scales)

# ----------------------------
# 1. Prepare data
# ----------------------------
media_plot <- df_wide %>%
  transmute(
    year = as.numeric(year),
    syria_hostility   = -avg_tone_hostile_proxy_syria,
    ukraine_hostility = -avg_tone_hostile_proxy_ukraine
  ) %>%
  arrange(year)

afd_plot <- national_df %>%
  transmute(
    year = as.numeric(year),
    afd_share = as.numeric(afd_share),
    far_right_share = as.numeric(far_right_share)
  ) %>%
  distinct(year, .keep_all = TRUE) %>%
  arrange(year)

year_ticks <- seq(2013, 2025, by = 2)

# ----------------------------
# 2. Common theme
# ----------------------------
theme_journal <- theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10, color = "black"),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    legend.position = "right",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "grey85", linewidth = 0.4),
    axis.line = element_line(color = "black", linewidth = 0.3),
    axis.ticks = element_line(color = "black", linewidth = 0.3),
    strip.text = element_text(size = 11, face = "bold"),
    plot.margin = margin(8, 12, 8, 8)
  )

# ----------------------------
# 3. Top panel: media hostility
# ----------------------------
p1 <- ggplot(media_plot, aes(x = year)) +
  geom_vline(xintercept = c(2015, 2022),
             linetype = "dotted", color = "grey55", linewidth = 0.5) +
  geom_line(aes(y = syria_hostility, color = "Syria"), linewidth = 1) +
  geom_point(aes(y = syria_hostility, color = "Syria"), size = 2.2) +
  geom_line(aes(y = ukraine_hostility, color = "Ukraine"), linewidth = 1) +
  geom_point(aes(y = ukraine_hostility, color = "Ukraine"), size = 2.2) +
  annotate("text", x = 2015, y = max(media_plot$syria_hostility, media_plot$ukraine_hostility, na.rm = TRUE) + 0.08,
           label = "2015", size = 3, color = "grey35") +
  annotate("text", x = 2022, y = max(media_plot$syria_hostility, media_plot$ukraine_hostility, na.rm = TRUE) + 0.08,
           label = "2022", size = 3, color = "grey35") +
  scale_color_manual(values = c("Syria" = "#D55E00", "Ukraine" = "#0072B2")) +
  scale_x_continuous(breaks = year_ticks, limits = c(2013, 2025)) +
  labs(
    title = "Media hostility toward refugees by origin",
    x = NULL,
    y = "Hostility index\n(higher = more negative)",
    color = NULL
  ) +
  coord_cartesian(clip = "off") +
  theme_journal

# ----------------------------
# 4. Bottom panel: far-right vote share
# ----------------------------
p2 <- ggplot(afd_plot, aes(x = year)) +
  geom_vline(xintercept = c(2015, 2022),
             linetype = "dotted", color = "grey55", linewidth = 0.5) +
  geom_line(aes(y = afd_share, color = "AfD", group = 1), linewidth = 1) +
  geom_point(aes(y = afd_share, color = "AfD"), size = 2.4) +
  geom_line(aes(y = far_right_share, color = "Far-right composite", group = 1),
            linewidth = 0.9, linetype = "22") +
  geom_point(aes(y = far_right_share, color = "Far-right composite"), size = 2) +
  scale_color_manual(values = c("AfD" = "black", "Far-right composite" = "grey45")) +
  scale_x_continuous(breaks = year_ticks, limits = c(2013, 2025)) +
  scale_y_continuous(
    labels = percent_format(accuracy = 1),
    expand = expansion(mult = c(0.02, 0.08))
  ) +
  labs(
    title = "National far-right vote share",
    x = "Year",
    y = "Vote share",
    color = NULL
  ) +
  theme_journal

# ----------------------------
# 5. Combine
# ----------------------------
final_plot <- p1 / p2 +
  plot_layout(heights = c(1.15, 1)) &
  theme(legend.position = "right")

final_plot
```

# Media Scraping

```{r}
library(readr)
library(dplyr)
library(stringr)

syria   <- read_csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Newspaper Data/Syria_newspapers_new.csv")
ukraine <- read_csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Newspaper Data/Ukraine_newspapers_new.csv")

articles <- bind_rows(syria, ukraine) %>%
  mutate(
    refugee_group = str_to_lower(refugee_group),
    year = as.integer(year)
  )
```

```{r}
articles <- articles %>%
  filter(!is.na(url), str_detect(url, "^https?://")) %>%
  distinct(url, .keep_all = TRUE)

#install.packages("urltools")
library(urltools)

domain_counts <- articles %>%
  mutate(domain = domain(url)) %>%
  count(domain, sort = TRUE)

domain_counts
```

```{r}
articles <- articles %>%
  mutate(
    domain_clean = str_replace(SourceCommonName, "^www\\.", ""),
    domain_clean = str_replace(domain_clean, 
      "^(plus|blogs|cmk|faktenfinder|newsticker|blog|projekte|causa)\\.", "")
  )

articles %>%
  count(domain_clean, sort = TRUE)
```

Scraping Articles

```{r}
#install.packages("rvest")
#install.packages("xml2")
library(rvest)
library(xml2)
library(stringr)
library(dplyr)
library(purrr)
library(tibble)

get_article_text <- function(url) {
  tryCatch({
    page <- read_html(url)
    
    title <- page %>%
      html_element("title") %>%
      html_text2()

    text_parts <- page %>%
      html_elements("article p, main p, .article p, .entry-content p, .post-content p") %>%
      html_text2()

    if (length(text_parts) < 5) {
      text_parts <- page %>%
        html_elements("p") %>%
        html_text2()
    }

    tibble(
      url = url,
      title = ifelse(length(title) == 0, NA_character_, title),
      text = str_squish(paste(text_parts, collapse = " "))
    )
  }, error = function(e) {
    tibble(
      url = url,
      title = NA_character_,
      text = NA_character_
    )
  })
}

test_urls <- articles %>%
  slice(1:20) %>%
  pull(url)

test_scrape <- purrr::map_dfr(test_urls, get_article_text)

test_scrape %>%
  select(url, title, text)

test_scrape %>%
  mutate(text_length = nchar(text)) %>%
  select(url, text_length)
```

```{r}
test_scrape %>%
  mutate(
    text_length = nchar(text),
    is_missing = is.na(text),
    has_boilerplate = grepl("Artikel-Länge|Uneingeschränkter Zugriff", text)
  ) %>%
  summarize(
    pct_missing = mean(is_missing),
    pct_short = mean(text_length < 500, na.rm = TRUE),
    pct_boilerplate = mean(has_boilerplate, na.rm = TRUE)
  )
```

Full Scrape

```{r}
library(dplyr)
library(stringr)
library(purrr)
library(rvest)
library(xml2)
library(tibble)
library(readr)

# --------------------------------
# 1. Keep all current news-source domains
# --------------------------------
keep_domains <- c(
  "t-online.de",
  "tagesspiegel.de",
  "welt.de",
  "sueddeutsche.de",
  "faz.net",
  "focus.de",
  "spiegel.de",
  "tagesschau.de",
  "zeit.de",
  "jungewelt.de",
  "bild.de",
  "wallstreet-online.de",
  "unsere-zeit.de",
  "behoerden-spiegel.de",
  "kino-zeit.de"
)

articles_keep <- articles %>%
  filter(domain_clean %in% keep_domains) %>%
  filter(!is.na(url)) %>%
  distinct(url, .keep_all = TRUE)

# --------------------------------
# 2. Boilerplate patterns
# --------------------------------
boilerplate_pattern <- paste(
  c(
    "Artikel-Länge",
    "Uneingeschränkter Zugriff",
    "Jetzt abonnieren",
    "Mehr zum Thema",
    "Lesen Sie auch",
    "© dpa",
    "© picture alliance",
    "Datenschutzerklärung",
    "Impressum",
    "Newsletter",
    "Cookie"
  ),
  collapse = "|"
)

# --------------------------------
# 3. Cleaning function
# --------------------------------
clean_article_text <- function(text) {
  if (is.na(text)) return(NA_character_)
  
  text %>%
    str_replace_all("\\s+", " ") %>%
    str_replace_all("Artikel-Länge:.*?Zugriff", " ") %>%
    str_replace_all("Jetzt abonnieren.*", " ") %>%
    str_replace_all("Mehr zum Thema.*", " ") %>%
    str_replace_all("Lesen Sie auch.*", " ") %>%
    str_replace_all("©\\s*dpa.*", " ") %>%
    str_replace_all("©\\s*picture alliance.*", " ") %>%
    str_squish()
}

# --------------------------------
# 4. Scraper
# --------------------------------
get_article_text <- function(url) {
  tryCatch({
    page <- read_html(url)
    
    title <- page %>%
      html_element("title") %>%
      html_text2()

    text_parts <- page %>%
      html_elements("article p, main p, .article p, .entry-content p, .post-content p") %>%
      html_text2()

    if (length(text_parts) < 5) {
      text_parts <- page %>%
        html_elements("p") %>%
        html_text2()
    }

    raw_text <- str_squish(paste(text_parts, collapse = " "))
    clean_text <- clean_article_text(raw_text)

    tibble(
      url = url,
      title = ifelse(length(title) == 0, NA_character_, title),
      raw_text = raw_text,
      text = clean_text,
      text_length = ifelse(is.na(clean_text), NA_integer_, nchar(clean_text)),
      is_missing = is.na(clean_text) | clean_text == "",
      has_boilerplate = ifelse(is.na(raw_text), NA, str_detect(raw_text, boilerplate_pattern))
    )
  }, error = function(e) {
    tibble(
      url = url,
      title = NA_character_,
      raw_text = NA_character_,
      text = NA_character_,
      text_length = NA_integer_,
      is_missing = TRUE,
      has_boilerplate = NA
    )
  })
}

# --------------------------------
# 6. Full scrape
# --------------------------------
scraped_full <- map_dfr(articles_keep$url, \(u) {
  Sys.sleep(1)
  get_article_text(u)
})

# --------------------------------
# 7. Merge text back to metadata
# --------------------------------
article_text_df <- articles_keep %>%
  left_join(scraped_full, by = "url")

# --------------------------------
# 8. Clean dataset
# --------------------------------
article_text_clean <- article_text_df %>%
  filter(!is_missing) %>%
  filter(!is.na(text_length), text_length > 1000) %>%
  filter(!has_boilerplate | is.na(has_boilerplate))

# --------------------------------
# 9. Save outputs
# --------------------------------
write_csv(article_text_df, "articles_scraped_raw.csv")
write_csv(article_text_clean, "articles_scraped_clean.csv")



# --------------------------------
# 10. Diagnostics
# --------------------------------
article_text_df %>%
  summarize(
    n_total = n(),
    n_missing = sum(is_missing, na.rm = TRUE),
    n_boilerplate = sum(has_boilerplate, na.rm = TRUE),
    n_clean = sum(!is_missing & text_length > 1000 & (!has_boilerplate | is.na(has_boilerplate)), na.rm = TRUE)
  )

article_text_df %>%
  mutate(keep_clean = !is_missing & text_length > 1000 & (!has_boilerplate | is.na(has_boilerplate))) %>%
  count(domain_clean, keep_clean, sort = TRUE)
```

```{r}
article_text_clean <- article_text_clean %>%
  distinct(url, .keep_all = TRUE)

article_text_clean <- article_text_clean %>%
  mutate(
    text = gsub("©\\s*picture.*", "", text),
    text = gsub("Lesezeit.*Min.*", "", text),
    text = gsub("\\[\\[.*?\\]\\]", "", text),
    text = stringr::str_squish(text)
  )

gabriel_input <- article_text_clean %>%
  transmute(
    id = row_number(),
    year = year,
    refugee_group = refugee_group,
    source = domain_clean,
    text = text
  )

closeAllConnections()
gc()

write_csv(gabriel_input, "~/Desktop/gabriel_input.csv")

write_csv(article_text_clean, "~/Desktop/articles_scraped_clean.csv")
```

Ukraine scrape

```{r}
library(dplyr)

articles_ukraine <- articles_keep %>%
  filter(refugee_group == "ukraine") %>%
  filter(!is.na(url)) %>%
  distinct(url, .keep_all = TRUE)

nrow(articles_ukraine)

library(dplyr)
library(stringr)
library(purrr)
library(rvest)
library(xml2)
library(tibble)
library(readr)

# --------------------------------
# 1. Keep all current news-source domains, Ukraine only
# --------------------------------
keep_domains <- c(
  "t-online.de",
  "tagesspiegel.de",
  "welt.de",
  "sueddeutsche.de",
  "faz.net",
  "focus.de",
  "spiegel.de",
  "tagesschau.de",
  "zeit.de",
  "jungewelt.de",
  "bild.de",
  "wallstreet-online.de",
  "unsere-zeit.de",
  "behoerden-spiegel.de",
  "kino-zeit.de"
)

articles_ukraine <- articles %>%
  filter(refugee_group == "ukraine") %>%
  filter(domain_clean %in% keep_domains) %>%
  filter(!is.na(url)) %>%
  distinct(url, .keep_all = TRUE)

# --------------------------------
# 2. Boilerplate patterns
# --------------------------------
boilerplate_pattern <- paste(
  c(
    "Artikel-Länge",
    "Uneingeschränkter Zugriff",
    "Jetzt abonnieren",
    "Mehr zum Thema",
    "Lesen Sie auch",
    "© dpa",
    "© picture alliance",
    "Datenschutzerklärung",
    "Impressum",
    "Newsletter",
    "Cookie"
  ),
  collapse = "|"
)

# --------------------------------
# 3. Cleaning function
# --------------------------------
clean_article_text <- function(text) {
  if (is.na(text)) return(NA_character_)
  
  text %>%
    str_replace_all("\\s+", " ") %>%
    str_replace_all("Artikel-Länge:.*?Zugriff", " ") %>%
    str_replace_all("Jetzt abonnieren.*", " ") %>%
    str_replace_all("Mehr zum Thema.*", " ") %>%
    str_replace_all("Lesen Sie auch.*", " ") %>%
    str_replace_all("©\\s*dpa.*", " ") %>%
    str_replace_all("©\\s*picture alliance.*", " ") %>%
    str_squish()
}

# --------------------------------
# 4. Scraper
# --------------------------------
get_article_text <- function(url) {
  tryCatch({
    page <- read_html(url)
    
    title <- page %>%
      html_element("title") %>%
      html_text2()

    text_parts <- page %>%
      html_elements("article p, main p, .article p, .entry-content p, .post-content p") %>%
      html_text2()

    if (length(text_parts) < 5) {
      text_parts <- page %>%
        html_elements("p") %>%
        html_text2()
    }

    raw_text <- str_squish(paste(text_parts, collapse = " "))
    clean_text <- clean_article_text(raw_text)

    tibble(
      url = url,
      title = ifelse(length(title) == 0, NA_character_, title),
      raw_text = raw_text,
      text = clean_text,
      text_length = ifelse(is.na(clean_text), NA_integer_, nchar(clean_text)),
      is_missing = is.na(clean_text) | clean_text == "",
      has_boilerplate = ifelse(is.na(raw_text), NA, str_detect(raw_text, boilerplate_pattern))
    )
  }, error = function(e) {
    tibble(
      url = url,
      title = NA_character_,
      raw_text = NA_character_,
      text = NA_character_,
      text_length = NA_integer_,
      is_missing = TRUE,
      has_boilerplate = NA
    )
  })
}

# --------------------------------
# 6. Full scrape, Ukraine only
# --------------------------------
scraped_ukraine <- map_dfr(articles_ukraine$url, \(u) {
  Sys.sleep(1)
  get_article_text(u)
})

# --------------------------------
# 7. Merge text back to metadata
# --------------------------------
article_text_ukraine_df <- articles_ukraine %>%
  left_join(scraped_ukraine, by = "url")

# --------------------------------
# 8. Clean dataset
# --------------------------------
article_text_ukraine_clean <- article_text_ukraine_df %>%
  filter(!is_missing) %>%
  filter(!is.na(text_length), text_length > 1000) %>%
  filter(!has_boilerplate | is.na(has_boilerplate))

# --------------------------------
# 9. Save outputs
# --------------------------------
write_csv(article_text_ukraine_df, "articles_ukraine_scraped_raw.csv")
write_csv(article_text_ukraine_clean, "articles_ukraine_scraped_clean.csv")ading Scored data
```

Loading Scored Data

```{r}
ratings <- read.csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/5000_RATINGS/checkpoint.csv")

library(dplyr)
library(ggplot2)

ratings %>%
  group_by(year, refugee_type) %>%
  summarise(
    avg_sentiment = mean(anti_immigration_sentiment, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = year, y = avg_sentiment, color = refugee_type)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_color_manual(values = c(
    "Ukrainian" = "steelblue",
    "Syrian" = "darkred"
  )) +
  labs(
    title = "Average Anti-Immigration Sentiment by Refugee Group",
    x = "Year",
    y = "Average Sentiment",
    color = "Refugee Group"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    legend.position = "bottom",
    panel.grid.minor = element_blank()
  )
```

```{r}
ukraine_media <- read.csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Newspaper Data/Ukraine_news_final.csv")

syria_media <- read.csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Newspaper Data/Syria_new_news.csv")

new_extracted <- read.csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Newspaper Data/new_extracted_articles_SAMPLE_5000.csv")
unique(new_extracted$refugee_group)
```

```{r}
before_scoring <- read.csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Newspaper Data/new_extracted_articles_2015_2025.csv")
all_scored <- read.csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Newspaper Data/new_extracted_articles_2015_2025.csv") 


all_scored <- all_scored %>%
  select(-ends_with("_x")) %>%
  rename_with(~ gsub("_y$", "", .x))

library(dplyr)
library(ggplot2)

all_scored %>%
  group_by(year, refugee_type) %>%
  summarise(avg_sentiment = mean(anti_immigration_sentiment, na.rm = TRUE),
            .groups = "drop") %>%
  ggplot(aes(x = year, y = avg_sentiment, color = refugee_type)) +
  geom_line(size = 1.2) +
  geom_point() +
  labs(
    title = "Anti-Immigration Sentiment by Year",
    x = "Year",
    y = "Average Sentiment",
    color = "Refugee Type"
  ) +
  theme_minimal()
```

Regressions/Tests

```{r}
model_fe2 <- feols(
  anti_immigration_sentiment ~ refugee_type | year + SourceCommonName,
  data = ratings
)

summary(model_fe2)

model_event <- feols(
  anti_immigration_sentiment ~ post_2022 * refugee_type | year + SourceCommonName,
  cluster = ~SourceCommonName,
  data = ratings
)

summary(model_event)

library(modelsummary)
library(gt)

fe_rows <- data.frame(
  term = c("Source FE", "Year FE"),
  Baseline = c("Yes", "Yes"),
  `Post-2022 Interaction` = c("Yes", "Yes"),
  check.names = FALSE
)

modelsummary(
  list(
    "Baseline" = model_fe2,
    "Post-2022 Interaction" = model_event
  ),
  coef_map = c(
    "refugee_typeUkrainian" = "Ukrainian (vs. Syrian)",
    "post_2022:refugee_typeUkrainian" = "Post-2022 × Ukrainian"
  ),
  add_rows = fe_rows,
  gof_omit = ".*",
  stars = TRUE,
  statistic = "({std.error})",
  output = "gt"
) |>
  tab_header(
    title = "Media Sentiment Regressions"
  ) |>
  tab_source_note(
    source_note = "Standard errors in parentheses."
  ) |>
  tab_options(
    table.font.names = "Times New Roman"
  )
```

Nice Plot

```{r}
library(broom)
library(dplyr)
library(ggplot2)

coef_plot_data <- bind_rows(
  tidy(model_fe2, conf.int = TRUE) %>%
    mutate(model = "Baseline"),
  tidy(model_event, conf.int = TRUE) %>%
    mutate(model = "Post-2022 Interaction")
) %>%
  filter(term %in% c(
    "refugee_typeUkrainian",
    "post_2022:refugee_typeUkrainian"
  )) %>%
  mutate(
    coefficient = recode(
      term,
      "refugee_typeUkrainian" = "Ukrainian vs. Syrian",
      "post_2022:refugee_typeUkrainian" = "Post-2022 × Ukrainian"
    ),
    model = factor(model, levels = c("Baseline", "Post-2022 Interaction"))
  )

ggplot(coef_plot_data, aes(x = estimate, y = coefficient, color = coefficient)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.15, size = 1) +
  facet_wrap(~ model, ncol = 1) +
  scale_color_manual(values = c(
    "Ukrainian vs. Syrian" = "#5AAE61",        # dark green
    "Post-2022 × Ukrainian" = "#1B7837"       # lighter green
  )) +
  labs(
    title = "Media Sentiment Toward Refugees: Baseline and Post-2022 Estimates",
    x = "Effect on Anti-Immigration Sentiment (95% CI)",
    y = NULL,
    color = NULL
  ) +
  theme_minimal(base_family = "Times New Roman") +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 16),
    strip.text = element_text(face = "bold", size = 13),
    legend.position = "bottom"
  )
```

More regressions

```{r}
model_fe <- feols(
  anti_immigration_sentiment ~ refugee_type | year,
  data = ratings
)

summary(model_fe)

model_fe2 <- feols(
  anti_immigration_sentiment ~ refugee_type | year + SourceCommonName,
  data = ratings
)

summary(model_fe2)
```

Post-2022

```{r}
ratings <- ratings %>%
  mutate(post_2022 = ifelse(year >= 2022, 1, 0))

library(fixest)

model_fe2 <- feols(
  anti_immigration_sentiment ~ refugee_type | year + SourceCommonName,
  data = ratings
)

summary(model_fe2)

model_event <- feols(
  anti_immigration_sentiment ~ post_2022 * refugee_type | year + SourceCommonName,
  cluster = ~SourceCommonName,
  data = ratings
)

summary(model_event)
```

```{r}
ratings <- ratings %>%
  mutate(
    post_2015 = ifelse(year >= 2015, 1, 0),
    post_2022 = ifelse(year >= 2022, 1, 0)
  )

model_multi <- feols(
  anti_immigration_sentiment ~ 
    post_2015 * refugee_type +
    post_2022 * refugee_type |
    year + SourceCommonName,
  cluster = ~SourceCommonName,
  data = ratings
)

summary(model_multi)
```

# Outlets and Mapping

```{r}
library(dplyr)
library(tidyr)

# German Bundesländer names
regions <- c(
  "Baden-Württemberg","Bayern","Berlin","Brandenburg","Bremen","Hamburg",
  "Hessen","Mecklenburg-Vorpommern","Niedersachsen","Nordrhein-Westfalen",
  "Rheinland-Pfalz","Saarland","Sachsen","Sachsen-Anhalt",
  "Schleswig-Holstein","Thüringen"
)

# --- Regional outlets ---
regional_map <- tibble::tibble(
  SourceCommonName = c(
    "berliner-zeitung.de","tagesspiegel.de","morgenpost.de",
    "rp-online.de","express.de",
    "tz.de","merkur.de"
  ),
  region = c(
    "Berlin","Berlin","Berlin",
    "Nordrhein-Westfalen","Nordrhein-Westfalen",
    "Bayern","Bayern"
  ),
  weight = 1,
  scope = "regional"
)

# --- National outlets ---
national_outlets <- c(
  "bild.de","faz.net","focus.de","fr.de",
  "n-tv.de","spiegel.de","stern.de",
  "sueddeutsche.de","newsticker.sueddeutsche.de",
  "t-online.de","welt.de","zeit.de"
)

# Equal-weight distribution across regions
national_map <- expand.grid(
  SourceCommonName = national_outlets,
  region = regions
) %>%
  as_tibble() %>%
  mutate(
    weight = 1 / length(regions),
    scope = "national"
  )

# Combine
full_mapping <- bind_rows(regional_map, national_map)


```

Old data loading

```{r}
Iv_election_panel_state <- read.csv("/Users/diananichvoloda/Desktop/iv_total_new.csv")

library(dplyr)

state_labels <- c(
  "1"  = "Schleswig-Holstein",
  "2"  = "Hamburg",
  "3"  = "Niedersachsen",
  "4"  = "Bremen",
  "5"  = "Nordrhein-Westfalen",
  "6"  = "Hessen",
  "7"  = "Rheinland-Pfalz",
  "8"  = "Baden-Württemberg",
  "9"  = "Bayern",
  "10" = "Saarland",
  "11" = "Berlin",
  "12" = "Brandenburg",
  "13" = "Mecklenburg-Vorpommern",
  "14" = "Sachsen",
  "15" = "Sachsen-Anhalt",
  "16" = "Thüringen"
)

panel_filtered <- iv_election_panel_state %>%
  filter(year >= 2017)


```

Ratings data

```{r}
library(dplyr)

ratings_mapped <- ratings %>%
  left_join(full_mapping, by = "SourceCommonName")

sentiment_clean <- ratings_mapped %>%
  mutate(
    election_year = case_when(
      year >= 2015 & year <= 2017 ~ 2017,
      year >= 2018 & year <= 2021 ~ 2021,
      year >= 2022 & year <= 2025 ~ 2025,
      TRUE ~ NA_real_
    ),
    time_weight = case_when(
      election_year == 2017 ~ year - 2015 + 1,
      election_year == 2021 ~ year - 2018 + 1,
      election_year == 2025 ~ year - 2022 + 1,
      TRUE ~ NA_real_
    ),
    final_weight = weight * time_weight
  ) %>%
  filter(!is.na(election_year)) %>%
  group_by(region, election_year, refugee_group) %>%
  summarise(
    avg_anti_immigration_sentiment =
      weighted.mean(anti_immigration_sentiment, final_weight, na.rm = TRUE),
    n_articles = n_distinct(url),
    .groups = "drop"
  )

library(tidyr)

sentiment_wide <- sentiment_clean %>%
  select(region, election_year, refugee_group, avg_anti_immigration_sentiment) %>%
  pivot_wider(
    names_from = refugee_group,
    values_from = avg_anti_immigration_sentiment,
    names_prefix = "sentiment_"
  )
```

County elections

```{r}
final_data <- panel_filtered %>%
  left_join(
    sentiment_wide,
    by = c("state_name" = "region", "year" = "election_year")
  )
```

Regression

```{r}
model <- feols(
  afd ~ sentiment_syria + sentiment_ukraine |
    AGS + year,
  cluster = ~state_name,
  data = final_data
)

summary(model)

library(modelsummary)
library(gt)

fe_rows <- data.frame(
  term = c("State FE", "Year FE"),
  Model = c("Yes", "Yes"),
  check.names = FALSE
)

modelsummary(
  list("AfD vote share" = model),
  coef_map = c(
    "sentiment_syria" = "Sentiment (Syrian refugees)",
    "sentiment_ukraine" = "Sentiment (Ukrainian refugees)"
  ),
  gof_omit = ".*",
  add_rows = fe_rows,
  stars = TRUE,
  statistic = "({std.error})",
  output = "gt"
) |>
  tab_header(
    title = "Media Sentiment and AfD Vote Share"
  ) |>
  tab_source_note(
    source_note = "Standard errors clustered at the state level."
  ) |>
  tab_options(
    table.font.names = "Times New Roman"
  )
```

```{r}
model <- feols(
  sentiment_syria ~ syria_per_voter |
    AGS + year,
  cluster = ~state_name,
  data = final_data
)

summary(model)
```

```{r}
model_s <- feols(
  sentiment_syria ~ syria_per_voter |
    AGS + year,
  cluster = ~state_name,
  data = final_data
)

summary(model_s)

model_u <- feols(
  sentiment_ukraine ~ ukraine_per_voter |
    AGS + year,
  cluster = ~state_name,
  data = final_data
)

summary(model_u)

library(modelsummary)
library(gt)

fe_rows <- data.frame(
  term = c("State FE", "Year FE"),
  `Syrian Sentiment` = c("Yes", "Yes"),
  `Ukrainian Sentiment` = c("Yes", "Yes"),
  check.names = FALSE
)

modelsummary(
  list(
    "Syrian Sentiment" = model_s,
    "Ukrainian Sentiment" = model_u
  ),
  coef_map = c(
    "syria_per_voter" = "Syrian refugees per voter",
    "ukraine_per_voter" = "Ukrainian refugees per voter"
  ),
  add_rows = fe_rows,
  gof_omit = ".*",
  stars = TRUE,
  statistic = "({std.error})",
  output = "gt"
) |>
  tab_header(
    title = "Local Refugee Presence and Media Sentiment"
  ) |>
  tab_source_note(
    source_note = "Standard errors clustered at the state level."
  ) |>
  tab_options(
    table.font.names = "Times New Roman"
  )
```

Sentiment for Syria + AfD

```{r}
model <- feols(
  afd ~ sentiment_syria * syria_per_voter |
    AGS + year,
  cluster = ~state_name,
  data = final_data
)

summary(model)
```

Sentiment for Ukraine + AfD

```{r}
model <- feols(
  afd ~ sentiment_ukraine * ukraine_per_voter |
    AGS + year,
  cluster = ~state_name,
  data = final_data
)

summary(model)
```

Sentiment Gap

```{r}
final_data <- final_data %>%
  mutate(
    sentiment_gap = sentiment_syria - sentiment_ukraine
  )

model_gap <- feols(
  afd ~ sentiment_gap + syria_per_voter + ukraine_per_voter |
    AGS + year,
  cluster = ~state_name,
  data = final_data
)

summary(model_gap)

library(modelsummary)
library(gt)

fe_rows <- data.frame(
  term = c("State FE", "Year FE"),
  Model = c("Yes", "Yes"),
  check.names = FALSE
)

modelsummary(
  list("AfD vote share" = model_gap),
  coef_map = c(
    "sentiment_gap" = "Sentiment gap (Syria − Ukraine)",
    "syria_per_voter" = "Syrian refugees per voter",
    "ukraine_per_voter" = "Ukrainian refugees per voter"
  ),
  add_rows = fe_rows,
  gof_omit = ".*",
  stars = TRUE,
  statistic = "({std.error})",
  output = "gt"
) |>
  tab_header(
    title = "Media Sentiment, Refugee Inflows, and AfD Vote Share"
  ) |>
  tab_source_note(
    source_note = "Standard errors clustered at the state level."
  ) |>
  tab_options(
    table.font.names = "Times New Roman"
  )
```

```{r}
library(dplyr)

plot_data <- final_data %>%
  group_by(year) %>%
  summarise(
    sentiment_gap = mean(sentiment_gap, na.rm = TRUE),
    afd = mean(afd, na.rm = TRUE)
  )

ggplot(plot_data, aes(x = year)) +
  geom_line(aes(y = sentiment_gap, color = "Sentiment Gap"), size = 1.2) +
  geom_point(aes(y = sentiment_gap, color = "Sentiment Gap")) +
  
  geom_line(aes(y = afd, color = "AfD Vote Share"), size = 1.2, linetype = "dashed") +
  geom_point(aes(y = afd, color = "AfD Vote Share")) +
  
  labs(
    title = "Media Sentiment Gap and AfD Vote Share Over Time",
    x = "Year",
    y = "Value",
    color = ""
  ) +
  theme_minimal()
```

Yearly Plot

```{r}
library(dplyr)
library(ggplot2)

library(tidyr)

yearly_gap <- yearly_sentiment %>%
  pivot_wider(
    names_from = refugee_group,
    values_from = sentiment
  ) %>%
  mutate(
    sentiment_gap = syria - ukraine
  )

ggplot(yearly_gap, aes(x = year, y = sentiment_gap)) +
  geom_line(color = "darkblue", size = 1.2) +
  geom_point() +
  labs(
    title = "Sentiment Gap (Syria - Ukraine) Over Time",
    x = "Year",
    y = "Sentiment Gap"
  ) +
  theme_minimal()
```

Regional breakdowns

```{r}
regional_sentiment <- ratings_mapped %>%
  group_by(region, year, refugee_group) %>%
  summarise(
    sentiment = weighted.mean(anti_immigration_sentiment, weight, na.rm = TRUE),
    .groups = "drop"
  )

ggplot(regional_sentiment, aes(x = year, y = sentiment, color = refugee_group)) +
  geom_line() +
  facet_wrap(~region) +
  scale_x_continuous(
    breaks = c(2015, 2018, 2021, 2025),
    labels = c("'15", "'18", "'21", "'25")
  ) +
  theme_minimal() +
  labs(
    title = "Sentiment by Region and Refugee Group",
    x = "Year",
    y = "Sentiment"
  )
```

```{r}


model_gap <- feols(
  sentiment_syria ~ z_syria_2008_per_voter |
    AGS + year,
  cluster = ~state_name,
  data = final_data
)

summary(model_gap)
```

# More graphs

Unemployment

```{r}
library(ggplot2)
library(dplyr)

df <- data.frame(
  origin = rep(c("Syria", "Ukraine"), each = 3),
  unemployment = rep(c(4.275, 6.300, 9.600), 2),
  effect = c(-0.324, -0.150, 0.134, -0.780, -0.534, -0.132)
)

ggplot(df, aes(x = unemployment, y = effect, color = origin)) +
  geom_line(size = 1.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_manual(values = c(
    "Syria" = "#B22222",    # red
    "Ukraine" = "#2C7FB8"   # blue
  )) +
  labs(
    title = "Effect of Refugee Inflows on AfD Vote Share Across Unemployment Levels",
    x = "Unemployment Rate (%)",
    y = "Marginal Effect on AfD Vote Share",
    color = "Refugee Origin"
  ) +
  theme_minimal(base_family = "Times New Roman") +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "bottom"
  )
```

Income

```{r}
library(ggplot2)
library(dplyr)

df_income <- data.frame(
  origin = rep(c("Syria", "Ukraine"), each = 3),
  income = rep(c(105.664, 149.386, 236.513), 2),
  effect = c(0.176, 0.115, -0.006, -0.048, -0.137, -0.315)
)

ggplot(df_income, aes(x = income, y = effect, color = origin)) +
  geom_line(size = 1.2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_manual(values = c(
    "Syria" = "#B22222",    # red
    "Ukraine" = "#2C7FB8"   # blue
  )) +
  labs(
    title = "Effect of Refugee Inflows on AfD Vote Share Across Income Levels",
    x = "Disposable Household Income (thousands of euros)",
    y = "Marginal Effect on AfD Vote Share",
    color = "Refugee Origin"
  ) +
  theme_minimal(base_family = "Times New Roman") +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    legend.position = "bottom"
  )
```
