---
title: "Final Project"
author: "Diana Nichvoloda"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
library(dplyr)
library(tidyverse)
library(kableExtra)
library(lmtest)
library(ggplot2)
library(fixest)
library(lfe)
#rm(list=ls())
options(tibble.width = Inf)
options(width = 200)
```

```{r preliminaries, echo=FALSE}
rm(list=ls()) #clean out memory 
```

# Federal Election data - municipal level (2013, 2017, 2021, 2025)

```{r}
library(readr)
library(haven)

fed_muni <- readRDS("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/federal_muni_harm_25.rds")

years_keep <- c(2013, 2017, 2021, 2025)

fed_muni <- fed_muni %>%
  filter(election_year %in% years_keep)

#Renaming
fed_muni <- fed_muni %>%
  rename(
    municipality = ags,
    year = election_year,
  )

#Getting rid of excess columns 
fed_muni <- fed_muni %>%
  select(
    -unique_mailin,
    -unique_multi_mailin,
    -eligible_voters_orig, 
    -number_voters_orig,
    -invalid_votes, 
    -voters_wo_blockingnotice,
    -voters_blockingnotice,
    -voters_par25_2,
    -blocked_voters_orig,
    -voters_w_ballot, 
    -turnout_wo_mailin,
    -pop_weight,
    -area_weight,
    -blocked_weight,
    -voters_weight
  )

# --- 1) Define which parties you want to KEEP (main parties + outcome) ---
keep_parties <- c(
  "afd",
  "cdu", "csu", "spd", "gruene", "fdp",
  "linke_pds"   # or whatever your Left-party column is named
)

# --- 2) Define which parties should count toward "far_right" (if they exist) ---
far_right_parts <- c("afd", "npd", "rep", "die_rechte", "dvu", "iii_weg")

# --- 3) Clean: keep only needed non-party vars + the party vars above ---
# (adjust these non-party vars to match your dataset)
keep_nonparty <- c(
  "municipality", "county", "state", "year",
  "eligible_voters", "number_voters", "valid_votes", "turnout"
)

fed_muni_clean <- fed_muni %>%
  # keep only columns that exist in your data
  select(any_of(c(keep_nonparty, keep_parties, far_right_parts))) %>%
  # ensure party shares are numeric
  mutate(across(any_of(unique(c(keep_parties, far_right_parts))), as.numeric)) %>%
  # create far_right (row-wise sum across whatever far-right columns exist)
  rowwise() %>%
  mutate(
    far_right = sum(c_across(any_of(far_right_parts)), na.rm = TRUE)
  ) %>%
  ungroup() 

fed_muni_clean <- fed_muni_clean %>%
  mutate(union = cdu + csu)
fed_muni_clean <- fed_muni_clean %>%
  select(-csu)

fed_muni_clean <- fed_muni_clean %>%
    # OPTIONAL: drop the micro far-right components after constructing far_right
  # (keeps afd + far_right + major parties)
  select(-any_of(setdiff(far_right_parts, "afd")))

# fed_muni_clean now contains:
# key vars + turnout/votes + {afd, cdu, csu, spd, gruene, fdp, linke_pds} + far_right

#Aggregating by county

share_vars <- c("afd","cdu","spd","gruene","fdp","linke_pds","far_right","union")

fed_county <- fed_muni_clean %>%
  filter(!is.na(valid_votes), valid_votes > 0) %>%
  mutate(across(all_of(share_vars), ~ .x * valid_votes, .names = "{.col}_votes")) %>%
  group_by(county, state, year) %>%
  summarise(
    eligible_voters = sum(eligible_voters, na.rm = TRUE),
    number_voters   = sum(number_voters,   na.rm = TRUE),
    valid_votes     = sum(valid_votes,     na.rm = TRUE),
    across(ends_with("_votes"), ~ sum(.x, na.rm = TRUE)),
    .groups = "drop"
  ) %>%
  mutate(
    turnout = number_voters / eligible_voters,
    across(ends_with("_votes"), ~ .x / valid_votes,
           .names = "{sub('_votes$', '', .col)}")
  ) %>%
  select(county, state, year, eligible_voters, number_voters, valid_votes, turnout,
         all_of(share_vars))
```

```{r}
#install.packages("gerda")
library(gerda)
codebook <- gerda_covariates_codebook()
print(codebook)
```

Data on 2013, 2017, 2021, and 2025 federal elections by municipality

# Parliamentary Elections

2024

```{r}
library(readr)
library(dplyr)

EU_Parliamentary2024 <- read_delim(
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/EU Parliament by district2024.csv",
  delim = ";",
  locale = locale(encoding = "UTF-8"),
  skip = 9,
  show_col_types = FALSE
)

EU_Parliamentary2024 <- EU_Parliamentary2024 %>%
  rename(
    election_type        = Wahlart,
    election_date        = Wahltag,
    region_type          = Gebietsart,
    region_code          = Gebietsnummer,
    region_name          = Gebietsname,
    higher_region_type   = UegGebietsart,
    higher_region_code   = UegGebietsnummer,
    group_type           = Gruppenart,
    party                = Gruppenname,
    group_order          = Gruppenreihenfolge,
    vote_type            = Stimme,
    votes                = Anzahl,
    vote_share_percent   = Prozent,
    prev_votes           = VorpAnzahl,
    prev_vote_share      = VorpProzent,
    diff_percent         = DiffProzent,
    diff_percentage_pts  = DiffProzentPkt,
    notes                = Bemerkung
  )

ep_afd_2024 <- EU_Parliamentary2024 %>%
  filter(
    region_type == "Kreis",
    group_type == "Partei",
    party == "AfD",
    vote_type == 1
  ) %>%
  mutate(
    vote_share_percent = as.numeric(gsub(",", ".", vote_share_percent)),
    afd_share = vote_share_percent / 100,
    year = 2024L,
    ags = as.character(region_code)
  ) %>%
  select(ags, year, afd_share)

ep_eligible_2024 <- EU_Parliamentary2024 %>%
  filter(
    region_type == "Kreis",
    group_type == "System-Gruppe",
    party == "Wahlberechtigte"
  ) %>%
  mutate(
    eligible_voters = as.numeric(gsub(",", ".", votes)),
    ags = as.character(region_code),
    year = 2024L
  ) %>%
  select(ags, year, eligible_voters)

ep_panel_2024 <- ep_afd_2024 %>%
  left_join(ep_eligible_2024, by = c("ags", "year"))
```

2019

```{r}
EU_Parliamentary2019 <- read_delim(
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/EU_parliamentary/ew2019_kerg2.csv",
  delim = ";",
  locale = locale(encoding = "UTF-8"),
  skip = 9,
  show_col_types = FALSE
)

EU_Parliamentary2019 <- EU_Parliamentary2019 %>%
  rename(
    election_type        = Wahlart,
    election_date        = Wahltag,
    region_type          = Gebietsart,
    region_code          = Gebietsnummer,
    region_name          = Gebietsname,
    higher_region_type   = UegGebietsart,
    higher_region_code   = UegGebietsnummer,
    group_type           = Gruppenart,
    party                = Gruppenname,
    group_order          = Gruppenreihenfolge,
    vote_type            = Stimme,
    votes                = Anzahl,
    vote_share_percent   = Prozent,
    prev_votes           = VorpAnzahl,
    prev_vote_share      = VorpProzent,
    diff_percent         = DiffProzent,
    diff_percentage_pts  = DiffProzentPkt,
    notes                = Bemerkung
  )

ep_afd_2019 <- EU_Parliamentary2019 %>%
  filter(
    region_type == "Kreis",
    group_type == "Partei",
    party == "AfD",
    vote_type == 1
  ) %>%
  mutate(
    vote_share_percent = as.numeric(gsub(",", ".", vote_share_percent)),
    afd_share = vote_share_percent / 100,
    year = 2019L,
    ags = as.character(region_code)
  ) %>%
  select(ags, year, afd_share)

ep_eligible_2019 <- EU_Parliamentary2019 %>%
  filter(
    region_type == "Kreis",
    group_type == "System-Gruppe",
    party == "Wahlberechtigte"
  ) %>%
  mutate(
    eligible_voters = as.numeric(gsub(",", ".", votes)),
    ags = as.character(region_code),
    year = 2019L
  ) %>%
  select(ags, year, eligible_voters)

ep_panel_2019 <- ep_afd_2019 %>%
  left_join(ep_eligible_2019, by = c("ags", "year"))
```

2014

```{r}
EU_Parliamentary2014_raw <- read_delim(
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/EU_parliamentary/ew2014_kerg.csv",
  delim = ";",
  locale = locale(encoding = "Latin1"),
  skip = 5,
  col_names = FALSE,
  show_col_types = FALSE,
  trim_ws = TRUE
)

header1 <- as.character(EU_Parliamentary2014_raw[1, ])
header2 <- as.character(EU_Parliamentary2014_raw[2, ])

header1[is.na(header1)] <- ""
header2[is.na(header2)] <- ""

col_names <- ifelse(
  header1 == "",
  header2,
  ifelse(
    header2 == "",
    header1,
    paste(header1, header2, sep = "_")
  )
)

col_names <- col_names %>%
  str_replace_all("[[:space:]]+", "_") %>%
  str_replace_all("[^[:alnum:]_]", "") %>%
  str_to_lower()

col_names[col_names == ""] <- paste0("x", which(col_names == ""))

EU_Parliamentary2014 <- EU_Parliamentary2014_raw[-c(1, 2), ]
names(EU_Parliamentary2014) <- make.unique(col_names)

EU_Parliamentary2014 <- EU_Parliamentary2014 %>%
  mutate(across(everything(), ~ type.convert(as.character(.x), as.is = TRUE)))

names(EU_Parliamentary2014)

ep_afd_2014 <- EU_Parliamentary2014 %>%
  transmute(
    ags = str_pad(as.character(nr), width = 5, side = "left", pad = "0"),
    region_name = gebiet,
    higher_region = `gehört_zu`,
    year = 2014,
    eligible_voters = as.numeric(`wahlberechtigte_endgültig`),
    valid_votes = as.numeric(`gültige_endgültig`),
    afd_votes = as.numeric(`afd_endgültig`),
    afd_share = afd_votes / valid_votes
  ) %>%
  filter(higher_region != 99) %>%
  select(ags, year, afd_share, eligible_voters)

ep_panel <- bind_rows(
  ep_afd_2014,
  ep_panel_2019,
  ep_panel_2024
) %>%
  arrange(ags, year)

count(ep_panel, year)

ep_panel %>%
  arrange(ags, year) %>%
  print(n = 20)
```

# Refugee/Asylum seeker data

```{r}
library(readxl)

Genesis <- read_excel("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/12531-0043_en.xlsx", skip = 5)

#Getting rid of excess columns 
Genesis <- Genesis %>%
  select(
    -5,
    -7,
    -9,
    -11,
    -13,
    -15,
    -17,
    -19,
    -21,
    -23,
    -25,
    -27,
    -29,
    -31,
    -33,
    -35,
    -37,
    -39,
    -41,
    -43
  )

library(dplyr)
library(stringr)

male_cols   <- grep("^Male",   names(Genesis), value = TRUE)
female_cols <- grep("^Female", names(Genesis), value = TRUE)

Genesis2 <- Genesis %>%
  mutate(
    across(all_of(c(male_cols, female_cols)),
           ~ as.numeric(replace(as.character(.x), .x == "-", NA)))
  ) %>%
  mutate(
    Male   = rowSums(across(all_of(male_cols)),   na.rm = TRUE),
    Female = rowSums(across(all_of(female_cols)), na.rm = TRUE)
  ) %>%
  select(-all_of(c(male_cols, female_cols)))

dates_in_col1 <- Genesis2$`...1`[grepl("^\\d{4}-\\d{2}-\\d{2}$", Genesis2$`...1`)]
sort(unique(dates_in_col1))
length(unique(dates_in_col1))
```

```{r}
Genesis_2007 <- read_excel("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Ukraine/Ukraine_2007.xlsx", skip = 5)

Genesis_2015 <- read_excel("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Ukraine/Ukraine_2015.xlsx", skip = 5)

```

# Ukraine - Panel Data

```{r}
library(readxl)
library(dplyr)
library(stringr)
library(purrr)

files <- list.files(
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Ukraine/",
  pattern = "Ukraine_.*\\.xlsx$",
  full.names = TRUE
)

files

ukraine_panel <- map_dfr(files, function(f) {
  
  # Extract year from filename
  year <- str_extract(basename(f), "\\d{4}") %>% as.numeric()
  
  # Read file (adjust skip if needed)
  df <- read_excel(f, skip = 5)
  
  # Add year column
  df <- df %>%
    mutate(year = year)
  
  return(df)
})

ukraine_panel <- ukraine_panel %>%
  relocate(year, .after = 2)

ukraine_panel <- ukraine_panel %>%
  rename(AGS = `...1`) %>%
  rename(Country = `...3`) 

ukraine_panel <- ukraine_panel %>%
  rename(AGS_name = `...2`) 

ukraine_panel <- ukraine_panel %>%
  mutate(AGS = as.character(AGS))

ukraine_panel <- ukraine_panel %>%
  filter(grepl("^\\d{5}$", AGS))

#Summing male and female
ukraine_panel <- ukraine_panel %>%
  # Replace "-" with NA
  mutate(across(matches("^Male|^Female"),
                ~na_if(.x, "-"))) %>%
  
  # Convert to numeric
  mutate(across(matches("^Male|^Female"),
                as.numeric))

ukraine_panel <- ukraine_panel %>%
  mutate(
    Ukraine_total = rowSums(across(matches("^Male|^Female")),
                            na.rm = TRUE)
  )

ukraine_panel <- ukraine_panel %>%
  select(AGS, AGS_name, year, Country, Ukraine_total)
```

# Syria - Panel Data

```{r}
library(readxl)
library(dplyr)
library(stringr)
library(purrr)

files <- list.files(
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Syria/",
  pattern = "Syria_.*\\.xlsx$",
  full.names = TRUE
)

files

syria_panel <- map_dfr(files, function(f) {
  
  # Extract year from filename
  year <- str_extract(basename(f), "\\d{4}") %>% as.numeric()
  
  # Read file (adjust skip if needed)
  df <- read_excel(f, skip = 5)
  
  # Add year column
  df <- df %>%
    mutate(year = year)
  
  return(df)
})

syria_panel <- syria_panel %>%
  relocate(year, .after = 2)

syria_panel <- syria_panel %>%
  rename(AGS = `...1`) %>%
  rename(Country = `...3`) 

syria_panel <- syria_panel %>%
  rename(AGS_name = `...2`) 

syria_panel <- syria_panel %>%
  mutate(AGS = as.character(AGS))

syria_panel <- syria_panel %>%
  filter(grepl("^\\d{5}$", AGS))

#Summing male and female
syria_panel <- syria_panel %>%
  # Replace "-" with NA
  mutate(across(matches("^Male|^Female"),
                ~na_if(.x, "-"))) %>%
  
  # Convert to numeric
  mutate(across(matches("^Male|^Female"),
                as.numeric))

syria_panel <- syria_panel %>%
  mutate(
    Syria_total = rowSums(across(matches("^Male|^Female")),
                            na.rm = TRUE)
  )

syria_panel <- syria_panel %>%
  select(AGS, AGS_name, year, Country, Syria_total)
```

# Merging

```{r}
syria_panel$AGS    <- as.character(syria_panel$AGS)
ukraine_panel$AGS  <- as.character(ukraine_panel$AGS)

syria_panel$year   <- as.numeric(syria_panel$year)
ukraine_panel$year <- as.numeric(ukraine_panel$year)

#syria_panel   <- syria_panel %>% select(-Country)
#ukraine_panel <- ukraine_panel %>% select(-Country)

refugee_panel <- full_join(
  syria_panel,
  ukraine_panel,
  by = c("AGS", "AGS_name", "year")
)

#refugee_panel <- refugee_panel %>%
  #mutate(
    #Syria_total    = ifelse(is.na(Syria_total), 0, Syria_total),
    #ukraine_total  = ifelse(is.na(ukraine_total), 0, Ukraine_total)
  #)

#For election synchronization
# =========================
# Refugee stocks -> 4-year "cumulative inflow" proxy (NET CHANGE) by election year
# Window = (t-4) ... t, implemented as Stock_t - Stock_(t-4)
# Election years: 2013, 2017, 2021, 2025
# =========================

library(dplyr)

# ---- 0) Set election years ----
election_years <- c(2013L, 2017L, 2021L, 2025L)

# ---- 1) Clean refugee panel types (AGS as 5-char string, year as integer) ----
# Assumes refugee_panel has columns: AGS, year, Syria_total, Ukraine_total
refugee_panel_clean <- refugee_panel %>%
  mutate(
    AGS = sprintf("%05s", as.character(AGS)),
    ref_year = as.integer(as.character(year))
  ) %>%
  select(AGS, ref_year, Syria_total, Ukraine_total)

# ---- 2) Get stocks at election year t (but for 2025 use 2024 as the last available refugee year) ----
stock_t <- refugee_panel_clean %>%
  filter(ref_year %in% c(2013L, 2017L, 2021L, 2024L)) %>%  # 2025 -> use 2024
  transmute(
    AGS,
    elec_year = if_else(ref_year == 2024L, 2025L, ref_year),  # relabel 2024 as election year 2025
    syria_stock_t = Syria_total,
    ukraine_stock_t = Ukraine_total
  ) %>%
  filter(elec_year %in% election_years)

# ---- 3) Get stocks at (t-4) for 2013/2017/2021, and at (2021) for 2025 (i.e., 3-year diff: 2024 - 2021) ----
stock_t4 <- refugee_panel_clean %>%
  filter(ref_year %in% c(2009L, 2013L, 2017L, 2021L)) %>%
  transmute(
    AGS,
    elec_year = ref_year + 4L,                               # 2009->2013, 2013->2017, 2017->2021, 2021->2025
    syria_stock_t4 = Syria_total,
    ukraine_stock_t4 = Ukraine_total
  ) %>%
  filter(elec_year %in% election_years)

# ---- 4) Compute net change:
# 2013/2017/2021: Stock_t - Stock_(t-4)
# 2025:           Stock_2024 - Stock_2021  (since last refugee year is 2024)
ref_4yr_net <- stock_t %>%
  left_join(stock_t4, by = c("AGS", "elec_year")) %>%
  mutate(
    syria_net_4yr = syria_stock_t - syria_stock_t4,
    ukraine_net_4yr = ukraine_stock_t - ukraine_stock_t4,
    window_years = if_else(elec_year == 2025L, 3L, 4L)        # optional: keeps track of window length
  ) %>%
  select(
    AGS,
    year = elec_year,
    syria_net_4yr,
    ukraine_net_4yr,
    window_years
  )

# ---- 5) Clean election panel key + merge ----
# Assumes fed_county has columns: county (or AGS) and year
election_panel_clean <- fed_county %>%
  mutate(
    AGS = sprintf("%05s", as.character(county)),
    year = as.integer(as.character(year))
  )

merged_panel <- election_panel_clean %>%
  left_join(ref_4yr_net, by = c("AGS", "year"))

merged_panel <- merged_panel %>%
  relocate(AGS, .after = 1) %>%
  relocate(syria_net_4yr, .after = 2) %>%
  relocate(ukraine_net_4yr, .after = 3) 

merged_panel <- merged_panel %>%
  relocate(state, .after = 6)
```

\*\*Leading up to 2025 we only use refugee net inflow from 2021 to 2024, since that is the last available year of the Genesis data

EP Elections

```{r}
library(dplyr)

# ---- 0) Define EP election years and their baseline years ----
ep_year_map <- tibble(
  year = c(2014L, 2019L, 2024L),
  base_year = c(2010L, 2015L, 2020L)
)

# ---- 1) Clean refugee panel ----
refugee_panel_clean <- refugee_panel_clean %>%
  mutate(
    AGS = sprintf("%05s", as.character(AGS)),
    ref_year = as.integer(ref_year)
  ) %>%
  select(AGS, ref_year, Syria_total, Ukraine_total)

# ---- 2) Get stock at election year t ----
stock_t <- refugee_panel_clean %>%
  inner_join(ep_year_map, by = c("ref_year" = "year")) %>%
  transmute(
    AGS,
    year = ref_year,
    syria_stock_t = Syria_total,
    ukraine_stock_t = Ukraine_total,
    base_year
  )

# ---- 3) Get stock at baseline (t-4) ----
stock_t4 <- refugee_panel_clean %>%
  rename(base_year = ref_year) %>%
  select(AGS, base_year, Syria_total, Ukraine_total) %>%
  rename(
    syria_stock_t4 = Syria_total,
    ukraine_stock_t4 = Ukraine_total
  )

# ---- 4) Compute 4-year net inflows ----
ref_4yr_net <- stock_t %>%
  left_join(stock_t4, by = c("AGS", "base_year")) %>%
  mutate(
    syria_net_4yr = syria_stock_t - syria_stock_t4,
    ukraine_net_4yr = ukraine_stock_t - ukraine_stock_t4,
    window_years = 4L
  ) %>%
  select(AGS, year, syria_net_4yr, ukraine_net_4yr, window_years)

# ---- 5) Clean EP election panel ----
ep_panel_clean <- ep_panel %>%
  mutate(
    AGS = sprintf("%05s", as.character(ags)),
    year = as.integer(year)
  )

# ---- 6) Merge ----
merged_panel_ep <- ep_panel_clean %>%
  left_join(ref_4yr_net, by = c("AGS", "year"))

# ---- 7) Optional: reorder columns ----
merged_panel_ep <- merged_panel_ep %>%
  relocate(AGS, .after = 1) %>%
  relocate(ukraine_net_4yr, .after = syria_net_4yr) 
```

Control variables

```{r}

```

# Full Merging

```{r}
fed_county <- fed_county %>%
  mutate(AGS = as.character(county))

refugee_panel <- refugee_panel %>%
  mutate(AGS = as.character(AGS))
```

Data on migrants to German countries, on December 31, 2024

Regression 1: German Federal elections

```{r}
library(fixest)
merged_panel <- merged_panel %>%
  mutate(
    syria_per_voter   = syria_net_4yr / eligible_voters,
    ukraine_per_voter = ukraine_net_4yr / eligible_voters
  )

model <- feols(
  afd ~ syria_per_voter + ukraine_per_voter | AGS + year,
  data = merged_panel,
  cluster = ~AGS
)

summary(model)
wald(model, "syria_per_voter = ukraine_per_voter")
```

```         
```

```{r}
model4 <- feols(
  afd ~ syria_per_voter + ukraine_per_voter + unemp_election | AGS + year,
  data = iv_election_panel,
  cluster = ~AGS
)

summary(model4)
```

Effect of unemployment on elections

```{r}
model5 <- feols(afd ~ unemp_election | AGS + year, data = iv_election_panel)
summary(model5)
```

Regression 2: European Parliamentary Elections

```{r}
library(fixest)
merged_panel_ep <- merged_panel_ep %>%
  mutate(
    syria_per_voter1   = syria_net_4yr / eligible_voters,
    ukraine_per_voter1 = ukraine_net_4yr / eligible_voters
  )

model_ep <- feols(
  afd_share ~ syria_per_voter1 + ukraine_per_voter1 | AGS + year,
  data = merged_panel_ep,
  cluster = ~AGS
)

model_ep_ukr <- feols(
  afd_share ~ ukraine_per_voter1 | AGS + year,
  data = merged_panel_ep,
  cluster = ~AGS
)

model_ep_syr <- feols(
  afd_share ~ syria_per_voter1 | AGS + year,
  data = merged_panel_ep,
  cluster = ~AGS
)


library(modelsummary)
library(gt)

models <- list(
  "Both" = model_ep,
  "Ukrainians only" = model_ep_ukr,
  "Syrians only" = model_ep_syr
)

modelsummary(
  models,
  title = "Table 2: Baseline OLS Estimates of Refugee Exposure and AfD Vote Share, EP Elections",
  statistic = "({std.error})",
  stars = c('*' = .1, '**' = .05, '***' = .01),
  coef_map = c(
    "syria_per_voter1" = "Syrians per voter",
    "ukraine_per_voter1" = "Ukrainians per voter"
  ),
  
  # ✅ KEEP ONLY what you want
  gof_map = data.frame(
    raw = c("nobs", "r.squared"),
    clean = c("Observations", "R-squared"),
    fmt = c(0, 3)
  ),
  
  add_rows = data.frame(
    term = c("District FE", "Year FE"),
    Both = c("Yes", "Yes"),
    `Ukraine only` = c("Yes", "Yes"),
    `Syria only` = c("Yes", "Yes")
  )
)
table(merged_panel_ep$year)
```

# Visualizing where immigrants came from

```{r}
library(sf)

kreise <- st_read("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/vg250_01-01.utm32s.shape.ebenen/vg250_ebenen_0101/VG250_KRS.shp")

names(kreise)

plot(st_geometry(kreise))

ggplot(kreise) +
  geom_sf(aes(fill = BEZ)) +
  theme_void() +
  guides(fill = "none")

library(dplyr)
library(stringr)

kreise <- kreise %>%
  mutate(AGS = str_pad(as.character(AGS), 5, pad = "0"))

merged_panel <- merged_panel %>%
  mutate(AGS = str_pad(as.character(AGS), 5, pad = "0"))

kreise_clean <- kreise %>%
  mutate(AGS = str_pad(as.character(AGS), 5, pad = "0")) %>%
  group_by(AGS) %>%
  summarise(
    GEN = first(GEN),
    BEZ = first(BEZ),
    geometry = st_union(geometry),
    .groups = "drop"
  )

kreise_clean %>%
  count(AGS) %>%
  filter(n > 1)

merged_panel <- merged_panel %>%
  mutate(AGS = str_pad(as.character(AGS), 5, pad = "0"))

map_data <- kreise_clean %>%
  left_join(merged_panel, by = "AGS")

#just syria map 2021
library(ggplot2)

ggplot(map_data %>% filter(year == 2021)) +
  geom_sf(aes(fill = syria_net_4yr), color = NA) +
  scale_fill_gradient(
    low = "#fee5d9",   # light red
    high = "#a50f15",  # dark red
    na.value = "grey90",
    name = "Net inflow"
  ) +
  theme_void()

#biscale map 
install.packages("biscale")
library(biscale)

map_bi <- map_data %>%
  filter(year == 2021) %>%
  bi_class(
    x = syria_net_4yr,
    y = ukraine_net_4yr,
    style = "quantile",
    dim = 3
  )

ggplot(map_bi) +
  geom_sf(aes(fill = bi_class), color = NA) +
  bi_scale_fill(pal = "DkBlue", dim = 3) +
  theme_void()

```

```{r}
library(dplyr)
library(ggplot2)
library(patchwork)
library(scales)

# Signed log transform
signed_log <- trans_new(
  name = "signed_log",
  transform = function(x) sign(x) * log1p(abs(x)),
  inverse = function(x) sign(x) * (exp(abs(x)) - 1)
)

map_2013 <- map_data %>% filter(year == 2013)

# Get symmetric limits
max_val <- max(
  abs(map_2013$syria_net_4yr),
  abs(map_2013$ukraine_net_4yr),
  na.rm = TRUE
)

# Syria
p_syria <- ggplot(map_2013) +
  geom_sf(aes(fill = syria_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",      # blue (outflow)
    mid = "white",
    high = "#b2182b",     # red (inflow)
    midpoint = 0,
    limits = c(-max_val, max_val),
    trans = signed_log,
    name = "Net inflow"
  ) +
  theme_void() +
  labs(title = "Syria")

# Ukraine (NOW SAME SCALE STRUCTURE)
p_ukraine <- ggplot(map_2013) +
  geom_sf(aes(fill = ukraine_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0,
    limits = c(-max_val, max_val),
    trans = signed_log,
    name = "Net inflow"
  ) +
  theme_void() +
  labs(title = "Ukraine")

# Combine
p_syria + p_ukraine +
  plot_annotation(
    title = "Net inflows before the 2013 election",
    subtitle = "Signed log scale (blue = net outflow, red = net inflow)"
  )
```

```{r}
library(dplyr)
library(ggplot2)
library(patchwork)
library(scales)
library(grid)

# Signed log transform
signed_log <- trans_new(
  name = "signed_log",
  transform = function(x) sign(x) * log1p(abs(x)),
  inverse = function(x) sign(x) * (exp(abs(x)) - 1)
)

map_2013 <- map_data %>% filter(year == 2013)

# Separate limits
max_syria <- max(abs(map_2013$syria_net_4yr), na.rm = TRUE)
max_ukraine <- max(abs(map_2013$ukraine_net_4yr), na.rm = TRUE)

# Optional: round nicely
max_syria <- ceiling(max_syria / 100) * 100
max_ukraine <- ceiling(max_ukraine / 100) * 100

# Syria map
p_syria <- ggplot(map_2013) +
  geom_sf(aes(fill = syria_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0,
    limits = c(-max_syria, max_syria),
    trans = signed_log,
    breaks = c(-max_syria, max_syria),
    labels = comma(c(-max_syria, max_syria)),
    name = "Net inflow",
    guide = guide_colorbar(
      barheight = unit(3, "cm"),
      barwidth = unit(0.4, "cm"),
      ticks = FALSE
    )
  ) +
  labs(title = "Syria") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right",
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10)
  )

# Ukraine map
p_ukraine <- ggplot(map_2013) +
  geom_sf(aes(fill = ukraine_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0,
    limits = c(-max_ukraine, max_ukraine),
    trans = signed_log,
    breaks = c(-max_ukraine, max_ukraine),
    labels = comma(c(-max_ukraine, max_ukraine)),
    name = "Net inflow",
    guide = guide_colorbar(
      barheight = unit(3, "cm"),
      barwidth = unit(0.4, "cm"),
      ticks = FALSE
    )
  ) +
  labs(title = "Ukraine") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right",
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10)
  )

# Combine (NO shared legend)
p_syria + p_ukraine +
  plot_annotation(
    title = "Net inflows before the 2013 election",
    subtitle = "Signed log scale (blue = net outflow, red = net inflow)"
  )
```

2017

```{r}
library(dplyr)
library(ggplot2)
library(patchwork)
library(scales)
library(grid)

# Signed log transform
signed_log <- trans_new(
  name = "signed_log",
  transform = function(x) sign(x) * log1p(abs(x)),
  inverse = function(x) sign(x) * (exp(abs(x)) - 1)
)

map_2017 <- map_data %>% filter(year == 2017)

# Separate limits
max_syria <- max(abs(map_2017$syria_net_4yr), na.rm = TRUE)
max_ukraine <- max(abs(map_2017$ukraine_net_4yr), na.rm = TRUE)

# Optional: round nicely
max_syria <- ceiling(max_syria / 100) * 100
max_ukraine <- ceiling(max_ukraine / 100) * 100

# Syria map
p_syria <- ggplot(map_2017) +
  geom_sf(aes(fill = syria_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0,
    limits = c(-max_syria, max_syria),
    trans = signed_log,
    breaks = c(-max_syria, max_syria),
    labels = comma(c(-max_syria, max_syria)),
    name = "Net inflow",
    guide = guide_colorbar(
      barheight = unit(3, "cm"),
      barwidth = unit(0.4, "cm"),
      ticks = FALSE
    )
  ) +
  labs(title = "Syria") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right",
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10)
  )

# Ukraine map
p_ukraine <- ggplot(map_2017) +
  geom_sf(aes(fill = ukraine_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0,
    limits = c(-max_ukraine, max_ukraine),
    trans = signed_log,
    breaks = c(-max_ukraine, max_ukraine),
    labels = comma(c(-max_ukraine, max_ukraine)),
    name = "Net inflow",
    guide = guide_colorbar(
      barheight = unit(3, "cm"),
      barwidth = unit(0.4, "cm"),
      ticks = FALSE
    )
  ) +
  labs(title = "Ukraine") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right",
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10)
  )

# Combine (NO shared legend)
p_syria + p_ukraine +
  plot_annotation(
    title = "Net inflows before the 2017 election",
    subtitle = "Signed log scale (blue = net outflow, red = net inflow)"
  )
```

2021

```{r}
library(dplyr)
library(ggplot2)
library(patchwork)
library(scales)
library(grid)

# Signed log transform
signed_log <- trans_new(
  name = "signed_log",
  transform = function(x) sign(x) * log1p(abs(x)),
  inverse = function(x) sign(x) * (exp(abs(x)) - 1)
)

map_2021 <- map_data %>% filter(year == 2021)

# Separate limits
max_syria <- max(abs(map_2021$syria_net_4yr), na.rm = TRUE)
max_ukraine <- max(abs(map_2021$ukraine_net_4yr), na.rm = TRUE)

# Optional: round nicely
max_syria <- ceiling(max_syria / 100) * 100
max_ukraine <- ceiling(max_ukraine / 100) * 100

# Syria map
p_syria <- ggplot(map_2021) +
  geom_sf(aes(fill = syria_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0,
    limits = c(-max_syria, max_syria),
    trans = signed_log,
    breaks = c(-max_syria, max_syria),
    labels = comma(c(-max_syria, max_syria)),
    name = "Net inflow",
    guide = guide_colorbar(
      barheight = unit(3, "cm"),
      barwidth = unit(0.4, "cm"),
      ticks = FALSE
    )
  ) +
  labs(title = "Syria") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right",
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10)
  )

# Ukraine map
p_ukraine <- ggplot(map_2021) +
  geom_sf(aes(fill = ukraine_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0,
    limits = c(-max_ukraine, max_ukraine),
    trans = signed_log,
    breaks = c(-max_ukraine, max_ukraine),
    labels = comma(c(-max_ukraine, max_ukraine)),
    name = "Net inflow",
    guide = guide_colorbar(
      barheight = unit(3, "cm"),
      barwidth = unit(0.4, "cm"),
      ticks = FALSE
    )
  ) +
  labs(title = "Ukraine") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right",
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10)
  )

# Combine (NO shared legend)
p_syria + p_ukraine +
  plot_annotation(
    title = "Net inflows before the 2021 election",
    subtitle = "Signed log scale (blue = net outflow, red = net inflow)"
  )
```

2025

```{r}
library(dplyr)
library(ggplot2)
library(patchwork)
library(scales)
library(grid)

# Signed log transform
signed_log <- trans_new(
  name = "signed_log",
  transform = function(x) sign(x) * log1p(abs(x)),
  inverse = function(x) sign(x) * (exp(abs(x)) - 1)
)

map_2025 <- map_data %>% filter(year == 2025)

# Separate limits
max_syria <- max(abs(map_2025$syria_net_4yr), na.rm = TRUE)
max_ukraine <- max(abs(map_2025$ukraine_net_4yr), na.rm = TRUE)

# Optional: round nicely
max_syria <- ceiling(max_syria / 100) * 100
max_ukraine <- ceiling(max_ukraine / 100) * 100

# Syria map
p_syria <- ggplot(map_2025) +
  geom_sf(aes(fill = syria_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0,
    limits = c(-max_syria, max_syria),
    trans = signed_log,
    breaks = c(-max_syria, max_syria),
    labels = comma(c(-max_syria, max_syria)),
    name = "Net inflow",
    guide = guide_colorbar(
      barheight = unit(3, "cm"),
      barwidth = unit(0.4, "cm"),
      ticks = FALSE
    )
  ) +
  labs(title = "Syria") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right",
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10)
  )

# Ukraine map
p_ukraine <- ggplot(map_2025) +
  geom_sf(aes(fill = ukraine_net_4yr), color = "black", linewidth = 0.1) +
  scale_fill_gradient2(
    low = "#2166ac",
    mid = "white",
    high = "#b2182b",
    midpoint = 0,
    limits = c(-max_ukraine, max_ukraine),
    trans = signed_log,
    breaks = c(-max_ukraine, max_ukraine),
    labels = comma(c(-max_ukraine, max_ukraine)),
    name = "Net inflow",
    guide = guide_colorbar(
      barheight = unit(3, "cm"),
      barwidth = unit(0.4, "cm"),
      ticks = FALSE
    )
  ) +
  labs(title = "Ukraine") +
  theme_void() +
  theme(
    plot.title = element_text(size = 16, hjust = 0.5),
    legend.position = "right",
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10)
  )

# Combine (NO shared legend)
p_syria + p_ukraine +
  plot_annotation(
    title = "Net inflows before the 2025 election",
    subtitle = "Signed log scale (blue = net outflow, red = net inflow)"
  )
```

# IV Analysis - Syria

Instrument ​= (national Syrian inflow​) × (EASY state shares) × (County weight)

County Weight

```{r}
library(dplyr)
library(readxl)
library(stringr)
library(tidyr)

# County_weight_pre = average of all persons seeing protection 2011, 2012, 2013, that went to that AGS, as a share of those who went to that county 

#Persons seeking protection by county
County_weight <- read_excel("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Persons Seeking Protection 2011-13.xlsx", skip = 3)

# Identify year rows and extract year
County_weight <- County_weight %>%
  mutate(
    is_year = str_detect(County_weight[[1]], "^\\d{4}-"),
    year = ifelse(is_year,
                  substr(County_weight[[1]], 1, 4),
                  NA_character_)
  ) %>%
  fill(year) %>%
  filter(!is_year)

# Keep AGS, total, year
df <- County_weight %>%
  select(AGS = 1, total = 7, year) %>%
  mutate(
    AGS = as.character(AGS),
    total = as.numeric(total),
    year = as.numeric(year)
  )

# Average 2011–2013
county_avg <- df %>%
  group_by(AGS) %>%
  summarise(avg_protection = mean(total, na.rm = TRUE), .groups = "drop")

# Compute weights
county_weights <- county_avg %>%
  mutate(state = substr(AGS, 1, 2)) %>%
  group_by(state) %>%
  mutate(
    state_total = sum(avg_protection, na.rm = TRUE),
    county_weight_pre = avg_protection / state_total
  ) %>%
  ungroup()

```

Shares of Syrian nationals by county

```{r}
Syrian_2008 <- read_excel(
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Syrian_2008.xlsx",
  skip = 3
)

Syrian_2008 <- Syrian_2008 %>%
  rename(
    AGS = 1,
    county_name = 2
  ) %>%
  
  # drop the row that contains the reference date
  filter(!str_detect(AGS, "^\\d{4}-\\d{2}-\\d{2}$")) %>%
  
  # keep only valid county rows
  filter(str_detect(AGS, "^\\d{5}$")) %>%
  
  mutate(
    AGS = str_pad(AGS, width = 5, pad = "0"),
    state = substr(AGS, 1, 2)
  ) %>%
  
  # turn all non-ID columns into numeric where possible
  mutate(
    across(
      -c(AGS, county_name, state),
      ~ as.numeric(na_if(as.character(.x), "-"))
    )
  ) %>%
  
  # total Syrians in each county
  rowwise() %>%
  mutate(
    total_syria = sum(c_across(where(is.numeric)), na.rm = TRUE)
  ) %>%
  ungroup() %>%
  
  # county share within each state
  group_by(state) %>%
  mutate(
    weight_2008 = total_syria / sum(total_syria, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  
  select(AGS, county_name, state, total_syria, weight_2008)
```

```{r}
#Persons seeking protection by county 2008
library(readxl)
library(dplyr)
library(stringr)

County_weight_2008 <- read_excel(
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/All_refugees_2008.xlsx",
  skip = 3
)

County_weight_2008 <- County_weight_2008 %>%
  rename(
    AGS = 1,
    county_name = 2,
    total = 7
  ) %>%
  filter(!str_detect(AGS, "^\\d{4}-\\d{2}-\\d{2}$")) %>%
  filter(str_detect(AGS, "^\\d{5}$")) %>%
  mutate(
    AGS = str_pad(AGS, width = 5, pad = "0"),
    state = substr(AGS, 1, 2),
    total = as.numeric(total)
  ) %>%
  group_by(state) %>%
  mutate(
    weight = total / sum(total, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  select(AGS, state, county_name, total, weight)
```

National Syrian Inflow

```{r}
#National Syrian Inflow
nat_syria <- refugee_panel_clean %>%
  group_by(ref_year) %>%
  summarise(
    nat_syria = sum(Syria_total, na.rm = TRUE),
    .groups = "drop"
  )
```

EASY shares

```{r}
#Easy shares - percentages used are for 2019 but assumed to be roughly constant over the years
Easy_shares <- read.csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Distribution quotas according to the Königstein Key for 2019 - Sheet1.csv", skip = 1)

state_lookup <- tibble::tribble(
  ~state_name, ~state,
  "Schleswig-Holstein", "01",
  "Hamburg", "02",
  "Niedersachsen", "03",
  "Bremen", "04",
  "Nordrhein-Westfalen", "05",
  "Hessen", "06",
  "Rheinland-Pfalz", "07",
  "Baden-Württemberg", "08",
  "Bayern", "09",
  "Saarland", "10",
  "Berlin", "11",
  "Brandenburg", "12",
  "Mecklenburg-Vorpommern", "13",
  "Sachsen", "14",
  "Sachsen-Anhalt", "15",
  "Thüringen", "16"
)

Easy_shares <- Easy_shares %>%
  mutate(
    quota_state = as.numeric(gsub(",", ".", gsub(" %", "", Quota))) / 100
  )

Easy_shares <- Easy_shares %>%
  rename(state_name = Name) %>%
  left_join(state_lookup, by = "state_name") %>%
  select(state, state_name, quota_state)

Easy_shares <- Easy_shares %>%
  arrange(state)
```

Full Instrument

```{r}
# 1. Start from your county-year refugee panel
#panel_iv1 <- refugee_panel_clean %>%
  
  # create 2-digit state code from AGS
  #mutate(state = substr(AGS, 1, 2)) %>%

panel_iv1 <- panel_iv1 %>%
  select(
    -ends_with(".x"),
    -ends_with(".y")
  )

panel_iv1 <- panel_iv1 %>%
  mutate(
    kreis_id = str_pad(kreis_id, 5, pad = "0"),
    state = substr(kreis_id, 1, 2)
  ) %>%
  
  left_join(
    County_weight_2008 %>% select(AGS, weight),
    by = c("kreis_id" = "AGS")
  ) %>%
  
  left_join(
    nat_syria %>% select(ref_year, nat_syria),
    by = c("year" = "ref_year")
  ) %>%
  
  left_join(
    Easy_shares %>% select(state, quota_state),
    by = "state"
  )
  
panel_iv1 <- panel_iv1 %>%
  mutate(
    z_syria = nat_syria * quota_state * weight
  )
```

```{r}
panel_iv1 <- panel_iv1 %>%
  left_join(nat_syria, by = c("year" = "ref_year")) %>%
  left_join(
    smerged_2008 %>% select(kreis_id, syr_share),
    by = "kreis_id"
  ) %>%
  left_join(
    Easy_shares %>% select(state, quota_state),
    by = "state"
  ) %>%
  mutate(
    z_syria = nat_syria.y * quota_state.y * syr_share
  )
```

```{r}
panel_iv1 <- panel_iv1 %>%
  left_join(
    Syrian_2008 %>% select(AGS, total_syria, weight_2008),
    by = c("kreis_id" = "AGS")
  )

panel_iv1 <- panel_iv1 %>%
  mutate(
    z_syria_2008 = nat_syria * quota_state * weight_2008
  )
```

Performing the IV

```{r}
#Does predicted 4-year Syrian inflow per voter explain actual 4-year Syrian inflow per voter?

library(dplyr)

election_years <- c(2013L, 2017L, 2021L, 2025L)

# predicted stock at election year t
z_stock_t <- panel_iv1 %>%
  mutate(
    AGS = as.character(kreis_id),
    year = as.integer(year)
  ) %>%
  filter(year %in% c(2013L, 2017L, 2021L, 2024L)) %>%
  transmute(
    AGS,
    elec_year = if_else(year == 2024L, 2025L, year),
    z_syria_t = z_syria
  ) %>%
  filter(elec_year %in% election_years)

# predicted stock at t-4
z_stock_t4 <- panel_iv1 %>%
  mutate(
    AGS = as.character(kreis_id),
    year = as.integer(year)
  ) %>%
  filter(year %in% c(2009L, 2013L, 2017L, 2021L)) %>%
  transmute(
    AGS,
    elec_year = year + 4L,
    z_syria_t4 = z_syria
  ) %>%
  filter(elec_year %in% election_years)

# predicted 4-year net change
z_ref_4yr_net <- z_stock_t %>%
  left_join(z_stock_t4, by = c("AGS", "elec_year")) %>%
  mutate(
    z_syria_net_4yr = z_syria_t - z_syria_t4,
    window_years = if_else(elec_year == 2025L, 3L, 4L)
  ) %>%
  transmute(
    AGS,
    year = elec_year,
    z_syria_net_4yr,
    window_years
  )

# merge onto election panel
iv_election_panel <- merged_panel %>%
  mutate(
    AGS = as.character(AGS),
    year = as.integer(year)
  ) %>%
  left_join(z_ref_4yr_net, by = c("AGS", "year")) %>%
  mutate(
    syria_per_voter = syria_net_4yr / eligible_voters,
    z_syria_per_voter = z_syria_net_4yr / eligible_voters
  )
```

```{r}

election_years <- c(2013L, 2017L, 2021L, 2025L)

# predicted stock at election year t
z_stock_t <- panel_iv1 %>%
  mutate(
    AGS = as.character(kreis_id),
    year = as.integer(year)
  ) %>%
  filter(year %in% c(2013L, 2017L, 2021L, 2024L)) %>%
  transmute(
    AGS,
    elec_year = if_else(year == 2024L, 2025L, year),
    z_syria_2008_t = z_syria_2008
  ) %>%
  filter(elec_year %in% election_years)

# predicted stock at t-4
z_stock_t4 <- panel_iv1 %>%
  mutate(
    AGS = as.character(kreis_id),
    year = as.integer(year)
  ) %>%
  filter(year %in% c(2009L, 2013L, 2017L, 2021L)) %>%
  transmute(
    AGS,
    elec_year = year + 4L,
    z_syria_2008_t4 = z_syria_2008
  ) %>%
  filter(elec_year %in% election_years)

# predicted 4-year net change
z_ref_4yr_net <- z_stock_t %>%
  left_join(z_stock_t4, by = c("AGS", "elec_year")) %>%
  mutate(
    z_syria_2008_net_4yr = z_syria_2008_t - z_syria_2008_t4,
    window_years = if_else(elec_year == 2025L, 3L, 4L)
  ) %>%
  transmute(
    AGS,
    year = elec_year,
    z_syria_2008_net_4yr,
    window_years
  )

# merge onto election panel
iv_election_panel <- merged_panel %>%
  mutate(
    AGS = as.character(AGS),
    year = as.integer(year)
  ) %>%
  left_join(z_ref_4yr_net, by = c("AGS", "year")) %>%
  mutate(
    syria_per_voter = syria_net_4yr / eligible_voters,
    z_syria_2008_per_voter = z_syria_2008_net_4yr / eligible_voters
  )
```

## State level IV

```{r}
library(dplyr)

iv_election_panel_state <- iv_election_panel %>%
  mutate(
    afd_votes = afd * valid_votes,
    syria_net_4yr_implied = syria_per_voter * eligible_voters,
    z_syria_net_4yr_implied = z_syria_per_voter * eligible_voters
  ) %>%
  group_by(state, year) %>%
  summarise(
    eligible_voters = sum(eligible_voters, na.rm = TRUE),
    number_voters   = sum(number_voters, na.rm = TRUE),
    valid_votes     = sum(valid_votes, na.rm = TRUE),

    afd_votes       = sum(afd_votes, na.rm = TRUE),
    syria_net_4yr   = sum(syria_net_4yr_implied, na.rm = TRUE),
    z_syria_net_4yr = sum(z_syria_net_4yr_implied, na.rm = TRUE),

    .groups = "drop"
  ) %>%
  mutate(
    afd = afd_votes / valid_votes,
    turnout = number_voters / eligible_voters,
    syria_per_voter = syria_net_4yr / eligible_voters,
    z_syria_per_voter = z_syria_net_4yr / eligible_voters
  ) %>%
  arrange(state, year)

```

Regression

```{r}
library(lfe)

iv_syria_state <- felm(
  afd ~ 1 | state + year | (syria_per_voter ~ z_syria_per_voter) | state,
  data = iv_election_panel_state
)

summary(iv_syria_state)
summary(iv_syria_state, stage = 1)
```

# Importing One dataset

Importing data

```{r}
iv_election_panel1 <- read.csv("/Users/diananichvoloda/Desktop/iv_election_panel.csv")

iv_total <- read.csv("/Users/diananichvoloda/Desktop/iv_total.csv")

iv_total_new <- read.csv("/Users/diananichvoloda/Desktop/iv_total_new.csv")
```

# IV First Stage - Syria

```{r}
library(fixest)

# ---- First stage regression ----
fs_syria <- feols(
  syria_per_voter ~ z_syria_2008_per_voter | AGS + year,
  cluster = ~AGS,
  data = iv_election_panel
)

summary(fs_syria)

f_test <- wald(fs_syria, "z_syria_2008_per_voter")

print(f_test)

f_stat <- f_test$stat
f_stat
```

# IV Second Stage

```{r}
library(fixest)

iv_syria <- feols(
  afd ~ 1 | AGS + year | syria_per_voter ~ z_syria_2008_per_voter,
  cluster = ~AGS,
  data = iv_total_new_income
)

summary(iv_syria)
```

IV all together:

```{r}
library(lfe)

iv_syria <- felm(
  afd ~ 1 | AGS + year | (syria_per_voter ~ z_syria_per_voter) | AGS,
  data = iv_election_panel
)

summary(iv_syria)
summary(iv_syria, stage = 1)


fs_no_ags <- felm(
  syria_per_voter ~ z_syria_per_voter | year | 0 | AGS,
  data = iv_election_panel
)

summary(fs_no_ags)

fs_no_year <- felm(
  syria_per_voter ~ z_syria_per_voter | AGS | 0 | AGS,
  data = iv_election_panel
) 
summary(fs_no_year)
```

```{r}
library(lfe)

iv_syria_1 <- felm(
  afd ~ 1 | AGS + year | (syria_per_voter ~ z_syria_per_voter) | state,
  data = iv_election_panel
)

summary(iv_syria_1)

first_stage <- felm(
  syria_per_voter ~ z_syria_per_voter | AGS + year | 0 | state,
  data = iv_election_panel
)

summary(first_stage)
```

Leo's Code

```{r}
felm(syria_net_4yr ~ z_syria_net_4yr + eligible_voters, data = iv_election_panel) %>% summary()
summary(felm(syria_net_4yr ~ z_syria_net_4yr + eligible_voters, 
             data = iv_election_panel))$fstat

```

```{r}
fs_syria <- feols(
  syria_per_voter ~ z_syria_per_voter | AGS + year,
  cluster = ~AGS,
  data = iv_election_panel
)

summary(fs_syria)
f_test <- wald(fs_syria, "z_syria_per_voter")
```

Other code

```{r}
felm(afd ~ eligible_voters | 0 | (syria_per_voter ~ z_syria_per_voter), data = iv_election_panel) %>% summary()

felm(afd ~ syria_per_voter, data = iv_election_panel) %>% summary()
```

Export

```{r}
write.csv(iv_election_panel, "~/Desktop/iv_total_new.csv", row.names = FALSE)


```

# IV Analysis - Ukraine

Instrument ​= (national Ukrainian inflow​) × (2000 shares of Ukrainian nationals by county)

National Ukrainian inflow

```{r}
#National Ukrainian Inflow
nat_ukraine <- refugee_panel_clean %>%
  group_by(ref_year) %>%
  summarise(
    nat_ukraine = sum(Ukraine_total, na.rm = TRUE),
    .groups = "drop"
  )
```

Shares of Ukrainian nationals by county

```{r}
library(dplyr)
library(readxl)
library(stringr)
library(tidyr)
Pre_inflows <- read_excel("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Ukrainian_2010.xlsx", skip = 5)

year_value <- as.numeric(str_sub(as.character(Pre_inflows[[1]][1]), 1, 4))

nat_ukraine_2010 <- Pre_inflows[-1, ] %>%
  rename(
    kreis_id = ...1,
    kreis_name = ...2,
    citizenship = ...3
  ) %>%
  mutate(
    kreis_id = as.character(kreis_id),
    across(-c(kreis_id, kreis_name, citizenship), ~ as.numeric(gsub("[^0-9.]", "", as.character(.))))
  ) %>%
  filter(str_detect(kreis_id, "^\\d{5}$")) %>%
  rowwise() %>%
  mutate(ukr_total = sum(c_across(-c(kreis_id, kreis_name, citizenship)), na.rm = TRUE)) %>%
  ungroup() %>%
  transmute(
    kreis_id,
    kreis_name,
    year = year_value,
    ukr_total
  )

Total_pop <- read_excel("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Population_2010.xlsx", skip = 4)

Total_pop <- Total_pop %>%
  rename(
    kreis_id = ...1,
    kreis_name = ...2,
    total_pop = `2010-12-31`
  ) %>%
  mutate(
    kreis_id = as.character(kreis_id)
  ) %>%
  select(kreis_id, kreis_name, total_pop)

# 2. Make sure IDs match in the second dataset too
nat_ukraine_2010 <- nat_ukraine_2010 %>%
  mutate(
    kreis_id = as.character(kreis_id)
  )

# 3. Merge
merged_2010 <- nat_ukraine_2010 %>%
  left_join(Total_pop, by = c("kreis_id", "kreis_name"))

# 4. Create share if you want
merged_2010 <- merged_2010 %>%
  mutate(
    ukr_total = as.numeric(ukr_total),
    total_pop = as.numeric(gsub("[^0-9.]", "", total_pop)),
    ukr_share = ukr_total / total_pop
  )
```

```{r}
library(dplyr)
library(readxl)
library(stringr)
library(tidyr)
Pre_inflows <- read_excel("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Ukrainian_2008.xlsx", skip = 5)

year_value <- as.numeric(str_sub(as.character(Pre_inflows[[1]][1]), 1, 4))

nat_ukraine_2008 <- Pre_inflows[-1, ] %>%
  rename(
    kreis_id = ...1,
    kreis_name = ...2,
    citizenship = ...3
  ) %>%
  mutate(
    kreis_id = as.character(kreis_id),
    across(-c(kreis_id, kreis_name, citizenship), ~ as.numeric(gsub("[^0-9.]", "", as.character(.))))
  ) %>%
  filter(str_detect(kreis_id, "^\\d{5}$")) %>%
  rowwise() %>%
  mutate(ukr_total = sum(c_across(-c(kreis_id, kreis_name, citizenship)), na.rm = TRUE)) %>%
  ungroup() %>%
  transmute(
    kreis_id,
    kreis_name,
    year = year_value,
    ukr_total
  )

Total_pop <- read_excel("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Population_2008.xlsx", skip = 4)

Total_pop <- Total_pop %>%
  rename(
    kreis_id = ...1,
    kreis_name = ...2,
    total_pop = `2008-12-31`
  ) %>%
  mutate(
    kreis_id = as.character(kreis_id)
  ) %>%
  select(kreis_id, kreis_name, total_pop)

# 2. Make sure IDs match in the second dataset too
nat_ukraine_2008 <- nat_ukraine_2008 %>%
  mutate(
    kreis_id = as.character(kreis_id)
  )

# 3. Merge
merged_2008 <- nat_ukraine_2008 %>%
  left_join(Total_pop, by = c("kreis_id", "kreis_name"))

# 4. Create share if you want
merged_2008 <- merged_2008 %>%
  mutate(
    ukr_total = as.numeric(ukr_total),
    total_pop = as.numeric(gsub("[^0-9.]", "", total_pop)),
    ukr_share = ukr_total / total_pop
  )
```

Constructing the Instrument

```{r}
library(dplyr)
library(stringr)

# ------------------------------------------------------------
# 1. Build predicted stock at election year t
# ------------------------------------------------------------

election_years <- c(2013L, 2017L, 2021L, 2025L)

z_stock_t <- panel_iv1 %>%
  mutate(
    AGS = str_pad(as.character(kreis_id), width = 5, side = "left", pad = "0"),
    year = as.integer(year)
  ) %>%
  filter(year %in% c(2013L, 2017L, 2021L, 2024L)) %>%
  transmute(
    AGS,
    elec_year = if_else(year == 2024L, 2025L, year),
    z_ukraine_t = z_ukraine
  ) %>%
  filter(elec_year %in% election_years)

# ------------------------------------------------------------
# 2. Build predicted stock at t-4
# ------------------------------------------------------------

z_stock_t4 <- panel_iv1 %>%
  mutate(
    AGS = str_pad(as.character(kreis_id), width = 5, side = "left", pad = "0"),
    year = as.integer(year)
  ) %>%
  filter(year %in% c(2009L, 2013L, 2017L, 2021L)) %>%
  transmute(
    AGS,
    elec_year = year + 4L,
    z_ukraine_t4 = z_ukraine
  ) %>%
  filter(elec_year %in% election_years)

# ------------------------------------------------------------
# 3. Compute predicted 4-year net change
# ------------------------------------------------------------

z_ref_4yr_net <- z_stock_t %>%
  left_join(z_stock_t4, by = c("AGS", "elec_year")) %>%
  mutate(
    z_ukraine_net_4yr = z_ukraine_t - z_ukraine_t4,
    window_years = if_else(elec_year == 2025L, 3L, 4L)
  ) %>%
  transmute(
    AGS,
    year = elec_year,
    z_ukraine_net_4yr,
    window_years
  )

# ------------------------------------------------------------
# 4. Merge into your regression panel
#    IMPORTANT: replace iv_total_new below if your regression
#    panel has a different name
# ------------------------------------------------------------

iv_total_new <- iv_total_new %>%
  select(-any_of(c("z_ukraine_net_4yr", "z_ukraine_per_voter"))) %>%
  mutate(
    AGS = str_pad(as.character(AGS), width = 5, side = "left", pad = "0"),
    year = as.integer(year)
  ) %>%
  left_join(
    z_ref_4yr_net %>% select(AGS, year, z_ukraine_net_4yr),
    by = c("AGS", "year")
  ) %>%
  mutate(
    ukraine_per_voter = ukraine_net_4yr / eligible_voters,
    z_ukraine_per_voter = z_ukraine_net_4yr / eligible_voters
  )

# ------------------------------------------------------------
# 5. Quick checks
# ------------------------------------------------------------

str(z_ref_4yr_net)
str(iv_total_new[, c("eligible_voters", "ukraine_net_4yr", "z_ukraine_net_4yr", "z_ukraine_per_voter")])

write.csv(iv_total_new,
          "/Users/diananichvoloda/Desktop/iv_total_new.csv",
          row.names = FALSE)
```

# IV First Stage - Ukraine

```{r}
# ---- First stage regression ----
fs_ukraine <- feols(
  ukraine_per_voter ~ z_ukraine_per_voter | AGS + year,
  cluster = ~AGS,
  data = iv_total_new
)

summary(fs_ukraine)

f_test <- wald(fs_ukraine, "z_ukraine_per_voter")
print(f_test)
f_stat <- f_test$stat
f_stat
```

IV Second Stage - Ukraine

```{r}
iv_ukraine <- feols(
  afd ~ 1 | AGS + year | ukraine_per_voter ~ z_ukraine_per_voter,
  cluster = ~AGS,
  data = iv_total_new
)

summary(iv_ukraine)
```

Full IV and Table

```{r}
# ---- First stage regression ----
fs_ukraine <- feols(
  ukraine_per_voter ~ z_ukraine_per_voter | AGS + year,
  cluster = ~AGS,
  data = iv_total_new
)

summary(fs_ukraine)

f_test <- wald(fs_ukraine, "z_ukraine_per_voter")
print(f_test)
f_stat <- f_test$stat
f_stat

iv_ukraine <- feols(
  afd ~ 1 | AGS + year | ukraine_per_voter ~ z_ukraine_per_voter,
  cluster = ~AGS,
  data = iv_total_new
)

summary(iv_ukraine)

library(modelsummary)

# Extract F-stat
f_test <- wald(fs_ukraine, "z_ukraine_per_voter")
f_stat <- round(f_test$stat, 2)

modelsummary(
  list(
    "Second Stage" = iv_ukraine,
    "First Stage"  = fs_ukraine
  ),
  title = "Table 4: IV Estimates of the Effect of Ukrainian Refugee Exposure on AfD Vote Share, Federal Elections",
  
  statistic = "({std.error})",
  stars = c('*' = .1, '**' = .05, '***' = .01),
  
  coef_map = c(
    "ukraine_per_voter"      = "Ukrainians per voter",
    "fit_ukraine_per_voter"  = "Ukrainians per voter",
    "z_ukraine_per_voter"    = "Ukrainian IV"
  ),
  
  gof_map = data.frame(
    raw   = c("nobs", "r.squared"),
    clean = c("Observations", "R-squared"),
    fmt   = c(0, 3)
  ),
  
  add_rows = data.frame(
    term = c("District FE", "Year FE", "First-stage F-statistic"),
    `Second Stage` = c("Yes", "Yes", ""),
    `First Stage`  = c("Yes", "Yes", f_stat)
  )
)
```

IV using FELM

```{r}
iv_Ukraine <- felm(
  afd ~ 1 | AGS + year | (ukraine_per_voter ~ z_ukraine_per_voter) | AGS,
  data = iv_election_panel
)

summary(iv_Ukraine)
```

# Unemployment

```{r}
library(dplyr)
library(tidyr)
library(stringr)
# 1. Read raw lines
lines <- readLines("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Unemployment 2007-25.csv")

# 2. Keep only actual table area
lines <- lines[8:length(lines)]

# 3. Split manually
split <- strsplit(lines, ";")

# 4. Make all rows same length
max_len <- max(lengths(split))
split <- lapply(split, function(x) {
  length(x) <- max_len
  x
})

# 5. Convert to data frame
raw_df <- as.data.frame(do.call(rbind, split), stringsAsFactors = FALSE)

# 6. Use row 2 as the real header row
colnames(raw_df) <- trimws(gsub('"', "", as.character(raw_df[2, ])))

# 7. Drop the empty first row and the header row
df <- raw_df[-c(1, 2), ]

# 8. Remove columns with missing or blank names
df <- df[, !(is.na(names(df)) | names(df) == "")]

# 9. Clean all values: remove quotes and trim whitespace
df[] <- lapply(df, function(x) {
  trimws(gsub('"', "", x))
})

# 10. Rename first two columns
names(df)[1:2] <- c("kreis", "ags8")

# 11. Identify year columns
year_cols <- names(df)[grepl("^20[0-9]{2}$", names(df))]

# 12. Reshape to long format
unemployment_long <- df %>%
  mutate(AGS5 = substr(ags8, 1, 5)) %>%
  select(AGS5, all_of(year_cols)) %>%
  pivot_longer(
    cols = all_of(year_cols),
    names_to = "year",
    values_to = "unemp_rate"
  ) %>%
  mutate(
    year = as.integer(year),
    unemp_rate = as.numeric(str_replace(unemp_rate, ",", "."))
  ) %>%
  filter(!is.na(year), year >= 2008, year <= 2024) %>%
  select(AGS5, year, unemp_rate)

# 13. Check output
head(unemployment_long)
View(unemployment_long)
```

```{r}
library(dplyr)
library(tidyr)
library(stringr)

#unemployment_long <- df %>%
  #pivot_longer(
    #cols = -c(kreis, ags8),
    #names_to = "year",
    #values_to = "unemp_rate"
  #) %>%
  #mutate(
    #year = as.integer(str_extract(year, "\\d{4}")),
    #unemp_rate = as.numeric(str_replace(unemp_rate, ",", ".")),
    #AGS5 = substr(ags8, 1, 5)
  #) %>%
  #select(AGS5, year, unemp_rate)

unemp_election <- unemployment_long %>%
  filter(year %in% c(2008, 2012, 2015, 2016, 2019, 2020, 2023, 2024)) %>%
  mutate(election_year = case_when(
    year %in% c(2011, 2012) ~ 2013L,
    year %in% c(2015, 2016) ~ 2017L,
    year %in% c(2019, 2020) ~ 2021L,
    year %in% c(2023, 2024) ~ 2025L
  )) %>%
  group_by(AGS5, election_year) %>%
  summarise(
    unemp_pre2yr_avg = mean(unemp_rate, na.rm = TRUE),
    .groups = "drop"
  )

iv_election_panel <- iv_election_panel %>%
  left_join(
    unemp_election,
    by = c("AGS" = "AGS5", "year" = "election_year")
  )
```

```{r}
iv_total_new <- iv_total_new %>%
  mutate(AGS = str_pad(AGS, width = 5, side = "left", pad = "0"))

unemp_historic <- unemployment_long %>%
  filter(year == 2008) %>%
  transmute(
    AGS5 = str_pad(AGS5, width = 5, side = "left", pad = "0"),
    unemp_historic_rate = unemp_rate
  )

iv_total_new_unemp <- iv_total_new %>%
  left_join(unemp_historic, by = c("AGS" = "AGS5"))

#iv_election_panel <- iv_election_panel %>%
  #left_join(
    #unemp_historic,
    #by = c("AGS" = "AGS5")
  #)

#unemp_election_year <- unemployment_long %>%
  #filter(year %in% c(2013, 2017, 2021, 2025)) %>%
  #rename(unemp_election = unemp_rate)

#iv_election_panel <- iv_election_panel %>%
  #left_join(
    #unemp_election_year,
    #by = c("AGS" = "AGS5", "year" = "year")
  #)
```

```{r}
iv_election_panel <- iv_election_panel %>%
  select(-income_historic_2008.y) 
```

# Income

```{r}
#Income_kreis <- read_excel("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Income by Kreis.xlsx")
library(readxl) 
path <- "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Income by Kreis.xlsx"

excel_sheets(path)

#read_excel(path, sheet = "3", n_max = 20, col_names = FALSE)

Income_kreis <- read_excel(path, sheet = "3", skip = 4)

income_historic <- Income_kreis %>%
  rename(
    AGS5 = `Regional-schlüssel`
  ) %>%
  filter(`NUTS 3` == 3) %>%   # keep only Kreise
  mutate(
    AGS5 = as.character(AGS5)
  ) %>%
  select(
    AGS5,
    income_historic_2008 = `2008`
  )

iv_total_new_income <- iv_total_new %>%
  left_join(
    income_historic,
    by = c("AGS" = "AGS5")
  )
```

# Regressions for Unemployment and Income

Unemployment

```{r}
model_unemp <- feols(
  afd ~ syria_per_voter + ukraine_per_voter + ukraine_per_voter:unemp_historic_rate +
    syria_per_voter:unemp_historic_rate |
    AGS + year,
  data = iv_total_new_unemp,
  cluster = ~AGS 
)

summary(model_unemp)
wald(model_unemp, "syria_per_voter = ukraine_per_voter")

vcov_mat <- vcov(model_unemp)

# Function to compute SE of marginal effect
se_func <- function(var_main, var_inter, unemp, vcov_mat){
  var <- vcov_mat[var_main, var_main] +
         (unemp^2) * vcov_mat[var_inter, var_inter] +
         2 * unemp * vcov_mat[var_main, var_inter]
  sqrt(var)
}

df_plot <- data.frame(
  unemp = unemp_seq,
  Syria = b1 + b3 * unemp_seq,
  Ukraine = b2 + b4 * unemp_seq,
  se_syria = sapply(unemp_seq, function(u)
    se_func("syria_per_voter",
            "syria_per_voter:unemp_historic_rate", u, vcov_mat)),
  se_ukraine = sapply(unemp_seq, function(u)
    se_func("ukraine_per_voter",
            "ukraine_per_voter:unemp_historic_rate", u, vcov_mat))
)

df_plot_long <- df_plot %>%
  mutate(
    Syria_low = Syria - 1.96 * se_syria,
    Syria_high = Syria + 1.96 * se_syria,
    Ukraine_low = Ukraine - 1.96 * se_ukraine,
    Ukraine_high = Ukraine + 1.96 * se_ukraine
  ) %>%
  pivot_longer(cols = c(Syria, Ukraine),
               names_to = "Group",
               values_to = "Effect") %>%
  mutate(
    lower = ifelse(Group == "Syria", Syria_low, Ukraine_low),
    upper = ifelse(Group == "Syria", Syria_high, Ukraine_high)
  )

ggplot(df_plot_long, aes(x = unemp, y = Effect, color = Group, fill = Group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, color = NA) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(
    x = "2008 Unemployment Rate",
    y = "Marginal Effect on AfD Vote Share",
    color = "Refugee Origin",
    fill = "Refugee Origin",
    title = "Heterogeneous Effects of Refugee Inflows by Unemployment"
  ) +
  theme_minimal(base_size = 14)

```

Just the table:

```{r}
library(dplyr)
library(knitr)

model_unemp <- feols(
  afd ~ syria_per_voter + ukraine_per_voter + 
    ukraine_per_voter:unemp_historic_rate +
    syria_per_voter:unemp_historic_rate |
    AGS + year,
  data = iv_total_new_unemp,
  cluster = ~AGS
)

summary(model_unemp)
wald(model_unemp, "syria_per_voter = ukraine_per_voter")

library(kableExtra)

kable(
  table_clean,
  format = "html",
  digits = 3,
  caption = "Marginal Effects of Refugee Inflows on AfD Vote Share"
) %>%
  kable_styling(
    full_width = FALSE,
    font_size = 12,
    position = "center"
  ) %>%
  row_spec(0,
           bold = TRUE,
           extra_css = "font-family: 'Times New Roman', Times, serif; color: black;") %>%
  column_spec(1:ncol(table_clean),
              extra_css = "font-family: 'Times New Roman', Times, serif;") %>%
  add_header_above(
    c(" " = 3, "Effects on AfD Vote Share" = 3),
    bold = TRUE,
    extra_css = "font-family: 'Times New Roman', Times, serif; color: black;"
  ) %>%
  kable_styling(
    bootstrap_options = "striped"
  ) %>%
  footnote(general = NULL) %>%
  # fix caption (title)
  kableExtra::kable_styling() %>%
  kableExtra::add_header_above(c(" " = ncol(table_clean))) %>%
  # override caption style
  kableExtra::column_spec(1, extra_css = "font-family: 'Times New Roman';")

kable(
  table_clean,
  format = "html",
  digits = 3
)
library(htmltools)

tagList(
  tags$div(
    "Marginal Effects of Refugee Inflows on AfD Vote Share",
    style = "
      font-family: 'Times New Roman', Times, serif;
      font-weight: bold;
      color: black;
      font-size: 18px;
      margin-bottom: 8px;
    "
  ),
  
  kable(
    table_clean,
    format = "html",
    digits = 3
  ) %>%
    kable_styling(
      full_width = FALSE,
      font_size = 12,
      position = "center"
    ) %>%
    row_spec(0, bold = TRUE) %>%
    add_header_above(c(" " = 3, "Effects on AfD Vote Share" = 3), bold = TRUE)
)
```

```{r}
model_unemp <- feols(
  afd ~ syria_per_voter + ukraine_per_voter +
    unemp_historic_rate +
    syria_per_voter:unemp_historic_rate +
    ukraine_per_voter:unemp_historic_rate |
    AGS + year,
  data = iv_total_new_unemp,
  cluster = ~AGS 
)
```

```{r}
model_unemp_quad <- feols(
  afd ~ syria_per_voter + ukraine_per_voter +
    syria_per_voter:unemp_historic_rate +
    ukraine_per_voter:unemp_historic_rate +
    syria_per_voter:I(unemp_historic_rate^2) +
    ukraine_per_voter:I(unemp_historic_rate^2) |
    AGS + year,
  data = iv_total_new_unemp,
  cluster = ~AGS
)

summary(model_unemp_quad)
```

Income

```{r}
#Income

model_income <- feols(
  afd ~ syria_per_voter + ukraine_per_voter +
    syria_per_voter:income_historic_2008 +
    ukraine_per_voter:income_historic_2008 |
    AGS + year,
  data = iv_total_new_income,
  cluster = ~AGS
)

summary(model_income)
wald(model_income, "syria_per_voter = ukraine_per_voter")
```

Income Graphic

```{r}
library(dplyr)
library(knitr)

model_income <- feols(
  afd ~ syria_per_voter + ukraine_per_voter + 
    ukraine_per_voter:income_historic_2008 +
    syria_per_voter:income_historic_2008 |
    AGS + year,
  data = iv_total_new_income,
  cluster = ~AGS
)

summary(model_income)
wald(model_income, "syria_per_voter = ukraine_per_voter")

library(kableExtra)

kable(
  table_clean,
  format = "html",
  digits = 3,
  caption = "Marginal Effects of Refugee Inflows on AfD Vote Share"
) %>%
  kable_styling(
    full_width = FALSE,
    font_size = 12,
    position = "center"
  ) %>%
  row_spec(0,
           bold = TRUE,
           extra_css = "font-family: 'Times New Roman', Times, serif; color: black;") %>%
  column_spec(1:ncol(table_clean),
              extra_css = "font-family: 'Times New Roman', Times, serif;") %>%
  add_header_above(
    c(" " = 3, "Effects on AfD Vote Share" = 3),
    bold = TRUE,
    extra_css = "font-family: 'Times New Roman', Times, serif; color: black;"
  ) %>%
  kable_styling(
    bootstrap_options = NULL
  ) %>%
  footnote(general = NULL) %>%
  # fix caption (title)
  kableExtra::kable_styling() %>%
  kableExtra::add_header_above(c(" " = ncol(table_clean))) %>%
  # override caption style
  kableExtra::column_spec(1, extra_css = "font-family: 'Times New Roman';")

kable(
  table_clean,
  format = "html",
  digits = 3
)
library(htmltools)

tagList(
  tags$div(
    "Marginal Effects of Refugee Inflows on AfD Vote Share",
    style = "
      font-family: 'Times New Roman', Times, serif;
      font-weight: bold;
      color: black;
      font-size: 18px;
      margin-bottom: 8px;
    "
  ),
  
  kable(
    table_clean,
    format = "html",
    digits = 3
  ) %>%
    kable_styling(
      full_width = FALSE,
      font_size = 12,
      position = "center"
    ) %>%
    row_spec(0, bold = TRUE) %>%
    add_header_above(c(" " = 3, "Effects on AfD Vote Share" = 3), bold = TRUE)
)
```

```{r}
library(fixest)
library(dplyr)
library(tibble)
library(knitr)
library(kableExtra)

#--------------------------------------------------
# 1. Run regression with income interactions
#--------------------------------------------------
model_income <- feols(
  afd ~ syria_per_voter + ukraine_per_voter +
    syria_per_voter:income_historic_2008 +
    ukraine_per_voter:income_historic_2008 |
    AGS + year,
  data = iv_total_new_income,
  cluster = ~AGS
)

summary(model_income)
wald(model_income, "syria_per_voter = ukraine_per_voter")

#--------------------------------------------------
# 2. Choose income values: 25th percentile, median, 75th percentile
#--------------------------------------------------
income_vals <- quantile(
  iv_total_new_income$income_historic_2008,
  probs = c(0.25, 0.50, 0.75),
  na.rm = TRUE
)

income_labels <- c("25th percentile", "Median", "75th percentile")

#--------------------------------------------------
# 3. Extract coefficients and clustered vcov
#--------------------------------------------------
b <- coef(model_income)
V <- vcov(model_income)

#--------------------------------------------------
# 4. Function to compute marginal effect, SE, and p-value
#--------------------------------------------------
get_me <- function(base_var, int_var, z, b, V) {
  me <- b[base_var] + z * b[int_var]

  se <- sqrt(
    V[base_var, base_var] +
      z^2 * V[int_var, int_var] +
      2 * z * V[base_var, int_var]
  )

  p <- 2 * (1 - pnorm(abs(me / se)))

  tibble(
    `Marginal effect` = sprintf("%.3f", me),
    `Std. error` = sprintf("%.3f", se),
    `p-value` = sprintf("%.3f", p)
  )
}

#--------------------------------------------------
# 5. Build final table data
#--------------------------------------------------
table_income <- bind_rows(
  lapply(seq_along(income_vals), function(i) {
    z <- as.numeric(income_vals[i])

    bind_rows(
      tibble(
        Origin = "Syria",
        `Income level` = income_labels[i],
        `Income value` = sprintf("%.3f", z)
      ) %>%
        bind_cols(
          get_me(
            "syria_per_voter",
            "syria_per_voter:income_historic_2008",
            z, b, V
          )
        ),

      tibble(
        Origin = "Ukraine",
        `Income level` = income_labels[i],
        `Income value` = sprintf("%.3f", z)
      ) %>%
        bind_cols(
          get_me(
            "ukraine_per_voter",
            "ukraine_per_voter:income_historic_2008",
            z, b, V
          )
        )
    )
  })
) %>%
  mutate(
    Origin = factor(Origin, levels = c("Syria", "Ukraine")),
    `Income level` = factor(
      `Income level`,
      levels = c("25th percentile", "Median", "75th percentile")
    )
  ) %>%
  arrange(Origin, `Income level`) %>%
  mutate(
    Origin = as.character(Origin),
    `Income level` = as.character(`Income level`)
  )

#--------------------------------------------------
# 6. Render table in Times New Roman with striped rows
#--------------------------------------------------
kbl(
  table_income,
  format = "html",
  escape = FALSE,
  align = c("l", "l", "r", "r", "r", "r"),
  col.names = c(
    "Origin",
    "Income level",
    "Income value",
    "Marginal effect",
    "Std. error",
    "p-value"
  )
) %>%
  add_header_above(
    c(" " = 3, "Effects on AfD Vote Share" = 3),
    extra_css = "font-family: 'Times New Roman', Times, serif; font-weight: bold;"
  ) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    font_size = 18,
    bootstrap_options = "striped"
  ) %>%
  row_spec(
    0,
    bold = TRUE,
    font_size = 20,
    extra_css = "
      font-family: 'Times New Roman', Times, serif;
      border-bottom: 2px solid #cfcfcf;
    "
  ) %>%
  row_spec(
    1:nrow(table_income),
    extra_css = "
      font-family: 'Times New Roman', Times, serif;
    "
  ) %>%
  column_spec(
    1:6,
    extra_css = "
      font-family: 'Times New Roman', Times, serif;
    "
  ) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "18em") %>%
  column_spec(3, width = "10em") %>%
  column_spec(4, width = "12em") %>%
  column_spec(5, width = "10em") %>%
  column_spec(6, width = "8em")
```

Quadratic

```{r}
model_income_quad <- feols(
  afd ~ syria_per_voter + ukraine_per_voter +
    syria_per_voter:income_historic_2008 +
    ukraine_per_voter:income_historic_2008 +
    syria_per_voter:I(income_historic_2008^2) +
    ukraine_per_voter:I(income_historic_2008^2) |
    AGS + year,
  data = iv_total_new_income,
  cluster = ~AGS
)

summary(model_income_quad)
```

Combined

```{r}
model_combined <- feols(
  afd ~ syria_per_voter + ukraine_per_voter +
    syria_per_voter:income_historic_2008 +
    ukraine_per_voter:income_historic_2008 +
    syria_per_voter:unemp_historic_rate +
    ukraine_per_voter:unemp_historic_rate |
    AGS + year,
  data = iv_election_panel,
  cluster = ~AGS
)

summary(model_combined)
model_combined$collin.var
```
