---
title: "Text Analysis"
output: html_document
date: "2026-04-15"
---

```{r echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
library(dplyr)
library(tidyverse)
library(kableExtra)
library(lmtest)
library(ggplot2)
library(fixest)
library(lfe)
#rm(list=ls())
options(tibble.width = Inf)
options(width = 200)
```

```{r preliminaries, echo=FALSE}
rm(list=ls()) #clean out memory 
```

## Baden Wurttemberg

Loading data

```{r}
# replace with your actual path
BadenWurttemberg <- read_csv(
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Baden-Württemberg.csv",
  locale = locale(encoding = "UTF-8"),
  show_col_types = FALSE
)


BadenWurttemberg <- BadenWurttemberg %>%
  mutate(
    # Step 1: remove "unknown"
    Date = ifelse(Date == "unknown", NA, Date),

    # Step 2: keep only the date part
    Date = substr(Date, 1, 10),

    # Step 3: convert to Date
    Date = as.Date(Date)
  )

summary(BadenWurttemberg$Date)
range(BadenWurttemberg$Date, na.rm = TRUE)

bw <- BadenWurttemberg %>%
  filter(!is.na(Date)) %>%
  filter(Date >= as.Date("2013-01-01"),
         Date <= as.Date("2025-12-31"))

summary(bw$Date)
range(bw$Date, na.rm = TRUE)

bw_clean <- bw %>%
  filter(Interjection == FALSE)
nrow(bw)
nrow(bw_clean)
```

```{r}
library(dplyr)
library(stringr)
library(readr)

speeches <- bw %>%
  filter(Interjection == FALSE) %>%
  arrange(Date, Period, Session) %>%
  mutate(
    new_speech = case_when(
      row_number() == 1 ~ TRUE,
      Period != lag(Period) ~ TRUE,
      Session != lag(Session) ~ TRUE,
      Date != lag(Date) ~ TRUE,
      MPID != lag(MPID) ~ TRUE,
      Chair != lag(Chair) ~ TRUE,
      TRUE ~ FALSE
    ),
    speech_id = cumsum(new_speech)
  ) %>%
  group_by(speech_id) %>%
  summarise(
    Period = first(Period),
    Session = first(Session),
    Date = first(Date),
    MPID = first(MPID),
    Party = first(Party),
    Constituency = first(Constituency),
    Chair = first(Chair),
    Speech = str_squish(str_c(Speech, collapse = " ")),
    n_rows_merged = n(),
    .groups = "drop"
  ) %>%
  mutate(
    n_words = str_count(Speech, "\\S+")
  ) %>%
  filter(n_words >= 5)

write_csv(speeches, "bw_speeches_2013_2023_clean.csv")

speeches <- speeches %>%
  mutate(
    constituency_name = str_remove(Constituency, "^\\d+\\s*"),
    constituency_name = str_squish(constituency_name)
  )
speeches %>%
  count(constituency_name, sort = TRUE)
```

```{r}
library(dplyr)
library(stringr)
library(tibble)

# 1) Standardize constituency names a bit more
speeches <- speeches %>%
  mutate(
    constituency_name = str_squish(constituency_name),
    constituency_name = str_replace_all(constituency_name, "–", "-")
  )

# 2) Collapse obvious sub-constituencies to city/county-level names
speeches <- speeches %>%
  mutate(
    constituency_name_std = case_when(
      str_detect(constituency_name, "^Stuttgart") ~ "Stuttgart",
      str_detect(constituency_name, "^Mannheim") ~ "Mannheim",
      str_detect(constituency_name, "^Karlsruhe") ~ "Karlsruhe",
      str_detect(constituency_name, "^Freiburg") ~ "Freiburg",
      str_detect(constituency_name, "^Hechingen-Munsingen$|^Hechingen-Münsingen$") ~ "Zollernalbkreis",
      str_detect(constituency_name, "^Tuttlingen-Donaueschingen$|^Tuttlingen-Donau") ~ "Tuttlingen",
      str_detect(constituency_name, "^Kirchheim unter Teck$") ~ "Esslingen",
      TRUE ~ constituency_name
    )
  )

# 3) Crosswalk: constituency -> Kreis / Stadtkreis + AGS
# match_quality:
#   exact = same-name or very close county/city match
#   approx = constituency name assigned to containing Kreis/Stadtkreis
constituency_to_kreis <- tribble(
  ~constituency_name_std, ~kreis_name,                ~ags,    ~match_quality,
  "Stuttgart",            "Stuttgart",                "08111", "approx",
  "Leonberg",             "Böblingen",                "08115", "approx",
  "Backnang",             "Rems-Murr-Kreis",          "08119", "approx",
  "Esslingen",            "Esslingen",                "08116", "exact",
  "Schwetzingen",         "Rhein-Neckar-Kreis",       "08226", "approx",
  "Main-Tauber",          "Main-Tauber-Kreis",        "08128", "exact",
  "Tuttlingen",           "Tuttlingen",               "08327", "approx",
  "Balingen",             "Zollernalbkreis",          "08417", "approx",
  "Neckarsulm",           "Heilbronn",                "08125", "approx",
  "Bruchsal",             "Karlsruhe",                "08215", "approx",
  "Göppingen",            "Göppingen",                "08117", "exact",
  "Lahr",                 "Ortenaukreis",             "08317", "approx",
  "Rottweil",             "Rottweil",                 "08325", "exact",
  "Schwabisch Hall",      "Schwäbisch Hall",          "08127", "approx",
  "Schwäbisch Hall",      "Schwäbisch Hall",          "08127", "exact",
  "Heidenheim",           "Heidenheim",               "08135", "exact",
  "Mannheim",             "Mannheim",                 "08222", "approx",
  "Waiblingen",           "Rems-Murr-Kreis",          "08119", "approx",
  "Zollernalbkreis",      "Zollernalbkreis",          "08417", "approx",
  "Heilbronn",            "Heilbronn",                "08125", "exact",
  "Schorndorf",           "Rems-Murr-Kreis",          "08119", "approx",
  "Pforzheim",            "Pforzheim",                "08231", "exact",
  "Freudenstadt",         "Freudenstadt",             "08237", "exact",
  "Weinheim",             "Rhein-Neckar-Kreis",       "08226", "approx",
  "Geislingen",           "Göppingen",                "08117", "approx",
  "Enz",                  "Enzkreis",                 "08236", "exact",
  "Böblingen",            "Böblingen",                "08115", "exact",
  "Nürtingen",            "Esslingen",                "08116", "approx",
  "Singen",               "Konstanz",                 "08335", "approx",
  "Ravensburg",           "Ravensburg",               "08436", "exact",
  "Kirchheim",            "Esslingen",                "08116", "approx",
  "Ludwigsburg",          "Ludwigsburg",              "08118", "exact",
  "Bretten",              "Karlsruhe",                "08215", "approx",
  "Eppingen",             "Heilbronn",                "08125", "approx",
  "Neckar-Odenwald",      "Neckar-Odenwald-Kreis",    "08225", "exact",
  "Lörrach",              "Lörrach",                  "08336", "exact",
  "Calw",                 "Calw",                     "08235", "exact",
  "Hohenlohe",            "Hohenlohekreis",           "08126", "approx",
  "Breisgau",             "Breisgau-Hochschwarzwald", "08315", "approx",
  "Reutlingen",           "Reutlingen",               "08415", "exact",
  "Sigmaringen",          "Sigmaringen",              "08437", "exact",
  "Sinsheim",             "Rhein-Neckar-Kreis",       "08226", "approx",
  "Wiesloch",             "Rhein-Neckar-Kreis",       "08226", "approx",
  "Ulm",                  "Ulm",                      "08421", "exact",
  "Wangen",               "Ravensburg",               "08436", "approx",
  "Heidelberg",           "Heidelberg",               "08221", "exact",
  "Rastatt",              "Rastatt",                  "08216", "exact",
  "Tübingen",             "Tübingen",                 "08416", "exact",
  "Offenburg",            "Ortenaukreis",             "08317", "approx",
  "Aalen",                "Ostalbkreis",              "08136", "approx",
  "Baden-Baden",          "Baden-Baden",              "08211", "exact",
  "Schwäbisch Gmünd",     "Ostalbkreis",              "08136", "approx",
  "Bodensee",             "Bodenseekreis",            "08435", "approx"
)

# 4) Join crosswalk onto full speeches dataset
speeches_mapped <- speeches %>%
  left_join(constituency_to_kreis, by = "constituency_name_std")

# 5) Diagnostics
# How many speeches got mapped?
speeches_mapped %>%
  summarise(
    total_speeches = n(),
    mapped_speeches = sum(!is.na(ags)),
    mapped_share = mean(!is.na(ags))
  )

# Which constituency labels are still unmatched?
speeches_mapped %>%
  filter(is.na(ags)) %>%
  count(constituency_name, sort = TRUE)

# Optional: keep only exact matches for a conservative baseline
#speeches_exact <- speeches_mapped %>%
  #filter(match_quality == "exact")

# Optional: keep exact + approximate for broader coverage
speeches_baseline <- speeches_mapped %>%
  filter(!is.na(ags))
```

```{r}
library(stringr)

speeches_baseline <- speeches_baseline %>%
  mutate(
    mentions_refugees = str_detect(
  str_to_lower(Speech),
  "flücht|asyl|migration|zuwander|migrant|integration|einwander|abschieb"
)
  )

mean(speeches_baseline$mentions_refugees)

write_csv(
  speeches_baseline,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/speeches_baseline_for_gabriel.csv"
)
```

# Baden-Wurttemberg

```{r}
file_bw <- "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Baden-Württemberg.csv"
```

```{r}
library(readr)
library(dplyr)
library(stringr)
library(tidyr)
library(purrr)

clean_state_immigration_subset <- function(file_path,
                                           start_date = "2013-01-01",
                                           end_date   = "2025-12-31") {
  
  state_name <- tools::file_path_sans_ext(basename(file_path))
  
  immigration_pattern <- paste(
    c(
      "flücht", "geflücht", "asyl", "migration", "migrant",
      "zuwander", "einwander", "ausländer", "fremd",
      "integration", "integrations", "abschieb", "abschiebe",
      "duld", "aufenthalt", "aufnahme", "schutzsuch",
      "visa", "visum", "grenze", "grenz", "illegal",
      "irregul", "schleus", "staatsangehör", "einbürger",
      "bürgerrecht", "ukrain", "syr", "afghan",
      "subsidiär", "schutzstatus", "rückführ", "rueckfuehr",
      "heimat", "obergrenz", "flucht", "vertrieben",
      "resettlement", "familiennachzug"
    ),
    collapse = "|"
  )
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  # Ensure required columns exist even if missing in some states
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = as.character(Date),
      Date = str_trim(Date),
      Date = case_when(
        Date %in% c("unknown", "NA", "", "null") ~ NA_character_,
        TRUE ~ Date
      ),
      Date = substr(Date, 1, 10),
      Date = suppressWarnings(as.Date(Date)),
      
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  # Remove interjections when column exists / is usable
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  # Reconstruct speeches
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      n_words = str_count(Speech, "\\S+"),
      state = state_name,
      immigration_related = str_detect(
        str_to_lower(Speech),
        immigration_pattern
      )
    ) %>%
    filter(n_words >= 5) %>%
    filter(immigration_related) %>%
    select(
      state, Period, Session, Date, MPID, Party,
      Constituency, Chair, Speech, n_rows_merged, n_words,
      immigration_related
    )
  
  return(speeches)
}
```

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_bw_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    
    # normalize dash variants
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    
    # remove leading constituency numbers like "01 Stuttgart I"
    x <- str_replace(x, "^\\d+\\s+", "")
    
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_bw <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      str_detect(constituency_key, "^Stuttgart") ~ "Stuttgart",
      constituency_key == "Böblingen" ~ "Böblingen",
      constituency_key == "Leonberg" ~ "Böblingen",
      constituency_key == "Esslingen" ~ "Esslingen",
      constituency_key %in% c("Kirchheim", "Kirchheim unter Teck", "Nürtingen") ~ "Esslingen",
      constituency_key == "Göppingen" ~ "Göppingen",
      constituency_key == "Geislingen" ~ "Göppingen",
      constituency_key == "Ludwigsburg" ~ "Ludwigsburg",
      constituency_key %in% c("Vaihingen", "Bietigheim-Bissingen") ~ "Ludwigsburg",
      constituency_key %in% c("Waiblingen", "Schorndorf", "Backnang") ~ "Rems-Murr-Kreis",
      constituency_key == "Heilbronn" ~ "Heilbronn",
      constituency_key %in% c("Eppingen", "Neckarsulm") ~ "Landkreis Heilbronn",
      constituency_key == "Hohenlohe" ~ "Hohenlohekreis",
      constituency_key == "Schwäbisch Hall" ~ "Schwäbisch Hall",
      constituency_key == "Main-Tauber" ~ "Main-Tauber-Kreis",
      constituency_key == "Heidenheim" ~ "Heidenheim",
      constituency_key %in% c("Schwäbisch Gmünd", "Aalen") ~ "Ostalbkreis",
      constituency_key == "Karlsruhe I" ~ "Karlsruhe",
      constituency_key %in% c("Bruchsal", "Ettlingen") ~ "Landkreis Karlsruhe",
      constituency_key == "Baden-Baden" ~ "Baden-Baden",
      constituency_key == "Heidelberg" ~ "Heidelberg",
      constituency_key %in% c("Mannheim I", "Mannheim II") ~ "Mannheim",
      constituency_key %in% c("Wiesloch", "Weinheim", "Schwetzingen", "Sinsheim") ~ "Rhein-Neckar-Kreis",
      constituency_key == "Neckar-Odenwald" ~ "Neckar-Odenwald-Kreis",
      constituency_key == "Calw" ~ "Calw",
      constituency_key == "Enz" ~ "Enzkreis",
      constituency_key == "Freudenstadt" ~ "Freudenstadt",
      str_detect(constituency_key, "^Freiburg") ~ "Freiburg im Breisgau",
      constituency_key == "Breisgau" ~ "Breisgau-Hochschwarzwald",
      constituency_key == "Emmendingen" ~ "Emmendingen",
      constituency_key == "Lahr" ~ "Ortenaukreis",
      constituency_key == "Rottweil" ~ "Rottweil",
      constituency_key == "Villingen-Schwenningen" ~ "Schwarzwald-Baar-Kreis",
      constituency_key %in% c("Konstanz", "Singen") ~ "Konstanz",
      constituency_key == "Lörrach" ~ "Lörrach",
      constituency_key == "Reutlingen" ~ "Reutlingen",
      constituency_key == "Tübingen" ~ "Tübingen",
      constituency_key == "Balingen" ~ "Zollernalbkreis",
      constituency_key == "Ulm" ~ "Ulm",
      constituency_key == "Ravensburg" ~ "Ravensburg",
      constituency_key == "Sigmaringen" ~ "Sigmaringen",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_bw <- function(district) {
    case_when(
      district == "Stuttgart" ~ "08111",
      district == "Böblingen" ~ "08115",
      district == "Esslingen" ~ "08116",
      district == "Göppingen" ~ "08117",
      district == "Ludwigsburg" ~ "08118",
      district == "Rems-Murr-Kreis" ~ "08119",
      district == "Heilbronn" ~ "08121",
      district == "Landkreis Heilbronn" ~ "08125",
      district == "Hohenlohekreis" ~ "08126",
      district == "Schwäbisch Hall" ~ "08127",
      district == "Main-Tauber-Kreis" ~ "08128",
      district == "Heidenheim" ~ "08135",
      district == "Ostalbkreis" ~ "08136",
      district == "Karlsruhe" ~ "08212",
      district == "Landkreis Karlsruhe" ~ "08215",
      district == "Baden-Baden" ~ "08211",
      district == "Heidelberg" ~ "08221",
      district == "Mannheim" ~ "08222",
      district == "Rhein-Neckar-Kreis" ~ "08226",
      district == "Neckar-Odenwald-Kreis" ~ "08225",
      district == "Calw" ~ "08235",
      district == "Enzkreis" ~ "08236",
      district == "Freudenstadt" ~ "08237",
      district == "Freiburg im Breisgau" ~ "08311",
      district == "Breisgau-Hochschwarzwald" ~ "08315",
      district == "Emmendingen" ~ "08316",
      district == "Ortenaukreis" ~ "08317",
      district == "Rottweil" ~ "08325",
      district == "Schwarzwald-Baar-Kreis" ~ "08326",
      district == "Konstanz" ~ "08335",
      district == "Lörrach" ~ "08336",
      district == "Reutlingen" ~ "08415",
      district == "Tübingen" ~ "08416",
      district == "Zollernalbkreis" ~ "08417",
      district == "Ulm" ~ "08421",
      district == "Ravensburg" ~ "08436",
      district == "Sigmaringen" ~ "08437",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Baden-Württemberg",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_bw(constituency_key),
      ags = district_to_ags_bw(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Baden-Württemberg AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}
bw_sample <- clean_bw_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Baden-Württemberg.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  bw_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/BW_sample.csv"
)
```

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

bw_raw <- read_csv(
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Baden-Württemberg.csv",
  locale = locale(encoding = "UTF-8"),
  show_col_types = FALSE
)

bw_raw %>%
  count(Constituency, sort = TRUE) %>%
  print(n = 200)



```

Write to csv

```{r}
bw_sample_200 <- bw_speeches %>%
  filter(n_words > 30) %>%
  slice_sample(n = 200)

write_csv(
  bw_sample_200,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/BW_sample_200.csv"
)
```

# Bayern

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_by_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_by <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      constituency_key == "Mittelfranken Erlangen-Stadt" ~ "Erlangen",
      str_detect(constituency_key, "Nürnberg") ~ "Nürnberg",
      constituency_key == "Niederbayern Deggendorf" ~ "Deggendorf",
      constituency_key == "Niederbayern Dingolfing" ~ "Dingolfing-Landau",
      constituency_key == "Niederbayern Landshut" ~ "Landshut",
      constituency_key == "Oberbayern Eichstätt" ~ "Eichstätt",
      constituency_key == "Oberbayern Fürstenfeldbruck-Ost" ~ "Fürstenfeldbruck",
      constituency_key == "Oberbayern Mühldorf am Inn" ~ "Mühldorf a.Inn",
      str_detect(constituency_key, "München-Giesing|München-Milbertshofen|München-Pasing|München-Ramersdorf|München-Schwabing") ~ "München",
      constituency_key == "Oberbayern München-Land-Süd" ~ "München, Landkreis",
      constituency_key == "Oberfranken Bamberg-Stadt" ~ "Bamberg",
      constituency_key == "Oberfranken Bayreuth" ~ "Bayreuth",
      constituency_key == "Oberfranken Coburg" ~ "Coburg",
      constituency_key == "Oberfranken Forchheim" ~ "Forchheim",
      constituency_key == "Oberfranken Hof" ~ "Hof",
      constituency_key == "Oberpfalz Cham" ~ "Cham",
      constituency_key == "Oberpfalz Neumarkt in der Oberpfalz" ~ "Neumarkt i.d.OPf.",
      constituency_key == "Oberpfalz Regensburg-Stadt" ~ "Regensburg",
      constituency_key == "Oberpfalz Tirschenreuth" ~ "Tirschenreuth",
      constituency_key == "Oberpfalz Weiden in der Oberpfalz" ~ "Weiden i.d.OPf.",
      constituency_key == "Schwaben Aichach-Friedberg" ~ "Aichach-Friedberg",
      constituency_key == "Schwaben Neu-Ulm" ~ "Neu-Ulm",
      constituency_key == "Schwaben, Memmingen" ~ "Memmingen",
      constituency_key == "Unterfranken Aschaffenburg-Ost" ~ "Aschaffenburg",
      constituency_key == "Unterfranken Schweinfurt" ~ "Schweinfurt",
      constituency_key == "Unterfranken Würzburg-Land" ~ "Würzburg, Landkreis",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_by <- function(district) {
    case_when(
      district == "Erlangen" ~ "09562",
      district == "Nürnberg" ~ "09564",
      district == "Deggendorf" ~ "09271",
      district == "Dingolfing-Landau" ~ "09279",
      district == "Landshut" ~ "09261",
      district == "Eichstätt" ~ "09176",
      district == "Fürstenfeldbruck" ~ "09179",
      district == "Mühldorf a.Inn" ~ "09183",
      district == "München" ~ "09162",
      district == "München, Landkreis" ~ "09184",
      district == "Bamberg" ~ "09461",
      district == "Bayreuth" ~ "09462",
      district == "Coburg" ~ "09463",
      district == "Forchheim" ~ "09474",
      district == "Hof" ~ "09464",
      district == "Cham" ~ "09372",
      district == "Neumarkt i.d.OPf." ~ "09373",
      district == "Regensburg" ~ "09362",
      district == "Tirschenreuth" ~ "09377",
      district == "Weiden i.d.OPf." ~ "09363",
      district == "Aichach-Friedberg" ~ "09771",
      district == "Neu-Ulm" ~ "09775",
      district == "Memmingen" ~ "09764",
      district == "Aschaffenburg" ~ "09661",
      district == "Schweinfurt" ~ "09662",
      district == "Würzburg, Landkreis" ~ "09679",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Bayern",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_by(constituency_key),
      ags = district_to_ags_by(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Bayern AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

by_sample <- clean_by_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Bayern.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  by_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/BY_sample.csv"
)
```

```{r}
by_sample_200 <- by_speeches %>%
  filter(n_words > 30) %>%
  slice_sample(n = 200)

write_csv(
  by_sample_200,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/BY_sample_200.csv"
)
```

# Berlin

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_be_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_be <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      str_detect(constituency_key, "Berlin-Mitte|\\bMitte\\b|Wedding|Tiergarten|Moabit|Gesundbrunnen") ~ "Mitte",
      str_detect(constituency_key, "Friedrichshain|Kreuzberg") ~ "Friedrichshain-Kreuzberg",
      str_detect(constituency_key, "\\bPankow\\b|Prenzlauer Berg|Weissensee|Weißensee") ~ "Pankow",
      str_detect(constituency_key, "Charlottenburg|Wilmersdorf") ~ "Charlottenburg-Wilmersdorf",
      str_detect(constituency_key, "\\bSpandau\\b") ~ "Spandau",
      str_detect(constituency_key, "Steglitz|Zehlendorf") ~ "Steglitz-Zehlendorf",
      str_detect(constituency_key, "Tempelhof|Schoneberg|Schöneberg") ~ "Tempelhof-Schöneberg",
      str_detect(constituency_key, "Neukolln|Neukölln") ~ "Neukölln",
      str_detect(constituency_key, "Treptow|Kopenick|Köpenick") ~ "Treptow-Köpenick",
      str_detect(constituency_key, "Marzahn|Hellersdorf") ~ "Marzahn-Hellersdorf",
      str_detect(constituency_key, "\\bLichtenberg\\b|Hohenschonhausen|Hohenschönhausen") ~ "Lichtenberg",
      str_detect(constituency_key, "Reinickendorf") ~ "Reinickendorf",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_be <- function(district) {
    case_when(
      !is.na(district) ~ "11000",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Berlin",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_be(constituency_key),
      ags = district_to_ags_be(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Berlin AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

be_sample <- clean_be_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Berlin.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  be_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/BE_sample.csv"
)
```

```{r}
bl_sample_200 <- bl_speeches %>%
  filter(n_words > 30) %>%
  slice_sample(n = 200)

write_csv(
  bl_sample_200,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/BL_sample_200.csv"
)
```

# Brandenburg

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_bb_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_bb <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      str_detect(constituency_key, "^Barnim") ~ "Barnim",
      constituency_key == "Brandenburg an der Havel II" ~ "Brandenburg an der Havel",
      str_detect(constituency_key, "^Cottbus") ~ "Cottbus",
      str_detect(constituency_key, "^Dahme-Spreewald") ~ "Dahme-Spreewald",
      str_detect(constituency_key, "^Elbe-Elster") ~ "Elbe-Elster",
      constituency_key == "Frankfurt (Oder)" ~ "Frankfurt (Oder)",
      str_detect(constituency_key, "^Havelland") ~ "Havelland",
      str_detect(constituency_key, "^Märkisch-Oderland") ~ "Märkisch-Oderland",
      str_detect(constituency_key, "^Oberhavel") ~ "Oberhavel",
      constituency_key == "Oberspreewald-Lausitz I" ~ "Oberspreewald-Lausitz",
      str_detect(constituency_key, "^Oder-Spree") ~ "Oder-Spree",
      constituency_key == "Ostprignitz-Ruppin I" ~ "Ostprignitz-Ruppin",
      str_detect(constituency_key, "^Potsdam I|^Potsdam II") ~ "Potsdam",
      str_detect(constituency_key, "^Potsdam-Mittelmark") ~ "Potsdam-Mittelmark",
      str_detect(constituency_key, "^Teltow-Fläming") ~ "Teltow-Fläming",
      str_detect(constituency_key, "^Uckermark") ~ "Uckermark",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_bb <- function(district) {
    case_when(
      district == "Barnim" ~ "12060",
      district == "Brandenburg an der Havel" ~ "12051",
      district == "Cottbus" ~ "12052",
      district == "Dahme-Spreewald" ~ "12061",
      district == "Elbe-Elster" ~ "12062",
      district == "Frankfurt (Oder)" ~ "12053",
      district == "Havelland" ~ "12063",
      district == "Märkisch-Oderland" ~ "12064",
      district == "Oberhavel" ~ "12065",
      district == "Oberspreewald-Lausitz" ~ "12066",
      district == "Oder-Spree" ~ "12067",
      district == "Ostprignitz-Ruppin" ~ "12068",
      district == "Potsdam" ~ "12054",
      district == "Potsdam-Mittelmark" ~ "12069",
      district == "Teltow-Fläming" ~ "12072",
      district == "Uckermark" ~ "12073",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Brandenburg",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_bb(constituency_key),
      ags = district_to_ags_bb(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Brandenburg AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

bb_sample <- clean_bb_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Brandenburg.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  bb_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/BB_sample.csv"
)
```

```{r}
br_sample_200 <- br_speeches %>%
  filter(n_words > 30) %>%
  slice_sample(n = 200)

write_csv(
  br_sample_200,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/BR_sample_200.csv"
)
```

# Bremen

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_hb_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_hb <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      str_detect(constituency_key, "Bremerhaven") ~ "Bremerhaven",
      str_detect(constituency_key, "^Bremen$|Bremen-") ~ "Bremen",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_hb <- function(district) {
    case_when(
      district == "Bremen" ~ "04011",
      district == "Bremerhaven" ~ "04012",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Bremen",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_hb(constituency_key),
      ags = district_to_ags_hb(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Bremen AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

hb_sample <- clean_hb_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Bremen.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  hb_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/HB_sample.csv"
)
```

# Hamburg

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_hh_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_hh <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      # Hamburg-Mitte
      str_detect(constituency_key, "Hamburg-Mitte|Billstedt|Wilhelmsburg|Finkenwerder") ~ "Hamburg-Mitte",
      
      # Altona
      str_detect(constituency_key, "Altona|Blankenese|Altona-West") ~ "Altona",
      
      # Eimsbüttel
      str_detect(constituency_key, "Eimsbuttel|Eimsbüttel|Lokstedt|Niendorf|Schnelsen|Stellingen|Rotherbaum|Harvestehude") ~ "Eimsbüttel",
      
      # Hamburg-Nord
      str_detect(constituency_key, "Hamburg-Nord|Fuhlsbuttel|Fuhlsbüttel|Alsterdorf|Langenhorn|Barmbek|Uhlenhorst|Dulsberg|Winterhude") ~ "Hamburg-Nord",
      
      # Wandsbek
      str_detect(constituency_key, "Wandsbek|Bramfeld|Farmsen|Berne|Alstertal|Walddorfer|Walddörfer|Rahlstedt") ~ "Wandsbek",
      
      # Bergedorf
      str_detect(constituency_key, "Bergedorf") ~ "Bergedorf",
      
      # Harburg
      str_detect(constituency_key, "Harburg|Suderelbe|Süderelbe") ~ "Harburg",
      
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_hh <- function(district) {
    case_when(
      !is.na(district) ~ "02000",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Hamburg",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_hh(constituency_key),
      ags = district_to_ags_hh(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Hamburg AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

hh_sample <- clean_hh_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Hamburg.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  hh_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/HH_sample.csv"
)
```

# Hessen

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_he_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_he <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      str_detect(constituency_key, "^Bergstraße") ~ "Bergstraße",
      str_detect(constituency_key, "^Darmstadt-Dieburg") ~ "Darmstadt-Dieburg",
      constituency_key == "Darmstadt-Stadt I" ~ "Darmstadt",
      constituency_key == "Eschwege-Witzenhausen" ~ "Werra-Meißner-Kreis",
      str_detect(constituency_key, "^Frankfurt am Main") ~ "Frankfurt am Main",
      str_detect(constituency_key, "^Fulda") ~ "Fulda",
      str_detect(constituency_key, "^Gießen") ~ "Gießen",
      str_detect(constituency_key, "^Gross-Gerau|^Groß-Gerau") ~ "Groß-Gerau",
      str_detect(constituency_key, "^Hochtaunus") ~ "Hochtaunuskreis",
      str_detect(constituency_key, "^Kassel-Land") ~ "Kassel, Landkreis",
      str_detect(constituency_key, "^Kassel-Stadt") ~ "Kassel",
      str_detect(constituency_key, "^Lahn-Dill") ~ "Lahn-Dill-Kreis",
      str_detect(constituency_key, "^Limburg-Weilburg") ~ "Limburg-Weilburg",
      str_detect(constituency_key, "^Marburg-Biedenkopf") ~ "Marburg-Biedenkopf",
      constituency_key == "Odenwald" ~ "Odenwaldkreis",
      str_detect(constituency_key, "^Offenbach Land") ~ "Offenbach, Landkreis",
      constituency_key == "Offenbach-Stadt" ~ "Offenbach am Main",
      str_detect(constituency_key, "^Rheingau-Taunus") ~ "Rheingau-Taunus-Kreis",
      constituency_key == "Rotenburg" ~ "Hersfeld-Rotenburg",
      str_detect(constituency_key, "^Schwalm-Eder") ~ "Schwalm-Eder-Kreis",
      str_detect(constituency_key, "^Waldeck-Frankenberg") ~ "Waldeck-Frankenberg",
      str_detect(constituency_key, "^Wetterau") ~ "Wetteraukreis",
      str_detect(constituency_key, "^Wiesbaden") ~ "Wiesbaden",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_he <- function(district) {
    case_when(
      district == "Bergstraße" ~ "06431",
      district == "Darmstadt-Dieburg" ~ "06432",
      district == "Darmstadt" ~ "06411",
      district == "Werra-Meißner-Kreis" ~ "06636",
      district == "Frankfurt am Main" ~ "06412",
      district == "Fulda" ~ "06631",
      district == "Gießen" ~ "06531",
      district == "Groß-Gerau" ~ "06433",
      district == "Hochtaunuskreis" ~ "06434",
      district == "Kassel, Landkreis" ~ "06633",
      district == "Kassel" ~ "06611",
      district == "Lahn-Dill-Kreis" ~ "06532",
      district == "Limburg-Weilburg" ~ "06533",
      district == "Marburg-Biedenkopf" ~ "06534",
      district == "Odenwaldkreis" ~ "06437",
      district == "Offenbach, Landkreis" ~ "06438",
      district == "Offenbach am Main" ~ "06413",
      district == "Rheingau-Taunus-Kreis" ~ "06439",
      district == "Hersfeld-Rotenburg" ~ "06632",
      district == "Schwalm-Eder-Kreis" ~ "06634",
      district == "Waldeck-Frankenberg" ~ "06635",
      district == "Wetteraukreis" ~ "06440",
      district == "Wiesbaden" ~ "06414",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Hessen",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_he(constituency_key),
      ags = district_to_ags_he(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Hessen AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

he_sample <- clean_he_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Hessen.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  he_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/HE_sample.csv"
)
```

# Mecklenburg-Vorpommern

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_mv_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_mv <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      str_detect(constituency_key, "Greifswald|Uecker-Randow|Vorpommern-Greifswald") ~ "Vorpommern-Greifswald",
      str_detect(constituency_key, "Wismar|Nordwestmecklenburg") ~ "Nordwestmecklenburg",
      str_detect(constituency_key, "Ludwigslust|Parchim") ~ "Ludwigslust-Parchim",
      str_detect(constituency_key, "Neubrandenburg|Demmin|Müritz|Mecklenburg-Strelitz|Mecklenburgische Seenplatte") ~ "Mecklenburgische Seenplatte",
      str_detect(constituency_key, "Hansestadt Rostock|Rostock") ~ "Rostock",
      str_detect(constituency_key, "Stralsund|Rügen|Vorpommern-Rügen") ~ "Vorpommern-Rügen",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_mv <- function(district) {
    case_when(
      district == "Vorpommern-Greifswald" ~ "13075",
      district == "Nordwestmecklenburg" ~ "13074",
      district == "Ludwigslust-Parchim" ~ "13076",
      district == "Mecklenburgische Seenplatte" ~ "13071",
      district == "Rostock" ~ "13003",
      district == "Vorpommern-Rügen" ~ "13073",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Mecklenburg-Vorpommern",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_mv(constituency_key),
      ags = district_to_ags_mv(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Mecklenburg-Vorpommern AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

mv_sample <- clean_mv_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Mecklenburg-Vorpommern.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  mv_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/MV_sample.csv"
)
```

# Rheinland-Pfalz

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_rp_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_rp <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      constituency_key == "Alzey" ~ "Alzey-Worms",
      constituency_key == "Andernach" ~ "Mayen-Koblenz",
      constituency_key == "Bad Kreuznach" ~ "Bad Kreuznach",
      constituency_key == "Bad Marienberg (Westerwald)/Westerburg" ~ "Westerwaldkreis",
      constituency_key == "Bad Neuenahr-Ahrweiler" ~ "Ahrweiler",
      constituency_key == "Bendorf/Weißenthurm" ~ "Mayen-Koblenz",
      constituency_key == "Betzdorf/Kirchen (Sieg)" ~ "Altenkirchen (Westerwald)",
      constituency_key == "Donnersberg" ~ "Donnersbergkreis",
      constituency_key == "Frankenthal (Pfalz)" ~ "Frankenthal (Pfalz)",
      constituency_key == "Kaiserslautern I" ~ "Kaiserslautern",
      constituency_key == "Kaiserslautern II" ~ "Kaiserslautern, Landkreis",
      constituency_key == "Kirn/Bad Sobernheim" ~ "Bad Kreuznach",
      constituency_key == "Kusel" ~ "Kusel",
      constituency_key == "Linz am Rhein/Rengsdorf" ~ "Neuwied",
      str_detect(constituency_key, "^Mainz") ~ "Mainz",
      constituency_key == "Mayen" ~ "Mayen-Koblenz",
      constituency_key == "Montabaur" ~ "Westerwaldkreis",
      constituency_key == "Mutterstadt" ~ "Rhein-Pfalz-Kreis",
      constituency_key == "Neustadt an der Weinstraße" ~ "Neustadt an der Weinstraße",
      constituency_key == "Pirmasens" ~ "Pirmasens",
      constituency_key == "Remagen/Sinzig" ~ "Ahrweiler",
      constituency_key == "Rhein-Hunsrück" ~ "Rhein-Hunsrück-Kreis",
      constituency_key == "Speyer" ~ "Speyer",
      constituency_key == "Südliche Weinstraße" ~ "Südliche Weinstraße",
      constituency_key == "Trier" ~ "Trier",
      constituency_key == "Vulkaneifel" ~ "Vulkaneifel",
      constituency_key == "Wittlich" ~ "Bernkastel-Wittlich",
      constituency_key == "Zweibrücken" ~ "Zweibrücken",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_rp <- function(district) {
    case_when(
      district == "Alzey-Worms" ~ "07331",
      district == "Mayen-Koblenz" ~ "07137",
      district == "Bad Kreuznach" ~ "07133",
      district == "Westerwaldkreis" ~ "07143",
      district == "Ahrweiler" ~ "07131",
      district == "Altenkirchen (Westerwald)" ~ "07132",
      district == "Donnersbergkreis" ~ "07333",
      district == "Frankenthal (Pfalz)" ~ "07311",
      district == "Kaiserslautern" ~ "07312",
      district == "Kaiserslautern, Landkreis" ~ "07335",
      district == "Kusel" ~ "07336",
      district == "Neuwied" ~ "07138",
      district == "Mainz" ~ "07315",
      district == "Rhein-Pfalz-Kreis" ~ "07338",
      district == "Neustadt an der Weinstraße" ~ "07316",
      district == "Pirmasens" ~ "07317",
      district == "Rhein-Hunsrück-Kreis" ~ "07140",
      district == "Speyer" ~ "07318",
      district == "Südliche Weinstraße" ~ "07337",
      district == "Trier" ~ "07211",
      district == "Vulkaneifel" ~ "07233",
      district == "Bernkastel-Wittlich" ~ "07231",
      district == "Zweibrücken" ~ "07320",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Rheinland-Pfalz",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_rp(constituency_key),
      ags = district_to_ags_rp(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Rheinland-Pfalz AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

rp_sample <- clean_rp_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Rheinland-Pfalz.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  rp_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/RP_sample.csv"
)
```

# Saarland

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_sl_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_sl <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      constituency_key == "Neunkirchen" ~ "Neunkirchen",
      constituency_key == "Saarbrücken" ~ "Regionalverband Saarbrücken",
      constituency_key == "Saarlouis" ~ "Saarlouis",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_sl <- function(district) {
    case_when(
      district == "Neunkirchen" ~ "10043",
      district == "Regionalverband Saarbrücken" ~ "10041",
      district == "Saarlouis" ~ "10044",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Saarland",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_sl(constituency_key),
      ags = district_to_ags_sl(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Saarland AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

sl_sample <- clean_sl_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Saarland.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  sl_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/SL_sample.csv"
)
```

# Sachsen-Anhalt

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_st_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_st <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      constituency_key == "Salzwedel" ~ "Altmarkkreis Salzwedel",
      constituency_key %in% c("Havelberg-Osterburg", "Havelberg-Osterburg") ~ "Stendal",
      constituency_key %in% c("Genthin", "Burg") ~ "Jerichower Land",
      constituency_key %in% c("Wolmirstedt", "Oschersleben", "Wanzleben") ~ "Börde",
      str_detect(constituency_key, "^Magdeburg") ~ "Magdeburg",
      constituency_key %in% c("Halberstadt", "Blankenburg", "Wernigerode", "Quedlinburg") ~ "Harz",
      constituency_key %in% c("Staßfurt", "Aschersleben", "Schönebeck", "Bernburg") ~ "Salzlandkreis",
      constituency_key %in% c("Köthen", "Bitterfeld-Wolfen", "Wolfen") ~ "Anhalt-Bitterfeld",
      constituency_key %in% c("Wittenberg", "Jessen") ~ "Wittenberg",
      str_detect(constituency_key, "^Dessau-Roßlau$") ~ "Dessau-Roßlau",
      constituency_key %in% c("Sangerhausen", "Eisleben") ~ "Mansfeld-Südharz",
      constituency_key %in% c("Saalekreis", "Bad Dürrenberg-Saalekreis", "Merseburg", "Querfurt") ~ "Saalekreis",
      str_detect(constituency_key, "^Halle") ~ "Halle (Saale)",
      constituency_key %in% c("Zeitz", "Nebra") ~ "Burgenlandkreis",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_st <- function(district) {
    case_when(
      district == "Altmarkkreis Salzwedel" ~ "15081",
      district == "Stendal" ~ "15090",
      district == "Jerichower Land" ~ "15086",
      district == "Börde" ~ "15083",
      district == "Magdeburg" ~ "15003",
      district == "Harz" ~ "15085",
      district == "Salzlandkreis" ~ "15089",
      district == "Anhalt-Bitterfeld" ~ "15082",
      district == "Wittenberg" ~ "15091",
      district == "Dessau-Roßlau" ~ "15001",
      district == "Mansfeld-Südharz" ~ "15087",
      district == "Saalekreis" ~ "15088",
      district == "Halle (Saale)" ~ "15002",
      district == "Burgenlandkreis" ~ "15084",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Sachsen-Anhalt",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_st(constituency_key),
      ags = district_to_ags_st(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Sachsen-Anhalt AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

st_sample <- clean_st_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Sachsen-Anhalt.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  st_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/ST_sample.csv"
)
```

# Sachsen

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_sn_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  # Conservative Sachsen lookup created from constituency naming patterns:
  # map only when the constituency name clearly identifies a single Kreis/city.
  constituency_to_ags_sn <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      str_detect(constituency_key, "^Vogtland") ~ "14523",
      str_detect(constituency_key, "^Zwickau") ~ "14524",
      str_detect(constituency_key, "^Chemnitz") ~ "14511",
      str_detect(constituency_key, "^Erzgeb") ~ "14521",
      str_detect(constituency_key, "^Mittelsachsen") ~ "14522",
      str_detect(constituency_key, "^Dresden") ~ "14612",
      str_detect(constituency_key, "^Bautzen") ~ "14625",
      str_detect(constituency_key, "^Gorlitz|^Görlitz") ~ "14626",
      str_detect(constituency_key, "^Meissen|^Meißen") ~ "14627",
      str_detect(constituency_key, "^Sachsische Schweiz-Osterzgebirge|^Sächsische Schweiz-Osterzgebirge") ~ "14628",
      str_detect(constituency_key, "^Leipzig ") ~ "14713",
      str_detect(constituency_key, "^Nordsachsen") ~ "14730",
      TRUE ~ NA_character_
    )
  }
  
  ags_to_district_sn <- function(ags) {
    case_when(
      ags == "14523" ~ "Vogtlandkreis",
      ags == "14524" ~ "Zwickau",
      ags == "14511" ~ "Chemnitz",
      ags == "14521" ~ "Erzgebirgskreis",
      ags == "14522" ~ "Mittelsachsen",
      ags == "14612" ~ "Dresden",
      ags == "14625" ~ "Bautzen",
      ags == "14626" ~ "Görlitz",
      ags == "14627" ~ "Meißen",
      ags == "14628" ~ "Sächsische Schweiz-Osterzgebirge",
      ags == "14713" ~ "Leipzig",
      ags == "14730" ~ "Nordsachsen",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Sachsen",
      constituency_key = normalize_text(Constituency),
      ags = constituency_to_ags_sn(constituency_key),
      district = ags_to_district_sn(ags),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Sachsen AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

sn_sample <- clean_sn_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Sachsen.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  sn_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/SN_sample.csv"
)
```

# Schleswig-Holstein

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_sh_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_sh <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      constituency_key == "Dithmarschen-Süd" ~ "Dithmarschen",
      constituency_key == "Eckernförde" ~ "Rendsburg-Eckernförde",
      constituency_key == "Flensburg" ~ "Flensburg",
      constituency_key == "Flensburg-Land" ~ "Schleswig-Flensburg",
      constituency_key == "Kiel-Ost" ~ "Kiel",
      constituency_key == "Lauenburg-Nord" ~ "Herzogtum Lauenburg",
      constituency_key == "Lübeck-Süd" ~ "Lübeck",
      constituency_key == "Neumünster" ~ "Neumünster",
      constituency_key == "Nordfriesland-Nord" ~ "Nordfriesland",
      str_detect(constituency_key, "^Pinneberg") ~ "Pinneberg",
      constituency_key == "Plön-Nord" ~ "Plön",
      constituency_key == "Rendsburg" ~ "Rendsburg-Eckernförde",
      constituency_key == "Segeberg-Ost" ~ "Segeberg",
      str_detect(constituency_key, "^Steinburg") ~ "Steinburg",
      str_detect(constituency_key, "^Stormarn") ~ "Stormarn",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_sh <- function(district) {
    case_when(
      district == "Dithmarschen" ~ "01051",
      district == "Rendsburg-Eckernförde" ~ "01058",
      district == "Flensburg" ~ "01001",
      district == "Schleswig-Flensburg" ~ "01059",
      district == "Kiel" ~ "01002",
      district == "Herzogtum Lauenburg" ~ "01053",
      district == "Lübeck" ~ "01003",
      district == "Neumünster" ~ "01004",
      district == "Nordfriesland" ~ "01054",
      district == "Pinneberg" ~ "01056",
      district == "Plön" ~ "01057",
      district == "Segeberg" ~ "01060",
      district == "Steinburg" ~ "01061",
      district == "Stormarn" ~ "01062",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Schleswig-Holstein",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_sh(constituency_key),
      ags = district_to_ags_sh(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Schleswig-Holstein AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

sh_sample <- clean_sh_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Schleswig-Holstein.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  sh_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/SH_sample.csv"
)
```

# Thüringen

```{r}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)

clean_th_random_ags_subset <- function(file_path,
                                       start_date = "2013-01-01",
                                       end_date   = "2025-12-31",
                                       sample_n   = 500,
                                       seed       = 123) {
  
  normalize_text <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x <- str_squish(x)
    x <- str_replace_all(x, "[\u2010\u2011\u2012\u2013\u2014\u2212]", "-")
    x <- str_replace(x, "^\\d+\\s+", "")
    x
  }
  
  parse_mixed_date <- function(x) {
    x <- as.character(x)
    x <- str_trim(x)
    x[x %in% c("unknown", "NA", "", "null")] <- NA_character_
    
    x10 <- substr(x, 1, 10)
    
    out <- suppressWarnings(ymd(x10))
    out <- coalesce(out, suppressWarnings(dmy(x10)))
    out <- coalesce(out, suppressWarnings(mdy(x10)))
    
    out <- coalesce(out, suppressWarnings(ymd(x)))
    out <- coalesce(out, suppressWarnings(dmy(x)))
    out <- coalesce(out, suppressWarnings(mdy(x)))
    
    out
  }
  
  constituency_to_district_th <- function(constituency) {
    constituency_key <- normalize_text(constituency)
    
    case_when(
      str_detect(constituency_key, "^Eichsfeld") ~ "Eichsfeld",
      str_detect(constituency_key, "^Erfurt") ~ "Erfurt",
      str_detect(constituency_key, "^Gera") ~ "Gera",
      constituency_key == "Gotha II" ~ "Gotha",
      constituency_key == "Greiz I" ~ "Greiz",
      str_detect(constituency_key, "^Ilm-Kreis") ~ "Ilm-Kreis",
      str_detect(constituency_key, "^Jena") ~ "Jena",
      str_detect(constituency_key, "^Kyffhäuserkreis") ~ "Kyffhäuserkreis",
      str_detect(constituency_key, "^Nordhausen") ~ "Nordhausen",
      str_detect(constituency_key, "^Saale-Holzland-Kreis") ~ "Saale-Holzland-Kreis",
      str_detect(constituency_key, "^Saale-Orla-Kreis") ~ "Saale-Orla-Kreis",
      str_detect(constituency_key, "^Saalfeld-Rudolstadt") ~ "Saalfeld-Rudolstadt",
      constituency_key == "Schmalkalden-Meiningen II" ~ "Schmalkalden-Meiningen",
      constituency_key == "Sonneberg I" ~ "Sonneberg",
      constituency_key == "Sömmerda II" ~ "Sömmerda",
      str_detect(constituency_key, "^Unstrut-Hainich-Kreis") ~ "Unstrut-Hainich-Kreis",
      TRUE ~ NA_character_
    )
  }
  
  district_to_ags_th <- function(district) {
    case_when(
      district == "Eichsfeld" ~ "16061",
      district == "Erfurt" ~ "16051",
      district == "Gera" ~ "16052",
      district == "Gotha" ~ "16067",
      district == "Greiz" ~ "16076",
      district == "Ilm-Kreis" ~ "16070",
      district == "Jena" ~ "16053",
      district == "Kyffhäuserkreis" ~ "16065",
      district == "Nordhausen" ~ "16062",
      district == "Saale-Holzland-Kreis" ~ "16074",
      district == "Saale-Orla-Kreis" ~ "16075",
      district == "Saalfeld-Rudolstadt" ~ "16073",
      district == "Schmalkalden-Meiningen" ~ "16066",
      district == "Sonneberg" ~ "16072",
      district == "Sömmerda" ~ "16068",
      district == "Unstrut-Hainich-Kreis" ~ "16064",
      TRUE ~ NA_character_
    )
  }
  
  df <- read_csv(
    file_path,
    locale = locale(encoding = "UTF-8"),
    show_col_types = FALSE
  ) %>%
    rename_with(trimws)
  
  required_cols <- c(
    "Period", "Session", "Date", "Chair", "Interjection",
    "MPID", "Party", "Constituency", "Speech"
  )
  
  for (col in required_cols) {
    if (!col %in% names(df)) {
      df[[col]] <- NA
    }
  }
  
  df <- df %>%
    select(all_of(required_cols)) %>%
    mutate(
      Period = suppressWarnings(as.integer(Period)),
      Session = suppressWarnings(as.integer(Session)),
      MPID = suppressWarnings(as.integer(MPID)),
      
      Chair = case_when(
        Chair %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Chair %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Interjection = case_when(
        Interjection %in% c(TRUE, "TRUE", "true", 1, "1") ~ TRUE,
        Interjection %in% c(FALSE, "FALSE", "false", 0, "0") ~ FALSE,
        TRUE ~ NA
      ),
      
      Date = parse_mixed_date(Date),
      Speech = str_squish(as.character(Speech)),
      Party = as.character(Party),
      Constituency = as.character(Constituency)
    ) %>%
    filter(!is.na(Speech), Speech != "") %>%
    filter(!is.na(Date)) %>%
    filter(Date >= as.Date(start_date),
           Date <= as.Date(end_date))
  
  df_clean <- df %>%
    filter(is.na(Interjection) | Interjection == FALSE)
  
  df_clean <- df_clean %>%
    mutate(
      new_speech = case_when(
        row_number() == 1 ~ TRUE,
        Period != lag(Period) ~ TRUE,
        Session != lag(Session) ~ TRUE,
        Date != lag(Date) ~ TRUE,
        MPID != lag(MPID) ~ TRUE,
        Chair != lag(Chair) ~ TRUE,
        TRUE ~ FALSE
      ),
      speech_group = cumsum(new_speech)
    )
  
  speeches <- df_clean %>%
    group_by(speech_group) %>%
    summarise(
      Period = first(Period),
      Session = first(Session),
      Date = first(Date),
      MPID = first(MPID),
      Party = first(Party),
      Constituency = first(Constituency),
      Chair = first(Chair),
      Speech = str_squish(str_c(Speech, collapse = " ")),
      n_rows_merged = n(),
      .groups = "drop"
    ) %>%
    mutate(
      state = "Thüringen",
      constituency_key = normalize_text(Constituency),
      district = constituency_to_district_th(constituency_key),
      ags = district_to_ags_th(district),
      n_words = str_count(Speech, "\\S+")
    ) %>%
    filter(n_words >= 5) %>%
    filter(!is.na(district), !is.na(ags)) %>%
    select(
      state, ags, district, Period, Session, Date, MPID, Party,
      Constituency, constituency_key, Chair, Speech, n_rows_merged, n_words
    )
  
  set.seed(seed)
  
  n_to_sample <- min(sample_n, nrow(speeches))
  
  if (n_to_sample == 0) {
    warning("No speeches matched the Thüringen AGS mapping and date filters.")
    return(speeches)
  }
  
  sampled_speeches <- speeches %>%
    slice_sample(n = n_to_sample)
  
  return(sampled_speeches)
}

th_sample <- clean_th_random_ags_subset(
  file_path = "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Thüringen.csv",
  start_date = "2013-01-01",
  end_date   = "2025-12-31",
  sample_n   = 300,
  seed       = 42
)

write_csv(
  th_sample,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/TH_sample.csv"
)
```

# Merging Everything

```{r}
library(readr)
library(dplyr)

data_dir <- "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/200-speech samples"

library(readr)
library(dplyr)

data_dir <- "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/200-speech samples"

all_files <- list.files(
  path = data_dir,
  pattern = "\\.csv$",
  full.names = TRUE
)

length(all_files)
basename(all_files)

all_speeches <- lapply(all_files, function(f) {
  read_csv(f, show_col_types = FALSE)
}) %>%
  bind_rows()

dim(all_speeches)
names(all_speeches)

all_speeches %>% count(state, sort = TRUE)

write_csv(
  all_speeches,
  file.path(data_dir, "all_sample_200_merged.csv")
)
```

Loading the scored data

```{r}
all_sample_scored <- read.csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/all_sample_200_scored.csv")

all_sample_scored <- all_sample_scored %>%
  select(-ends_with("_y")) %>%
  rename_with(~ str_remove(.x, "_x$"), ends_with("_x"))
```

```{r}
library(dplyr)
library(stringr)
library(readr)

constituency_universe <- all_sample_scored %>%
  transmute(
    state,
    Constituency,
    constituency_name_std = Constituency %>%
      coalesce("") %>%
      str_to_lower() %>%
      str_squish()
  ) %>%
  distinct() %>%
  arrange(state, constituency_name_std)

constituency_universe

write_csv(
  constituency_universe,
  "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/constituency_universe.csv"
)
```

Cleaning

```{r}
library(dplyr)
library(stringr)
library(readr)

std_text <- function(x) {
  x %>%
    coalesce("") %>%
    str_replace_all("\u00a0", " ") %>%
    str_squish()
}

constituency_universe <- all_sample_scored %>%
  transmute(
    state = std_text(state),
    Constituency = std_text(Constituency)
  ) %>%
  distinct() %>%
  mutate(
    constituency_name_std = Constituency %>%
      str_to_lower() %>%
      str_squish(),
    constituency_key = Constituency %>%
      str_replace_all("\u00a0", " ") %>%
      str_squish() %>%
      str_remove("^\\d+\\s*") %>%                 # remove leading numbers like "01 "
      str_remove("^Wahlkreis\\s+") %>%           # remove "Wahlkreis "
      str_remove("^Bezirksliste\\s+") %>%        # remove "Bezirksliste "
      str_replace("^Landesliste( Platz \\d+)?$", "Landesliste") %>%
      str_replace("^nur Landesliste$", "Landesliste") %>%
      str_replace("^Listenmandat$", "Landesliste") %>%
      str_replace("^–$", "") %>%
      str_squish()
  )

constituency_universe
```

```{r}
constituency_to_kreis <- constituency_universe %>%
  mutate(
    kreis_name = case_when(

      # =========================
      # CITY STATES
      # =========================
      state == "Berlin" ~ "Berlin",
      state == "Hamburg" & constituency_key != "" ~ "Hamburg",
      state == "Bremen" & constituency_key %in% c("Bremen Listenwahl", "Bremen Personenwahl", "Bremen, Personenwahl") ~ "Bremen",
      state == "Bremen" & constituency_key == "Bremerhaven Listenwahl" ~ "Bremerhaven",

      # =========================
      # BADEN-WUERTTEMBERG
      # =========================
      state == "Baden-Württemberg" & str_detect(constituency_key, "^Stuttgart") ~ "Stuttgart",
      state == "Baden-Württemberg" & constituency_key == "Böblingen" ~ "Böblingen",
      state == "Baden-Württemberg" & constituency_key == "Leonberg" ~ "Böblingen",
      state == "Baden-Württemberg" & constituency_key == "Esslingen" ~ "Esslingen",
      state == "Baden-Württemberg" & constituency_key %in% c("Kirchheim", "Kirchheim unter Teck", "Nürtingen") ~ "Esslingen",
      state == "Baden-Württemberg" & constituency_key == "Göppingen" ~ "Göppingen",
      state == "Baden-Württemberg" & constituency_key == "Geislingen" ~ "Göppingen",
      state == "Baden-Württemberg" & constituency_key == "Ludwigsburg" ~ "Ludwigsburg",
      state == "Baden-Württemberg" & constituency_key %in% c("Vaihingen", "Bietigheim-Bissingen") ~ "Ludwigsburg",
      state == "Baden-Württemberg" & constituency_key %in% c("Waiblingen", "Schorndorf", "Backnang") ~ "Rems-Murr-Kreis",
      state == "Baden-Württemberg" & constituency_key == "Heilbronn" ~ "Heilbronn",
      state == "Baden-Württemberg" & constituency_key %in% c("Eppingen", "Neckarsulm") ~ "Landkreis Heilbronn",
      state == "Baden-Württemberg" & constituency_key == "Hohenlohe" ~ "Hohenlohekreis",
      state == "Baden-Württemberg" & constituency_key == "Schwäbisch Hall" ~ "Schwäbisch Hall",
      state == "Baden-Württemberg" & constituency_key == "Main-Tauber" ~ "Main-Tauber-Kreis",
      state == "Baden-Württemberg" & constituency_key == "Heidenheim" ~ "Heidenheim",
      state == "Baden-Württemberg" & constituency_key == "Schwäbisch Gmünd" ~ "Ostalbkreis",
      state == "Baden-Württemberg" & constituency_key == "Karlsruhe I" ~ "Karlsruhe",
      state == "Baden-Württemberg" & constituency_key %in% c("Bruchsal", "Ettlingen") ~ "Landkreis Karlsruhe",
      state == "Baden-Württemberg" & constituency_key == "Baden-Baden" ~ "Baden-Baden",
      state == "Baden-Württemberg" & constituency_key == "Heidelberg" ~ "Heidelberg",
      state == "Baden-Württemberg" & constituency_key %in% c("Mannheim I", "Mannheim II") ~ "Mannheim",
      state == "Baden-Württemberg" & constituency_key %in% c("Wiesloch", "Weinheim", "Schwetzingen", "Sinsheim") ~ "Rhein-Neckar-Kreis",
      state == "Baden-Württemberg" & constituency_key == "Neckar-Odenwald" ~ "Neckar-Odenwald-Kreis",
      state == "Baden-Württemberg" & constituency_key == "Calw" ~ "Calw",
      state == "Baden-Württemberg" & constituency_key == "Enz" ~ "Enzkreis",
      state == "Baden-Württemberg" & constituency_key == "Freudenstadt" ~ "Freudenstadt",
      state == "Baden-Württemberg" & str_detect(constituency_key, "^Freiburg") ~ "Freiburg im Breisgau",
      state == "Baden-Württemberg" & constituency_key == "Breisgau" ~ "Breisgau-Hochschwarzwald",
      state == "Baden-Württemberg" & constituency_key == "Emmendingen" ~ "Emmendingen",
      state == "Baden-Württemberg" & constituency_key == "Lahr" ~ "Ortenaukreis",
      state == "Baden-Württemberg" & constituency_key == "Rottweil" ~ "Rottweil",
      state == "Baden-Württemberg" & constituency_key == "Villingen-Schwenningen" ~ "Schwarzwald-Baar-Kreis",
      state == "Baden-Württemberg" & constituency_key == "Konstanz" ~ "Konstanz",
      state == "Baden-Württemberg" & constituency_key == "Singen" ~ "Konstanz",
      state == "Baden-Württemberg" & constituency_key == "Lörrach" ~ "Lörrach",
      state == "Baden-Württemberg" & constituency_key == "Reutlingen" ~ "Reutlingen",
      state == "Baden-Württemberg" & constituency_key == "Tübingen" ~ "Tübingen",
      state == "Baden-Württemberg" & constituency_key == "Balingen" ~ "Zollernalbkreis",
      state == "Baden-Württemberg" & constituency_key == "Ulm" ~ "Ulm",
      state == "Baden-Württemberg" & constituency_key == "Ravensburg" ~ "Ravensburg",
      state == "Baden-Württemberg" & constituency_key == "Sigmaringen" ~ "Sigmaringen",

      # =========================
      # BAYERN
      # =========================
      state == "Bayern" & constituency_key == "Mittelfranken Erlangen-Stadt" ~ "Erlangen",
      state == "Bayern" & str_detect(constituency_key, "Nürnberg") ~ "Nürnberg",
      state == "Bayern" & constituency_key == "Niederbayern Deggendorf" ~ "Deggendorf",
      state == "Bayern" & constituency_key == "Niederbayern Dingolfing" ~ "Dingolfing-Landau",
      state == "Bayern" & constituency_key == "Niederbayern Landshut" ~ "Landshut",
      state == "Bayern" & constituency_key == "Oberbayern Eichstätt" ~ "Eichstätt",
      state == "Bayern" & constituency_key == "Oberbayern Fürstenfeldbruck-Ost" ~ "Fürstenfeldbruck",
      state == "Bayern" & constituency_key == "Oberbayern Mühldorf am Inn" ~ "Mühldorf a.Inn",
      state == "Bayern" & str_detect(constituency_key, "München-Giesing|München-Milbertshofen|München-Pasing|München-Ramersdorf|München-Schwabing") ~ "München",
      state == "Bayern" & constituency_key == "Oberbayern München-Land-Süd" ~ "München, Landkreis",
      state == "Bayern" & constituency_key == "Oberfranken Bamberg-Stadt" ~ "Bamberg",
      state == "Bayern" & constituency_key == "Oberfranken Bayreuth" ~ "Bayreuth",
      state == "Bayern" & constituency_key == "Oberfranken Coburg" ~ "Coburg",
      state == "Bayern" & constituency_key == "Oberfranken Forchheim" ~ "Forchheim",
      state == "Bayern" & constituency_key == "Oberfranken Hof" ~ "Hof",
      state == "Bayern" & constituency_key == "Oberpfalz Cham" ~ "Cham",
      state == "Bayern" & constituency_key == "Oberpfalz Neumarkt in der Oberpfalz" ~ "Neumarkt i.d.OPf.",
      state == "Bayern" & constituency_key == "Oberpfalz Regensburg-Stadt" ~ "Regensburg",
      state == "Bayern" & constituency_key == "Oberpfalz Tirschenreuth" ~ "Tirschenreuth",
      state == "Bayern" & constituency_key == "Oberpfalz Weiden in der Oberpfalz" ~ "Weiden i.d.OPf.",
      state == "Bayern" & constituency_key == "Schwaben Aichach-Friedberg" ~ "Aichach-Friedberg",
      state == "Bayern" & constituency_key == "Schwaben Neu-Ulm" ~ "Neu-Ulm",
      state == "Bayern" & constituency_key == "Schwaben, Memmingen" ~ "Memmingen",
      state == "Bayern" & constituency_key == "Unterfranken Aschaffenburg-Ost" ~ "Aschaffenburg",
      state == "Bayern" & constituency_key == "Unterfranken Schweinfurt" ~ "Schweinfurt",
      state == "Bayern" & constituency_key == "Unterfranken Würzburg-Land" ~ "Würzburg, Landkreis",

      # =========================
      # BRANDENBURG
      # =========================
      state == "Brandenburg" & str_detect(constituency_key, "^Barnim") ~ "Barnim",
      state == "Brandenburg" & constituency_key == "Brandenburg an der Havel II" ~ "Brandenburg an der Havel",
      state == "Brandenburg" & str_detect(constituency_key, "^Cottbus") ~ "Cottbus",
      state == "Brandenburg" & str_detect(constituency_key, "^Dahme-Spreewald") ~ "Dahme-Spreewald",
      state == "Brandenburg" & str_detect(constituency_key, "^Elbe-Elster") ~ "Elbe-Elster",
      state == "Brandenburg" & constituency_key == "Frankfurt (Oder)" ~ "Frankfurt (Oder)",
      state == "Brandenburg" & str_detect(constituency_key, "^Havelland") ~ "Havelland",
      state == "Brandenburg" & str_detect(constituency_key, "^Märkisch-Oderland") ~ "Märkisch-Oderland",
      state == "Brandenburg" & str_detect(constituency_key, "^Oberhavel") ~ "Oberhavel",
      state == "Brandenburg" & constituency_key == "Oberspreewald-Lausitz I" ~ "Oberspreewald-Lausitz",
      state == "Brandenburg" & str_detect(constituency_key, "^Oder-Spree") ~ "Oder-Spree",
      state == "Brandenburg" & constituency_key == "Ostprignitz-Ruppin I" ~ "Ostprignitz-Ruppin",
      state == "Brandenburg" & str_detect(constituency_key, "^Potsdam I|^Potsdam II") ~ "Potsdam",
      state == "Brandenburg" & str_detect(constituency_key, "^Potsdam-Mittelmark") ~ "Potsdam-Mittelmark",
      state == "Brandenburg" & str_detect(constituency_key, "^Teltow-Fläming") ~ "Teltow-Fläming",
      state == "Brandenburg" & str_detect(constituency_key, "^Uckermark") ~ "Uckermark",

      # =========================
      # HESSEN
      # =========================
      state == "Hessen" & str_detect(constituency_key, "^Bergstraße") ~ "Bergstraße",
      state == "Hessen" & str_detect(constituency_key, "^Darmstadt-Dieburg") ~ "Darmstadt-Dieburg",
      state == "Hessen" & constituency_key == "Darmstadt-Stadt I" ~ "Darmstadt",
      state == "Hessen" & constituency_key == "Eschwege-Witzenhausen" ~ "Werra-Meißner-Kreis",
      state == "Hessen" & str_detect(constituency_key, "^Frankfurt am Main") ~ "Frankfurt am Main",
      state == "Hessen" & str_detect(constituency_key, "^Fulda") ~ "Fulda",
      state == "Hessen" & str_detect(constituency_key, "^Gießen") ~ "Gießen",
      state == "Hessen" & str_detect(constituency_key, "^Groß-Gerau") ~ "Groß-Gerau",
      state == "Hessen" & str_detect(constituency_key, "^Hochtaunus") ~ "Hochtaunuskreis",
      state == "Hessen" & str_detect(constituency_key, "^Kassel-Land") ~ "Kassel, Landkreis",
      state == "Hessen" & str_detect(constituency_key, "^Kassel-Stadt") ~ "Kassel",
      state == "Hessen" & str_detect(constituency_key, "^Lahn-Dill") ~ "Lahn-Dill-Kreis",
      state == "Hessen" & str_detect(constituency_key, "^Limburg-Weilburg") ~ "Limburg-Weilburg",
      state == "Hessen" & str_detect(constituency_key, "^Marburg-Biedenkopf") ~ "Marburg-Biedenkopf",
      state == "Hessen" & constituency_key == "Odenwald" ~ "Odenwaldkreis",
      state == "Hessen" & str_detect(constituency_key, "^Offenbach Land") ~ "Offenbach, Landkreis",
      state == "Hessen" & constituency_key == "Offenbach-Stadt" ~ "Offenbach am Main",
      state == "Hessen" & str_detect(constituency_key, "^Rheingau-Taunus") ~ "Rheingau-Taunus-Kreis",
      state == "Hessen" & constituency_key == "Rotenburg" ~ "Hersfeld-Rotenburg",
      state == "Hessen" & str_detect(constituency_key, "^Schwalm-Eder") ~ "Schwalm-Eder-Kreis",
      state == "Hessen" & str_detect(constituency_key, "^Waldeck-Frankenberg") ~ "Waldeck-Frankenberg",
      state == "Hessen" & str_detect(constituency_key, "^Wetterau") ~ "Wetteraukreis",
      state == "Hessen" & str_detect(constituency_key, "^Wiesbaden") ~ "Wiesbaden",

      # =========================
      # MECKLENBURG-VORPOMMERN
      # =========================
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Greifswald|Uecker-Randow|Vorpommern-Greifswald") ~ "Vorpommern-Greifswald",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Wismar|Nordwestmecklenburg") ~ "Nordwestmecklenburg",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Ludwigslust|Parchim") ~ "Ludwigslust-Parchim",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Neubrandenburg|Demmin|Müritz|Mecklenburg-Strelitz|Mecklenburgische Seenplatte") ~ "Mecklenburgische Seenplatte",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Hansestadt Rostock|Rostock") ~ "Rostock",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Stralsund|Rügen|Vorpommern-Rügen") ~ "Vorpommern-Rügen",

      # =========================
      # RHEINLAND-PFALZ
      # =========================
      state == "Rheinland-Pfalz" & constituency_key == "Alzey" ~ "Alzey-Worms",
      state == "Rheinland-Pfalz" & constituency_key == "Andernach" ~ "Mayen-Koblenz",
      state == "Rheinland-Pfalz" & constituency_key == "Bad Kreuznach" ~ "Bad Kreuznach",
      state == "Rheinland-Pfalz" & constituency_key == "Bad Marienberg (Westerwald)/Westerburg" ~ "Westerwaldkreis",
      state == "Rheinland-Pfalz" & constituency_key == "Bad Neuenahr-Ahrweiler" ~ "Ahrweiler",
      state == "Rheinland-Pfalz" & constituency_key == "Bendorf/Weißenthurm" ~ "Mayen-Koblenz",
      state == "Rheinland-Pfalz" & constituency_key == "Betzdorf/Kirchen (Sieg)" ~ "Altenkirchen (Westerwald)",
      state == "Rheinland-Pfalz" & constituency_key == "Donnersberg" ~ "Donnersbergkreis",
      state == "Rheinland-Pfalz" & constituency_key == "Frankenthal (Pfalz)" ~ "Frankenthal (Pfalz)",
      state == "Rheinland-Pfalz" & constituency_key == "Kaiserslautern I" ~ "Kaiserslautern",
      state == "Rheinland-Pfalz" & constituency_key == "Kaiserslautern II" ~ "Kaiserslautern, Landkreis",
      state == "Rheinland-Pfalz" & constituency_key == "Kirn/Bad Sobernheim" ~ "Bad Kreuznach",
      state == "Rheinland-Pfalz" & constituency_key == "Kusel" ~ "Kusel",
      state == "Rheinland-Pfalz" & constituency_key == "Linz am Rhein/Rengsdorf" ~ "Neuwied",
      state == "Rheinland-Pfalz" & str_detect(constituency_key, "^Mainz") ~ "Mainz",
      state == "Rheinland-Pfalz" & constituency_key == "Mayen" ~ "Mayen-Koblenz",
      state == "Rheinland-Pfalz" & constituency_key == "Montabaur" ~ "Westerwaldkreis",
      state == "Rheinland-Pfalz" & constituency_key == "Mutterstadt" ~ "Rhein-Pfalz-Kreis",
      state == "Rheinland-Pfalz" & constituency_key == "Neustadt an der Weinstraße" ~ "Neustadt an der Weinstraße",
      state == "Rheinland-Pfalz" & constituency_key == "Pirmasens" ~ "Pirmasens",
      state == "Rheinland-Pfalz" & constituency_key == "Remagen/Sinzig" ~ "Ahrweiler",
      state == "Rheinland-Pfalz" & constituency_key == "Rhein-Hunsrück" ~ "Rhein-Hunsrück-Kreis",
      state == "Rheinland-Pfalz" & constituency_key == "Speyer" ~ "Speyer",
      state == "Rheinland-Pfalz" & constituency_key == "Südliche Weinstraße" ~ "Südliche Weinstraße",
      state == "Rheinland-Pfalz" & constituency_key == "Trier" ~ "Trier",
      state == "Rheinland-Pfalz" & constituency_key == "Vulkaneifel" ~ "Vulkaneifel",
      state == "Rheinland-Pfalz" & constituency_key == "Wittlich" ~ "Bernkastel-Wittlich",
      state == "Rheinland-Pfalz" & constituency_key == "Zweibrücken" ~ "Zweibrücken",

      # =========================
      # SAARLAND
      # =========================
      state == "Saarland" & constituency_key == "Neunkirchen" ~ "Neunkirchen",
      state == "Saarland" & constituency_key == "Saarbrücken" ~ "Regionalverband Saarbrücken",
      state == "Saarland" & constituency_key == "Saarlouis" ~ "Saarlouis",

      # =========================
      # SACHSEN-ANHALT
      # =========================
      state == "Sachsen-Anhalt" & constituency_key == "Salzwedel" ~ "Altmarkkreis Salzwedel",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Havelberg-Osterburg", "Havelberg-Osterburg") ~ "Stendal",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Genthin", "Burg") ~ "Jerichower Land",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Wolmirstedt", "Oschersleben", "Wanzleben") ~ "Börde",
      state == "Sachsen-Anhalt" & str_detect(constituency_key, "^Magdeburg") ~ "Magdeburg",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Halberstadt", "Blankenburg", "Wernigerode", "Quedlinburg") ~ "Harz",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Staßfurt", "Aschersleben", "Schönebeck", "Bernburg") ~ "Salzlandkreis",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Köthen", "Bitterfeld-Wolfen", "Wolfen") ~ "Anhalt-Bitterfeld",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Wittenberg", "Jessen") ~ "Wittenberg",
      state == "Sachsen-Anhalt" & str_detect(constituency_key, "^Dessau-Roßlau$") ~ "Dessau-Roßlau",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Sangerhausen", "Eisleben") ~ "Mansfeld-Südharz",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Saalekreis", "Bad Dürrenberg-Saalekreis", "Merseburg", "Querfurt") ~ "Saalekreis",
      state == "Sachsen-Anhalt" & str_detect(constituency_key, "^Halle") ~ "Halle (Saale)",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Zeitz", "Nebra") ~ "Burgenlandkreis",

      # =========================
      # SCHLESWIG-HOLSTEIN
      # =========================
      state == "Schleswig-Holstein" & constituency_key == "Dithmarschen-Süd" ~ "Dithmarschen",
      state == "Schleswig-Holstein" & constituency_key == "Eckernförde" ~ "Rendsburg-Eckernförde",
      state == "Schleswig-Holstein" & constituency_key == "Flensburg" ~ "Flensburg",
      state == "Schleswig-Holstein" & constituency_key == "Flensburg-Land" ~ "Schleswig-Flensburg",
      state == "Schleswig-Holstein" & constituency_key == "Kiel-Ost" ~ "Kiel",
      state == "Schleswig-Holstein" & constituency_key == "Lauenburg-Nord" ~ "Herzogtum Lauenburg",
      state == "Schleswig-Holstein" & constituency_key == "Lübeck-Süd" ~ "Lübeck",
      state == "Schleswig-Holstein" & constituency_key == "Neumünster" ~ "Neumünster",
      state == "Schleswig-Holstein" & constituency_key == "Nordfriesland-Nord" ~ "Nordfriesland",
      state == "Schleswig-Holstein" & str_detect(constituency_key, "^Pinneberg") ~ "Pinneberg",
      state == "Schleswig-Holstein" & constituency_key == "Plön-Nord" ~ "Plön",
      state == "Schleswig-Holstein" & constituency_key == "Rendsburg" ~ "Rendsburg-Eckernförde",
      state == "Schleswig-Holstein" & constituency_key == "Segeberg-Ost" ~ "Segeberg",
      state == "Schleswig-Holstein" & str_detect(constituency_key, "^Steinburg") ~ "Steinburg",
      state == "Schleswig-Holstein" & str_detect(constituency_key, "^Stormarn") ~ "Stormarn",

      # =========================
      # THUERINGEN
      # =========================
      state == "Thüringen" & str_detect(constituency_key, "^Eichsfeld") ~ "Eichsfeld",
      state == "Thüringen" & str_detect(constituency_key, "^Erfurt") ~ "Erfurt",
      state == "Thüringen" & str_detect(constituency_key, "^Gera") ~ "Gera",
      state == "Thüringen" & constituency_key == "Gotha II" ~ "Gotha",
      state == "Thüringen" & constituency_key == "Greiz I" ~ "Greiz",
      state == "Thüringen" & str_detect(constituency_key, "^Ilm-Kreis") ~ "Ilm-Kreis",
      state == "Thüringen" & str_detect(constituency_key, "^Jena") ~ "Jena",
      state == "Thüringen" & str_detect(constituency_key, "^Kyffhäuserkreis") ~ "Kyffhäuserkreis",
      state == "Thüringen" & str_detect(constituency_key, "^Nordhausen") ~ "Nordhausen",
      state == "Thüringen" & str_detect(constituency_key, "^Saale-Holzland-Kreis") ~ "Saale-Holzland-Kreis",
      state == "Thüringen" & str_detect(constituency_key, "^Saale-Orla-Kreis") ~ "Saale-Orla-Kreis",
      state == "Thüringen" & str_detect(constituency_key, "^Saalfeld-Rudolstadt") ~ "Saalfeld-Rudolstadt",
      state == "Thüringen" & constituency_key == "Schmalkalden-Meiningen II" ~ "Schmalkalden-Meiningen",
      state == "Thüringen" & constituency_key == "Sonneberg I" ~ "Sonneberg",
      state == "Thüringen" & constituency_key == "Sömmerda II" ~ "Sömmerda",
      state == "Thüringen" & str_detect(constituency_key, "^Unstrut-Hainich-Kreis") ~ "Unstrut-Hainich-Kreis",

      TRUE ~ NA_character_
    ),

    ags = case_when(

      # =========================
      # CITY STATES
      # =========================
      state == "Berlin" ~ "11000",
      state == "Hamburg" & constituency_key != "" ~ "02000",
      state == "Bremen" & constituency_key %in% c("Bremen Listenwahl", "Bremen Personenwahl", "Bremen, Personenwahl") ~ "04011",
      state == "Bremen" & constituency_key == "Bremerhaven Listenwahl" ~ "04012",

      # =========================
      # BADEN-WUERTTEMBERG
      # =========================
      state == "Baden-Württemberg" & str_detect(constituency_key, "^Stuttgart") ~ "08111",
      state == "Baden-Württemberg" & constituency_key == "Böblingen" ~ "08115",
      state == "Baden-Württemberg" & constituency_key == "Leonberg" ~ "08115",
      state == "Baden-Württemberg" & constituency_key == "Esslingen" ~ "08116",
      state == "Baden-Württemberg" & constituency_key %in% c("Kirchheim", "Kirchheim unter Teck", "Nürtingen") ~ "08116",
      state == "Baden-Württemberg" & constituency_key == "Göppingen" ~ "08117",
      state == "Baden-Württemberg" & constituency_key == "Geislingen" ~ "08117",
      state == "Baden-Württemberg" & constituency_key == "Ludwigsburg" ~ "08118",
      state == "Baden-Württemberg" & constituency_key %in% c("Vaihingen", "Bietigheim-Bissingen") ~ "08118",
      state == "Baden-Württemberg" & constituency_key %in% c("Waiblingen", "Schorndorf", "Backnang") ~ "08119",
      state == "Baden-Württemberg" & constituency_key == "Heilbronn" ~ "08125",
      state == "Baden-Württemberg" & constituency_key %in% c("Eppingen", "Neckarsulm") ~ "08125",
      state == "Baden-Württemberg" & constituency_key == "Hohenlohe" ~ "08126",
      state == "Baden-Württemberg" & constituency_key == "Schwäbisch Hall" ~ "08127",
      state == "Baden-Württemberg" & constituency_key == "Main-Tauber" ~ "08128",
      state == "Baden-Württemberg" & constituency_key == "Heidenheim" ~ "08135",
      state == "Baden-Württemberg" & constituency_key == "Schwäbisch Gmünd" ~ "08136",
      state == "Baden-Württemberg" & constituency_key == "Karlsruhe I" ~ "08212",
      state == "Baden-Württemberg" & constituency_key %in% c("Bruchsal", "Ettlingen") ~ "08215",
      state == "Baden-Württemberg" & constituency_key == "Baden-Baden" ~ "08211",
      state == "Baden-Württemberg" & constituency_key == "Heidelberg" ~ "08221",
      state == "Baden-Württemberg" & constituency_key %in% c("Mannheim I", "Mannheim II") ~ "08222",
      state == "Baden-Württemberg" & constituency_key %in% c("Wiesloch", "Weinheim", "Schwetzingen", "Sinsheim") ~ "08226",
      state == "Baden-Württemberg" & constituency_key == "Neckar-Odenwald" ~ "08225",
      state == "Baden-Württemberg" & constituency_key == "Calw" ~ "08235",
      state == "Baden-Württemberg" & constituency_key == "Enz" ~ "08236",
      state == "Baden-Württemberg" & constituency_key == "Freudenstadt" ~ "08237",
      state == "Baden-Württemberg" & str_detect(constituency_key, "^Freiburg") ~ "08311",
      state == "Baden-Württemberg" & constituency_key == "Breisgau" ~ "08315",
      state == "Baden-Württemberg" & constituency_key == "Emmendingen" ~ "08316",
      state == "Baden-Württemberg" & constituency_key == "Lahr" ~ "08317",
      state == "Baden-Württemberg" & constituency_key == "Rottweil" ~ "08325",
      state == "Baden-Württemberg" & constituency_key == "Villingen-Schwenningen" ~ "08326",
      state == "Baden-Württemberg" & constituency_key == "Konstanz" ~ "08335",
      state == "Baden-Württemberg" & constituency_key == "Singen" ~ "08335",
      state == "Baden-Württemberg" & constituency_key == "Lörrach" ~ "08336",
      state == "Baden-Württemberg" & constituency_key == "Reutlingen" ~ "08415",
      state == "Baden-Württemberg" & constituency_key == "Tübingen" ~ "08416",
      state == "Baden-Württemberg" & constituency_key == "Balingen" ~ "08417",
      state == "Baden-Württemberg" & constituency_key == "Ulm" ~ "08421",
      state == "Baden-Württemberg" & constituency_key == "Ravensburg" ~ "08436",
      state == "Baden-Württemberg" & constituency_key == "Sigmaringen" ~ "08437",

      # =========================
      # BAYERN
      # =========================
      state == "Bayern" & constituency_key == "Mittelfranken Erlangen-Stadt" ~ "09562",
      state == "Bayern" & str_detect(constituency_key, "Nürnberg") ~ "09564",
      state == "Bayern" & constituency_key == "Niederbayern Deggendorf" ~ "09271",
      state == "Bayern" & constituency_key == "Niederbayern Dingolfing" ~ "09279",
      state == "Bayern" & constituency_key == "Niederbayern Landshut" ~ "09274",
      state == "Bayern" & constituency_key == "Oberbayern Eichstätt" ~ "09176",
      state == "Bayern" & constituency_key == "Oberbayern Fürstenfeldbruck-Ost" ~ "09179",
      state == "Bayern" & constituency_key == "Oberbayern Mühldorf am Inn" ~ "09183",
      state == "Bayern" & str_detect(constituency_key, "München-Giesing|München-Milbertshofen|München-Pasing|München-Ramersdorf|München-Schwabing") ~ "09162",
      state == "Bayern" & constituency_key == "Oberbayern München-Land-Süd" ~ "09184",
      state == "Bayern" & constituency_key == "Oberfranken Bamberg-Stadt" ~ "09461",
      state == "Bayern" & constituency_key == "Oberfranken Bayreuth" ~ "09462",
      state == "Bayern" & constituency_key == "Oberfranken Coburg" ~ "09463",
      state == "Bayern" & constituency_key == "Oberfranken Forchheim" ~ "09474",
      state == "Bayern" & constituency_key == "Oberfranken Hof" ~ "09464",
      state == "Bayern" & constituency_key == "Oberpfalz Cham" ~ "09372",
      state == "Bayern" & constituency_key == "Oberpfalz Neumarkt in der Oberpfalz" ~ "09373",
      state == "Bayern" & constituency_key == "Oberpfalz Regensburg-Stadt" ~ "09362",
      state == "Bayern" & constituency_key == "Oberpfalz Tirschenreuth" ~ "09377",
      state == "Bayern" & constituency_key == "Oberpfalz Weiden in der Oberpfalz" ~ "09363",
      state == "Bayern" & constituency_key == "Schwaben Aichach-Friedberg" ~ "09771",
      state == "Bayern" & constituency_key == "Schwaben Neu-Ulm" ~ "09775",
      state == "Bayern" & constituency_key == "Schwaben, Memmingen" ~ "09764",
      state == "Bayern" & constituency_key == "Unterfranken Aschaffenburg-Ost" ~ "09661",
      state == "Bayern" & constituency_key == "Unterfranken Schweinfurt" ~ "09662",
      state == "Bayern" & constituency_key == "Unterfranken Würzburg-Land" ~ "09679",

      # =========================
      # BRANDENBURG
      # =========================
      state == "Brandenburg" & str_detect(constituency_key, "^Barnim") ~ "12060",
      state == "Brandenburg" & constituency_key == "Brandenburg an der Havel II" ~ "12051",
      state == "Brandenburg" & str_detect(constituency_key, "^Cottbus") ~ "12052",
      state == "Brandenburg" & str_detect(constituency_key, "^Dahme-Spreewald") ~ "12061",
      state == "Brandenburg" & str_detect(constituency_key, "^Elbe-Elster") ~ "12062",
      state == "Brandenburg" & constituency_key == "Frankfurt (Oder)" ~ "12053",
      state == "Brandenburg" & str_detect(constituency_key, "^Havelland") ~ "12063",
      state == "Brandenburg" & str_detect(constituency_key, "^Märkisch-Oderland") ~ "12064",
      state == "Brandenburg" & str_detect(constituency_key, "^Oberhavel") ~ "12065",
      state == "Brandenburg" & constituency_key == "Oberspreewald-Lausitz I" ~ "12066",
      state == "Brandenburg" & str_detect(constituency_key, "^Oder-Spree") ~ "12067",
      state == "Brandenburg" & constituency_key == "Ostprignitz-Ruppin I" ~ "12068",
      state == "Brandenburg" & str_detect(constituency_key, "^Potsdam I|^Potsdam II") ~ "12054",
      state == "Brandenburg" & str_detect(constituency_key, "^Potsdam-Mittelmark") ~ "12069",
      state == "Brandenburg" & str_detect(constituency_key, "^Teltow-Fläming") ~ "12072",
      state == "Brandenburg" & str_detect(constituency_key, "^Uckermark") ~ "12073",

      # =========================
      # HESSEN
      # =========================
      state == "Hessen" & str_detect(constituency_key, "^Bergstraße") ~ "06431",
      state == "Hessen" & str_detect(constituency_key, "^Darmstadt-Dieburg") ~ "06432",
      state == "Hessen" & constituency_key == "Darmstadt-Stadt I" ~ "06411",
      state == "Hessen" & constituency_key == "Eschwege-Witzenhausen" ~ "06636",
      state == "Hessen" & str_detect(constituency_key, "^Frankfurt am Main") ~ "06412",
      state == "Hessen" & str_detect(constituency_key, "^Fulda") ~ "06631",
      state == "Hessen" & str_detect(constituency_key, "^Gießen") ~ "06531",
      state == "Hessen" & str_detect(constituency_key, "^Groß-Gerau") ~ "06433",
      state == "Hessen" & str_detect(constituency_key, "^Hochtaunus") ~ "06434",
      state == "Hessen" & str_detect(constituency_key, "^Kassel-Land") ~ "06633",
      state == "Hessen" & str_detect(constituency_key, "^Kassel-Stadt") ~ "06611",
      state == "Hessen" & str_detect(constituency_key, "^Lahn-Dill") ~ "06532",
      state == "Hessen" & str_detect(constituency_key, "^Limburg-Weilburg") ~ "06533",
      state == "Hessen" & str_detect(constituency_key, "^Marburg-Biedenkopf") ~ "06534",
      state == "Hessen" & constituency_key == "Odenwald" ~ "06437",
      state == "Hessen" & str_detect(constituency_key, "^Offenbach Land") ~ "06438",
      state == "Hessen" & constituency_key == "Offenbach-Stadt" ~ "06413",
      state == "Hessen" & str_detect(constituency_key, "^Rheingau-Taunus") ~ "06439",
      state == "Hessen" & constituency_key == "Rotenburg" ~ "06632",
      state == "Hessen" & str_detect(constituency_key, "^Schwalm-Eder") ~ "06634",
      state == "Hessen" & str_detect(constituency_key, "^Waldeck-Frankenberg") ~ "06635",
      state == "Hessen" & str_detect(constituency_key, "^Wetterau") ~ "06440",
      state == "Hessen" & str_detect(constituency_key, "^Wiesbaden") ~ "06414",

      # =========================
      # MECKLENBURG-VORPOMMERN
      # =========================
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Greifswald|Uecker-Randow|Vorpommern-Greifswald") ~ "13075",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Wismar|Nordwestmecklenburg") ~ "13074",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Ludwigslust|Parchim") ~ "13076",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Neubrandenburg|Demmin|Müritz|Mecklenburg-Strelitz|Mecklenburgische Seenplatte") ~ "13071",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Hansestadt Rostock|Rostock") ~ "13003",
      state == "Mecklenburg-Vorpommern" & str_detect(constituency_key, "Stralsund|Rügen|Vorpommern-Rügen") ~ "13073",

      # =========================
      # RHEINLAND-PFALZ
      # =========================
      state == "Rheinland-Pfalz" & constituency_key == "Alzey" ~ "07331",
      state == "Rheinland-Pfalz" & constituency_key == "Andernach" ~ "07137",
      state == "Rheinland-Pfalz" & constituency_key == "Bad Kreuznach" ~ "07133",
      state == "Rheinland-Pfalz" & constituency_key == "Bad Marienberg (Westerwald)/Westerburg" ~ "07143",
      state == "Rheinland-Pfalz" & constituency_key == "Bad Neuenahr-Ahrweiler" ~ "07131",
      state == "Rheinland-Pfalz" & constituency_key == "Bendorf/Weißenthurm" ~ "07137",
      state == "Rheinland-Pfalz" & constituency_key == "Betzdorf/Kirchen (Sieg)" ~ "07132",
      state == "Rheinland-Pfalz" & constituency_key == "Donnersberg" ~ "07333",
      state == "Rheinland-Pfalz" & constituency_key == "Frankenthal (Pfalz)" ~ "07311",
      state == "Rheinland-Pfalz" & constituency_key == "Kaiserslautern I" ~ "07312",
      state == "Rheinland-Pfalz" & constituency_key == "Kaiserslautern II" ~ "07335",
      state == "Rheinland-Pfalz" & constituency_key == "Kirn/Bad Sobernheim" ~ "07133",
      state == "Rheinland-Pfalz" & constituency_key == "Kusel" ~ "07336",
      state == "Rheinland-Pfalz" & constituency_key == "Linz am Rhein/Rengsdorf" ~ "07138",
      state == "Rheinland-Pfalz" & str_detect(constituency_key, "^Mainz") ~ "07315",
      state == "Rheinland-Pfalz" & constituency_key == "Mayen" ~ "07137",
      state == "Rheinland-Pfalz" & constituency_key == "Montabaur" ~ "07143",
      state == "Rheinland-Pfalz" & constituency_key == "Mutterstadt" ~ "07338",
      state == "Rheinland-Pfalz" & constituency_key == "Neustadt an der Weinstraße" ~ "07316",
      state == "Rheinland-Pfalz" & constituency_key == "Pirmasens" ~ "07317",
      state == "Rheinland-Pfalz" & constituency_key == "Remagen/Sinzig" ~ "07131",
      state == "Rheinland-Pfalz" & constituency_key == "Rhein-Hunsrück" ~ "07140",
      state == "Rheinland-Pfalz" & constituency_key == "Speyer" ~ "07318",
      state == "Rheinland-Pfalz" & constituency_key == "Südliche Weinstraße" ~ "07337",
      state == "Rheinland-Pfalz" & constituency_key == "Trier" ~ "07211",
      state == "Rheinland-Pfalz" & constituency_key == "Vulkaneifel" ~ "07233",
      state == "Rheinland-Pfalz" & constituency_key == "Wittlich" ~ "07231",
      state == "Rheinland-Pfalz" & constituency_key == "Zweibrücken" ~ "07320",

      # =========================
      # SAARLAND
      # =========================
      state == "Saarland" & constituency_key == "Neunkirchen" ~ "10043",
      state == "Saarland" & constituency_key == "Saarbrücken" ~ "10041",
      state == "Saarland" & constituency_key == "Saarlouis" ~ "10044",

      # =========================
      # SACHSEN-ANHALT
      # =========================
      state == "Sachsen-Anhalt" & constituency_key == "Salzwedel" ~ "15081",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Havelberg-Osterburg", "Havelberg-Osterburg") ~ "15090",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Genthin", "Burg") ~ "15086",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Wolmirstedt", "Oschersleben", "Wanzleben") ~ "15083",
      state == "Sachsen-Anhalt" & str_detect(constituency_key, "^Magdeburg") ~ "15003",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Halberstadt", "Blankenburg", "Wernigerode", "Quedlinburg") ~ "15085",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Staßfurt", "Aschersleben", "Schönebeck", "Bernburg") ~ "15089",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Köthen", "Bitterfeld-Wolfen", "Wolfen") ~ "15082",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Wittenberg", "Jessen") ~ "15091",
      state == "Sachsen-Anhalt" & str_detect(constituency_key, "^Dessau-Roßlau$") ~ "15001",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Sangerhausen", "Eisleben") ~ "15087",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Saalekreis", "Bad Dürrenberg-Saalekreis", "Merseburg", "Querfurt") ~ "15088",
      state == "Sachsen-Anhalt" & str_detect(constituency_key, "^Halle") ~ "15002",
      state == "Sachsen-Anhalt" & constituency_key %in% c("Zeitz", "Nebra") ~ "15084",

      # =========================
      # SCHLESWIG-HOLSTEIN
      # =========================
      state == "Schleswig-Holstein" & constituency_key == "Dithmarschen-Süd" ~ "01051",
      state == "Schleswig-Holstein" & constituency_key == "Eckernförde" ~ "01058",
      state == "Schleswig-Holstein" & constituency_key == "Flensburg" ~ "01001",
      state == "Schleswig-Holstein" & constituency_key == "Flensburg-Land" ~ "01059",
      state == "Schleswig-Holstein" & constituency_key == "Kiel-Ost" ~ "01002",
      state == "Schleswig-Holstein" & constituency_key == "Lauenburg-Nord" ~ "01053",
      state == "Schleswig-Holstein" & constituency_key == "Lübeck-Süd" ~ "01003",
      state == "Schleswig-Holstein" & constituency_key == "Neumünster" ~ "01004",
      state == "Schleswig-Holstein" & constituency_key == "Nordfriesland-Nord" ~ "01054",
      state == "Schleswig-Holstein" & str_detect(constituency_key, "^Pinneberg") ~ "01056",
      state == "Schleswig-Holstein" & constituency_key == "Plön-Nord" ~ "01057",
      state == "Schleswig-Holstein" & constituency_key == "Rendsburg" ~ "01058",
      state == "Schleswig-Holstein" & constituency_key == "Segeberg-Ost" ~ "01060",
      state == "Schleswig-Holstein" & str_detect(constituency_key, "^Steinburg") ~ "01061",
      state == "Schleswig-Holstein" & str_detect(constituency_key, "^Stormarn") ~ "01062",

      # =========================
      # THUERINGEN
      # =========================
      state == "Thüringen" & str_detect(constituency_key, "^Eichsfeld") ~ "16061",
      state == "Thüringen" & str_detect(constituency_key, "^Erfurt") ~ "16051",
      state == "Thüringen" & str_detect(constituency_key, "^Gera") ~ "16052",
      state == "Thüringen" & constituency_key == "Gotha II" ~ "16067",
      state == "Thüringen" & constituency_key == "Greiz I" ~ "16076",
      state == "Thüringen" & str_detect(constituency_key, "^Ilm-Kreis") ~ "16070",
      state == "Thüringen" & str_detect(constituency_key, "^Jena") ~ "16053",
      state == "Thüringen" & str_detect(constituency_key, "^Kyffhäuserkreis") ~ "16065",
      state == "Thüringen" & str_detect(constituency_key, "^Nordhausen") ~ "16062",
      state == "Thüringen" & str_detect(constituency_key, "^Saale-Holzland-Kreis") ~ "16074",
      state == "Thüringen" & str_detect(constituency_key, "^Saale-Orla-Kreis") ~ "16075",
      state == "Thüringen" & str_detect(constituency_key, "^Saalfeld-Rudolstadt") ~ "16073",
      state == "Thüringen" & constituency_key == "Schmalkalden-Meiningen II" ~ "16066",
      state == "Thüringen" & constituency_key == "Sonneberg I" ~ "16072",
      state == "Thüringen" & constituency_key == "Sömmerda II" ~ "16068",
      state == "Thüringen" & str_detect(constituency_key, "^Unstrut-Hainich-Kreis") ~ "16064",

      TRUE ~ NA_character_
    ),

    match_quality = case_when(

      # non geographic
      constituency_key == "" ~ "missing",
      constituency_key == "Landesliste" ~ "non_geographic",
      state == "Bremen" & constituency_key == "" ~ "missing",

      # city-state handling
      state == "Berlin" ~ "state_level",
      state == "Hamburg" & constituency_key != "" ~ "state_level",
      state == "Bremen" & constituency_key %in% c("Bremen Listenwahl", "Bremen Personenwahl", "Bremen, Personenwahl", "Bremerhaven Listenwahl") ~ "exact",

      # explicit ambiguous multi-kreis
      state == "Baden-Württemberg" & constituency_key %in% c("Hechingen-Münsingen", "Tuttlingen-Donaueschingen") ~ "ambiguous_multi",
      state == "Bayern" & constituency_key %in% c(
        "Niederbayern", "Niederbayern Regen Freyung-Grafenau",
        "Mittelfranken Neustadt an der Aisch-Bad Windsheim Fürth-Land",
        "Oberfranken Wunsiedel Kulmbach",
        "Schwaben Kempten Oberallgäu",
        "Schwaben Lindau Sonthofen",
        "Schwaben Lindau-Sonthofen"
      ) ~ "ambiguous_multi",
      state == "Brandenburg" & constituency_key %in% c(
        "Märkisch-Oderland I/Oder-Spree IV",
        "Oberspreewald-Lausitz II/Spree-Neiße IV",
        "Oberspreewald-Lausitz III/Spree-Neiße III",
        "Ostprignitz-Ruppin III / Havelland III",
        "Prignitz II/Ostprignitz-Ruppin II",
        "Uckermark III / Oberhavel IV"
      ) ~ "ambiguous_multi",
      state == "Rheinland-Pfalz" & constituency_key %in% c(
        "Bernkastel-Kues/Morbach/Kirchberg (Hunsrück)",
        "Koblenz/Lahnstein"
      ) ~ "ambiguous_multi",
      state == "Sachsen-Anhalt" & constituency_key == "Dessau-Roßlau-Wittenberg" ~ "ambiguous_multi",
      state == "Schleswig-Holstein" & constituency_key %in% c("Dithmarschen-Schleswig", "Plön-Ostholstein") ~ "ambiguous_multi",
      state == "Thüringen" & constituency_key %in% c(
        "Hildburghausen I – Schmalkalden-Meiningen III",
        "Suhl - Schmalkalden-Meiningen III",
        "Suhl – Schmalkalden-Meiningen IV",
        "Sömmerda I – Gotha III",
        "Wartburgkreis II – Eisenach",
        "Weimar I – Weimarer Land II",
        "Weimarer Land I – Saalfeld-Rudolstadt III"
      ) ~ "ambiguous_multi",

      # exact one-kreis/city name matches
      state == "Baden-Württemberg" & constituency_key %in% c(
        "Böblingen", "Esslingen", "Göppingen", "Ludwigsburg", "Heidenheim",
        "Baden-Baden", "Heidelberg", "Neckar-Odenwald", "Calw", "Enz",
        "Freudenstadt", "Emmendingen", "Rottweil", "Konstanz", "Lörrach",
        "Reutlingen", "Tübingen", "Ulm", "Ravensburg", "Sigmaringen"
      ) ~ "exact",

      state == "Bayern" & constituency_key %in% c(
        "Mittelfranken Erlangen-Stadt", "Niederbayern Deggendorf",
        "Oberbayern Eichstätt", "Oberbayern Mühldorf am Inn",
        "Oberfranken Forchheim", "Oberpfalz Cham",
        "Oberpfalz Neumarkt in der Oberpfalz", "Oberpfalz Regensburg-Stadt",
        "Oberpfalz Tirschenreuth", "Oberpfalz Weiden in der Oberpfalz",
        "Schwaben Aichach-Friedberg", "Schwaben Neu-Ulm",
        "Schwaben, Memmingen", "Unterfranken Würzburg-Land"
      ) ~ "exact",

      state == "Brandenburg" & constituency_key %in% c(
        "Frankfurt (Oder)"
      ) ~ "exact",

      state == "Hessen" & constituency_key %in% c(
        "Odenwald", "Offenbach-Stadt"
      ) ~ "exact",

      state == "Rheinland-Pfalz" & constituency_key %in% c(
        "Bad Kreuznach", "Donnersberg", "Frankenthal (Pfalz)", "Kusel",
        "Neustadt an der Weinstraße", "Pirmasens", "Speyer",
        "Südliche Weinstraße", "Trier", "Vulkaneifel", "Zweibrücken"
      ) ~ "exact",

      state == "Saarland" & constituency_key %in% c(
        "Neunkirchen", "Saarbrücken", "Saarlouis"
      ) ~ "exact",

      state == "Sachsen-Anhalt" & constituency_key %in% c(
        "Salzwedel", "Dessau-Roßlau", "Saalekreis"
      ) ~ "exact",

      state == "Schleswig-Holstein" & constituency_key %in% c(
        "Flensburg", "Neumünster"
      ) ~ "exact",

      # everything else with a usable kreis_name
      !is.na(kreis_name) ~ "approx",

      TRUE ~ NA_character_
    )
  )
```

```{r}
constituency_to_kreis %>%
  filter(is.na(kreis_name) | is.na(match_quality)) %>%
  select(state, Constituency, constituency_key) %>%
  arrange(state, constituency_key)
```

```{r}
iv_panel <- read.csv("/Users/diananichvoloda/Desktop/iv_total_new.csv")
```

# Merge Together

```{r}
library(readr)
library(dplyr)
library(stringr)
library(purrr)
library(lubridate)

samples_dir <- "/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples"

sample_files <- list.files(
  path = samples_dir,
  pattern = "_sample\\.csv$",
  full.names = TRUE
)

all_samples <- map_dfr(sample_files, function(f) {
  df <- read_csv(
    f,
    show_col_types = FALSE,
    col_types = cols(
      ags = col_character(),
      state = col_character(),
      district = col_character(),
      Party = col_character(),
      Constituency = col_character(),
      constituency_key = col_character(),
      Speech = col_character()
    )
  )
  
  df %>%
    mutate(
      source_file = basename(f),
      ags = str_pad(as.character(ags), width = 5, side = "left", pad = "0")
    )
})

all_samples <- all_samples %>%
  mutate(
    Date = as.Date(Date),
    year = year(Date),
    month = month(Date),
    ym = format(Date, "%Y-%m")
  )

print(dim(all_samples))
print(names(all_samples))
print(table(all_samples$state, useNA = "ifany"))

write_csv(
  all_samples,
  file.path(samples_dir, "all_state_samples_stacked.csv")
)
```

```{r}
# Importing scored samples

Final_scored <- read.csv("/Users/diananichvoloda/Library/CloudStorage/GoogleDrive-diananichvoloda@college.harvard.edu/My Drive/2025-2026/Econ 1425/PAPER/DATA/Text Data/Samples/all_state_samples_scored.csv")

library(dplyr)
library(stringr)

Final_clean <- Final_scored %>%
  
  # Step 1: identify base column names
  {
    df <- .
    
    base_names <- unique(str_remove(names(df), "_x$|_y$"))
    
    # Step 2: loop over base names and coalesce
    for (nm in base_names) {
      x_col <- paste0(nm, "_x")
      y_col <- paste0(nm, "_y")
      
      if (x_col %in% names(df) & y_col %in% names(df)) {
        df[[nm]] <- dplyr::coalesce(df[[x_col]], df[[y_col]])
      } else if (x_col %in% names(df)) {
        df[[nm]] <- df[[x_col]]
      } else if (y_col %in% names(df)) {
        df[[nm]] <- df[[y_col]]
      }
    }
    
    df
  } %>%
  
  # Step 3: drop all *_x and *_y columns
  select(-matches("_x$|_y$"))

```

```{r}
Final_clean <- Final_clean %>%
  mutate(
    year = as.integer(year),
    election_year = case_when(
      year <= 2013 ~ 2013,
      year <= 2017 ~ 2017,
      year <= 2021 ~ 2021,
      year <= 2025 ~ 2025,
      TRUE ~ NA_real_
    )
  )



panel_ags_election <- Final_clean %>%
  group_by(ags, election_year) %>%
  summarise(
    n_speeches = n(),
    mean_anti_immigration = mean(anti_immigration_sentiment, na.rm = TRUE),
    share_nonzero = mean(anti_immigration_sentiment > 0, na.rm = TRUE),
    .groups = "drop"
  )
```

Filter for Immigration-related speeches

```{r}
keywords <- c(
  # Core migration terms
  "migration", "migrant", "immigra", "einwander", "zuwander",
  
  # Refugees / asylum
  "flücht", "asyl", "schutzsuch", "vertrieb", "umsiedl",
  
  # Legal status / policy
  "aufenthalt", "visa", "visum", "aufnahm", "abschieb", "duld",
  "einbürger", "staatsbürg",
  
  # Borders / control
  "grenz", "grenze", "grenzschutz", "kontroll",
  
  # Integration / society
  "integration", "integrations", "teilhabe", "parallelgesellschaft",
  "leitkultur", "multikulti",
  
  # Labor / economic migration
  "fachkräft", "arbeitskräft", "zuwanderungsgesetz",
  
  # Irregular migration / enforcement
  "illegal", "irregul", "schleus", "abschieb", "rückführ",
  
  # Crisis framing (very relevant in Germany)
  "flüchtlingskrise", "migrationskrise", "asylpolitik",
  
  # Regions often used as proxies
  "syr", "ukrain", "afghan", "irak", "afrika",
  
  # EU / external dimension
  "dublin", "frontex", "schengen",
  
  # General foreigner terms
  "ausländer", "ausländ", "nichtdeutsch"
)

library(stringr)

Final_clean_immigration <- Final_clean %>%
  mutate(
    mentions_immigration = str_detect(
      tolower(Speech),
      str_c(keywords, collapse = "|")
    )
  )

immigration_speeches <- Final_clean_immigration %>%
  filter(mentions_immigration == TRUE)
```

Aggregate

```{r}


state_agg <- immigration_speeches %>%
  group_by(state, election_year) %>%
  summarise(
    mean_sentiment = mean(anti_immigration_sentiment, na.rm = TRUE),
    median_sentiment = median(anti_immigration_sentiment, na.rm = TRUE),
    sd_sentiment = sd(anti_immigration_sentiment, na.rm = TRUE),
    n_speeches = n()
  )
```

Merging with IV panel

```{r}
IV <- read.csv("/Users/diananichvoloda/Desktop/iv_total_new.csv")

IV_clean <- IV %>%
  mutate(
    AGS = str_pad(as.character(AGS), 5, pad = "0"),
    year = as.integer(year)
  )

panel_ags_election <- panel_ags_election %>%
  mutate(
    ags = str_pad(as.character(ags), 5, pad = "0"),
    election_year = as.integer(election_year)
  )

IV_merged <- IV_clean %>%
  left_join(
    panel_ags_election,
    by = c("AGS" = "ags", "year" = "election_year")
  )
```

# New Merge with IV

```{r}
IV <- read.csv("/Users/diananichvoloda/Desktop/iv_total_new.csv") 

library(dplyr)

state_year_agg <- IV %>%
  group_by(state, year) %>%
  summarise(
    counties_n = n(),

    afd = weighted.mean(afd, w = valid_votes, na.rm = TRUE),
    far_right = weighted.mean(far_right, w = valid_votes, na.rm = TRUE),

    eligible_voters = sum(eligible_voters, na.rm = TRUE),
    number_voters   = sum(number_voters, na.rm = TRUE),
    valid_votes_sum = sum(valid_votes, na.rm = TRUE),

    syria_net_4yr   = sum(syria_net_4yr, na.rm = TRUE),
    ukraine_net_4yr = sum(ukraine_net_4yr, na.rm = TRUE),

    turnout = number_voters / eligible_voters,

    .groups = "drop"
  ) %>%
  rename(valid_votes = valid_votes_sum)
```

# New Merge

```{r}
state_year_agg <- state_year_agg %>%
  rename(election_year = year)
state_lookup <- tibble::tribble(
  ~state, ~state_name,
  1, "Schleswig-Holstein",
  2, "Hamburg",
  3, "Niedersachsen",
  4, "Bremen",
  5, "Nordrhein-Westfalen",
  6, "Hessen",
  7, "Rheinland-Pfalz",
  8, "Baden-Württemberg",
  9, "Bayern",
  10, "Saarland",
  11, "Berlin",
  12, "Brandenburg",
  13, "Mecklenburg-Vorpommern",
  14, "Sachsen",
  15, "Sachsen-Anhalt",
  16, "Thüringen"
)

state_year_agg <- state_year_agg %>%
  left_join(state_lookup, by = "state") %>%
  mutate(state = state_name) %>%
  select(-state_name)

state_year_full <- state_year_agg %>%
  left_join(state_agg, by = c("state", "election_year"))

state_year_full <- state_year_full %>%
  mutate(
    ukraine_per_voter = ukraine_net_4yr / eligible_voters,
    syria_per_voter   = syria_net_4yr / eligible_voters
  )
```

Regression at the state level

```{r}
model_state <- feols(
  mean_sentiment ~ syria_per_voter + ukraine_per_voter |
  state + election_year,
  data = state_year_full,
  cluster = ~state
)

summary(model2) 
```

Diagnostic

```{r}
unmatched <- IV_clean %>%
  anti_join(
    panel_clean,
    by = c("AGS" = "ags", "year" = "election_year")
  )

unmatched %>%
  count(year, sort = TRUE)

unmatched %>%
  select(AGS, year) %>%
  distinct() %>%
  print(n = 100)
```

```{r}
Final_clean %>%
  count(ags, election_year) %>%
  nrow()
nrow(panel_ags_election)

mean(is.na(IV_merged$mean_anti_immigration))

IV_observed <- IV_merged %>%
  filter(!is.na(mean_anti_immigration))
```

Regressions

```{r}
model1 <- lm(
  mean_anti_immigration ~ syria_per_voter + ukraine_per_voter,
  data = IV_merged
)

summary(model1)
```

```{r}
model2 <- feols(
  mean_anti_immigration ~ syria_per_voter + ukraine_per_voter |
  AGS + year,
  data = IV_merged,
  cluster = ~AGS
)

summary(model2) 
```

```{r}
model3 <- feols(
  mean_anti_immigration ~ syria_per_voter + ukraine_per_voter |
  AGS + year,
  weights = ~n_speeches,
  data = IV_merged,
  cluster = ~AGS
)

summary(model3)
```

```{r}
model4 <- feols(
  share_nonzero ~ syria_per_voter + ukraine_per_voter |
  AGS + year,
  weights = ~n_speeches,
  cluster = ~AGS,
  data = IV_merged
)

summary(model4)
```

# IV Estimates

Ukraine

```{r}
# ---- First stage regression ----
fs_ukraine <- feols(
  ukraine_per_voter ~ z_ukraine_per_voter | AGS + year,
  cluster = ~AGS,
  data = IV_merged
)

summary(fs_ukraine)

f_test <- wald(fs_ukraine, "z_ukraine_per_voter")
print(f_test)
f_stat <- f_test$stat
f_stat


iv_ukraine <- feols(
  mean_anti_immigration ~ 1 | AGS + year |
  ukraine_per_voter ~ z_ukraine_per_voter,
  cluster = ~AGS,
  data = IV_merged
)

summary(iv_ukraine)
```

Syria

```{r}
# ---- First stage regression ----
fs_syria <- feols(
  syria_per_voter ~ z_syria_2008_per_voter | AGS + year,
  cluster = ~AGS,
  data = IV_merged
)

summary(fs_syria)

f_test <- wald(fs_syria, "z_syria_2008_per_voter")
print(f_test)
f_stat <- f_test$stat
f_stat

iv_syria <- feols(
  mean_anti_immigration ~ 1 | AGS + year | syria_per_voter ~ z_syria_2008_per_voter,
  cluster = ~AGS,
  data = IV_merged
)

summary(iv_syria)
```

With AfD

```{r}
ols_interaction_w <- feols(
  afd ~ mean_anti_immigration  ,
  weights = ~n_speeches,
  cluster = ~AGS,
  data = IV_merged %>% filter(n_speeches>5)
)

summary(ols_interaction_w)
```

```{r}
ols_interaction_w1 <- feols(
  afd ~ syria_per_voter * mean_anti_immigration | AGS + year,
  weights = ~n_speeches,
  cluster = ~AGS,
  data = IV_merged
)

summary(ols_interaction_w1)
```
